### 2022-05-17 masters_paper_new_2022(1).tex
Add files via upload

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\author{}
\date{}

\begin{document}

\begin{quote}
Predicting the Quality of CDRH3 Antibody Loop Structural Models

From the Department of Structural and Molecular Biology,

University College of London, Gower Street, London WC1E 6BT UK
\end{quote}

\hypertarget{abstract}{%
\section{ABSTRACT}\label{abstract}}

\hypertarget{therapeutic-antibodies-have-shown-an-unprecedented-pace-of-development-and-have-brought-new-hope-for-the-treatment-of-numerous-diseases.-the-bioinformatic-tools-for-modelling-antibody-structures-have-become-invaluable-for-antibody-engineering-and-the-development-of-therapeutic-antibodies.-the-antigen-binding-site-consists-of-six-hypervariable-loops-also-known-as-the-complementary-determining-regions-cdr-all-of-which-can-be-modelled-with-adequate-accuracy-except-for-one.-it-remains-markedly-difficult-to-model-the-third-cdr-loop-of-the-antibody-heavy-chain.-the-cdrh3-differs-in-length-has-far-greater-sequence-variability-and-has-such-a-great-structural-diversity-that-modelling-it-is-considerably-harder.}{%
\section{\texorpdfstring{Therapeutic antibodies have shown an
unprecedented pace of development and have brought new hope for the
treatment of numerous diseases. The bioinformatic tools for modelling
antibody structures have become invaluable for antibody engineering and
the development of therapeutic antibodies. The antigen-binding site
consists of six hypervariable loops, also known as the Complementary
Determining Regions (CDR), all of which can be modelled with adequate
accuracy, except for one. It remains markedly difficult to model the
third CDR loop of the antibody heavy chain. The CDRH3 differs in length,
has far greater sequence variability and has such a great structural
diversity that modelling it is considerably harder.
}{Therapeutic antibodies have shown an unprecedented pace of development and have brought new hope for the treatment of numerous diseases. The bioinformatic tools for modelling antibody structures have become invaluable for antibody engineering and the development of therapeutic antibodies. The antigen-binding site consists of six hypervariable loops, also known as the Complementary Determining Regions (CDR), all of which can be modelled with adequate accuracy, except for one. It remains markedly difficult to model the third CDR loop of the antibody heavy chain. The CDRH3 differs in length, has far greater sequence variability and has such a great structural diversity that modelling it is considerably harder. }}\label{therapeutic-antibodies-have-shown-an-unprecedented-pace-of-development-and-have-brought-new-hope-for-the-treatment-of-numerous-diseases.-the-bioinformatic-tools-for-modelling-antibody-structures-have-become-invaluable-for-antibody-engineering-and-the-development-of-therapeutic-antibodies.-the-antigen-binding-site-consists-of-six-hypervariable-loops-also-known-as-the-complementary-determining-regions-cdr-all-of-which-can-be-modelled-with-adequate-accuracy-except-for-one.-it-remains-markedly-difficult-to-model-the-third-cdr-loop-of-the-antibody-heavy-chain.-the-cdrh3-differs-in-length-has-far-greater-sequence-variability-and-has-such-a-great-structural-diversity-that-modelling-it-is-considerably-harder.}}

\hypertarget{many-sophisticated-approaches-for-antibody-modelling-such-as-the-abymod-software-have-been-developed.-although-such-efforts-have-improved-prediction-accuracy-the-results-for-the-cdrh3-loop-are-still-inconsistent-and-require-further-improvement.-providing-a-confidence-score-for-the-structure-predictions-would-aid-in-differentiating-well-modelled-structures-from-incorrectly-modelled-structures-giving-the-abymod-user-a-clearer-understanding-of-the-generated-model-reliability.}{%
\section{\texorpdfstring{Many sophisticated approaches for antibody
modelling, such as the abYmod software, have been developed. Although
such efforts have improved prediction accuracy the results for the CDRH3
loop are still inconsistent and require further improvement. Providing a
confidence score for the structure predictions would aid in
differentiating well-modelled structures from incorrectly modelled
structures, giving the abYmod user a clearer understanding of the
generated model reliability.
}{Many sophisticated approaches for antibody modelling, such as the abYmod software, have been developed. Although such efforts have improved prediction accuracy the results for the CDRH3 loop are still inconsistent and require further improvement. Providing a confidence score for the structure predictions would aid in differentiating well-modelled structures from incorrectly modelled structures, giving the abYmod user a clearer understanding of the generated model reliability. }}\label{many-sophisticated-approaches-for-antibody-modelling-such-as-the-abymod-software-have-been-developed.-although-such-efforts-have-improved-prediction-accuracy-the-results-for-the-cdrh3-loop-are-still-inconsistent-and-require-further-improvement.-providing-a-confidence-score-for-the-structure-predictions-would-aid-in-differentiating-well-modelled-structures-from-incorrectly-modelled-structures-giving-the-abymod-user-a-clearer-understanding-of-the-generated-model-reliability.}}

\hypertarget{we-present-a-model-quality-predictor-combining-domain-knowledge-with-machine-learning-techniques-to-predict-the-accuracy-of-cdrh3-models-generated-by-abymod.-the-newly-developed-predictor-scored-a-mathews-correlation-coefficient-of-0.63-thus-its-reliability-could-be-demonstrated.}{%
\section{We present a model quality predictor, combining domain
knowledge with machine learning techniques to predict the accuracy of
CDRH3 models generated by abYmod. The newly developed predictor scored a
Mathews Correlation Coefficient of 0.63, thus its reliability could be
demonstrated.}\label{we-present-a-model-quality-predictor-combining-domain-knowledge-with-machine-learning-techniques-to-predict-the-accuracy-of-cdrh3-models-generated-by-abymod.-the-newly-developed-predictor-scored-a-mathews-correlation-coefficient-of-0.63-thus-its-reliability-could-be-demonstrated.}}

\hypertarget{we-conclude-our-predictor-may-prove-useful-for-abymod-users-and-would-be-a-useful-future-addition-to-the-modelling-software-web-interface.}{%
\section{\texorpdfstring{We conclude our predictor may prove useful for
abYmod users and would be a useful future addition to the modelling
software web interface.
}{We conclude our predictor may prove useful for abYmod users and would be a useful future addition to the modelling software web interface. }}\label{we-conclude-our-predictor-may-prove-useful-for-abymod-users-and-would-be-a-useful-future-addition-to-the-modelling-software-web-interface.}}

Antibodies are highly specialized proteins of the immune system that are
produced in response to a foreign substance, called an antigen. A mature
antibody binds a specific antigen with high affinity, while only weakly
interacting with other antigens, or not at all. This high affinity, high
specificity sets it apart from other pharmaceuticals. Furthermore, in
contrast with small drug molecules, antibodies can not only bind
pockets, but also flat, concave or even convex
surfaces\textsuperscript{1}. Their unique characteristics have enabled
researchers to develop efficient antibody drugs for treating cancers,
autoimmune disorders, infectious diseases and many more
\textsuperscript{2}. Their ability to target an immense variety of
antigens allows for endless possibilities in application. The global
market size was valued at USD 130.9 billion in 2020, estimated to grow
223.7 billion by the end of 2025 at a compound annual growth rate of
11.31\% \textsuperscript{3}. Four of the top 10 best-selling drugs in
2020 were monoclonal antibodies \textsuperscript{4}.

In order to rationally design therapeutic antibodies, knowledge of their
structure is essential. The acquired structural information can be used
to increase binding affinity to a target of interest, predicting both
the exact binding site and the antibody stability as well as assessing
immunogenicity \textsuperscript{5}. As experimental structure
determination is very costly and time consuming, computational
predictions of an antibody's structure are used to streamline the
process.

Antibodies consist of a heavy and a light chain, which are linked by
disulphide bonds. The N-terminal domain of each makes up the variable
fragment (Fv), which contains the complementarity determining regions
(CDRs). The antigen binding site is composed of six CDRs, also known as
hypervariable loops. All except one of these loops can be clustered into
a limited number of canonical structures. Therefore, modelling these
loops with adequate accuracy is commonly achievable
\textsuperscript{6,7}. However, the CDR loop 3 of the heavy chain
(CDRH3) has a far greater sequence variability due to the processes of
V(D)J recombination and somatic hyper‐mutation and its structure has
remained unclassifiable \textsuperscript{8}. The variety in structure is
so great, that its structural diversity is remarkable even compared to
other protein loops \textsuperscript{9}. It was found that over 75\% of
CDRH3 loops do not have a sub-Angstrom non-antibody structural
neighbour, as well as that 30\% of CDRH3 loops have a completely unique
structure compared with under 3\% for all other loops on average
\textsuperscript{9}.

Apart from being the most structurally diverse, the H3 loop is also the
most important for antigen binding, being located at the center of the
binding site and forming the most contacts to the antigen
\textsuperscript{10}. In fact, it was demonstrated that differences in
this loop alone were sufficient to enable otherwise identical antibodies
to distinguish between various antigens \textsuperscript{11}.

\includegraphics[width=6.51667in,height=2.55833in]{media/image1.png}
According to the Kabat definition, the CDRH3 loop is made up of the
residues 95-105 (Kabat numbering scheme\textsuperscript{12}) in the
heavy chain, with a potential insertion site at position 100. The
possibility of such an insertion of a varying number of residues leads
to a large range of loop lengths, with bovine antibodies being
exceptionally long (Fig.1).

For shorter loops, a higher prediction accuracy can be achieved than for
longer CDRH3 loops. This was also shown by the Antibody Modelling
Assessments (AMA), two blind contests that required researchers to build
structural models from antibody sequences. The CDR-H3 loop modelling
quality achieved at the contests was on average much lower for loops of
longer lengths \textsuperscript{13,14}.

Several different approaches for generating three-dimensional structure
models from antibody sequences exist such as RosettaAntibody
\textsuperscript{15,16}, ABodyBuilder\textsuperscript{17},
PIGSPro\textsuperscript{18} and abYmod, UCL's in-house software
developed by Prof. Martin. One of the most used methods is
RosettaAntibody, which implements template selection and ab initio
CDR-H3 loop modelling using loop fragments and employing specific angle
restraints which bias the conformational space towards so-called
`kinked' loops\textsuperscript{19,20}. In contrast, ABodyBuilder uses a
database search algorithm (FREAD\textsuperscript{21}) for CDR loop
modelling.

In this project abYmod is used, which is to be found at
\url{http://abymod.abysis.org/}. The program utilizes extensive
canonical class definitions, VH/VL angle prediction and a large database
of loop structures (LoopDB) for CDR-H3 modelling to achieve optimal
results. Upon inputting an antibody sequence, abYmod assigns the
canonical class using a set of key residues \textsuperscript{22}and
where an exact match is not possible, a nearest match is made. Then, the
program identifies the 10 best overall-matching PDB files according to
sequence identity for the light and heavy chain. Of these, the best
template is then identified for each CDR using sequence similarity and
identity. In general, modelling the antibody using the single best
overall-matching template works best and the CDR-specific templates are
used if there is no canonical match. The VH/VL packing angle is then
determined either using machine learning or the chosen template
structure for one of the chains. CDR specific templates, if selected,
are grafted onto the framework. If there is no template of the correct
length for CDR-H3, the loop is built using the LoopDB database,
containing CDRH3-like loops from all proteins. Finally, Gromacs energy
minimization software is used to optimize the model. This method has
proven very effective and preliminary analysis suggests the method
achieves comparable results or outperforms other modelling software (see
results section).

\includegraphics[width=5.78542in,height=3.34583in]{media/image7.png}\includegraphics[width=2.61914in,height=2.05972in]{media/image9.png}
Using these mentioned modelling methods, framework regions can generally
be predicted with great accuracy (with better than 1Å
RMSD\textsuperscript{13}), as one can often find a very similar
structure for the homology modelling process. However, the CDR loops are
not as easily predicted due to their great diversity. If the canonical
conformation of CDR loops 1-5 can be identified, they too can be
modelled rather well, often within 1Å RMSD, for CDR-H3 loops the average
is usually above 3Å \textsuperscript{13}.

\includegraphics[width=3.32639in,height=3.65972in]{media/image10.png}To
our knowledge, ABodyBuilder is the only modelling server that provides
the user with a confidence score for each region (e.g.CDR-H2) of the
antibody model. The given score is the probability that a specific
region (e.g. CDR-H2) will be Thus, it can be used to obtain an expected
RMSD value for a given probability (default 75\%). For the CDR-H3 this
score is calculated as a function of the loop length. The confidence
scorer is described as robust, but less accurate in the case of CDR
loops due to the lack of data.\textsuperscript{17}

Modelling the H3 loop is a hurdle for in silico development of
therapeutic antibodies. Currently, there is no reliable way to determine
how accurate a generated structural model is within the H3 region.
Therefore, the aim of this project will be to produce a user-friendly
predictor of H3 model quality. The predictor will give the user an
RMSD-range in Ångstöms, in which the generated model lies with a high
probability. Making such a confidence score available via the web
interface of the in-house modelling software abYmod is a future goal.
Such a score is not provided by most modelling programs and would thus
be a novel addition. This information can guide the user in the antibody
engineering process. The user has the choice to determine whether the
model is to be used in the intended way, or whether the model should be
re-worked.

\textbf{RESULTS}

predictive power regarding the CDR-H3 loop, the software was tested on a
test-set of antibody structures used in the 2014 and 2011 Antibody
Modelling Assessments \textsuperscript{13,23}. As the results depicted
in \emph{fig}.2 show, abYmod achieves results similar to, or better than
other modelling programs. However, the outliers with very high RMSD
values increase abYmod's RMSD average. The predictor in this work would
aim to identify such outlier models.

The predictive power of any machine learning model is largely dependent
on the quality and size of the dataset it was trained on. As this is a
non-linear, complex, multi-class classification problem, a substantial
amount of data was required. Thus, an extensive, verified dataset of
antibody structures called abYbank/AbDb\textsuperscript{24}, established
by Prof. Andrew Martin, was utilised (1924 non-redundant structures).
The root-mean-square deviation (RMSD) value, a measure of distance
between backbone C-α atoms of superimposed crystal structures and
modelled structures, is calculated (see methods). This metric for model
quality was used to classify models.

\includegraphics[width=3.60764in,height=3.48125in]{media/image14.png}The
full pipeline for creating the final machine learning model that will
predict model quality by giving its RMSD range is summarized in
\emph{fig.3}. The first step of this process is feature-set calculation
using the antibody sequence. The feature set includes many different
attributes linked to sequence, physical characteristics, interactions,
etc. within as well as outside of the loop. There is a plethora of
information to train our classifier on, including packing quality,
protrusion, hydrophobicity, pseudo-energy (see

protrusion, hydrophobicity, pseudo-energy (see methods for details). The
sequence logo (\emph{fig.4}) visualizes amino acid occurrence within the
loop sequence, elements of which can be extracted as features
\textsuperscript{26,27}.

After creating the feature dataset, it is pre-processed (cleaning,
scaling, encoding, see methods for details). Structures with a
resolution below 4Å were removed given their low quality. Identical
whole antibody structures were removed from the dataset, while instances
of different antibodies that matched in loop sequence were not removed.
Fig.5 illustrates that models of some of these structures with the same
loop sequence differ significantly. The few large RMSD ranges may stem
from low resolution, e.g. the highest datapoint contains a structure
with a resolution of 3.00 Å. Residue differences near the loop may also
explain the conformational difference. Some of these structures are
complexed while others are not, which may also affect the loop
structure.

The dataset was also screened for any models which

abYmod created using a template sequence from LoopDB, a database of
CDR-H3 like loops from all proteins. This was not the case for any of
our structures.

The target data (i.e. RMSD values) are then transformed from numerical
values to nominal values so that they can be used for classification. In
order to define these nominal categories, the total RMSD range must be
divided into categories. This is done either by creating uniform classes
i.e. 1-2Å, 2-3Å (the optimal size of which must be determined), etc. or
by creating balanced classes. When creating balanced classes, the upper
and lower thresholds of a category are chosen in such a way that each
class contains an equal number of instances. This approach is chosen to
counteract the skewness of the RMSD distribution (\emph{fig}.2).
However, this was found to negatively affect the final model's
predictive power. Therefore, uniform classes were used.

They are also transformed into a set of binary values according to a
list of RMSD thresholds. This is done so that binary models can be
trained, which will predict the probability e.g. that the model's RMSD
is above 2Å, 2.2Å, 2.4Å, and so on. The number of binary classifiers
incorporated into the first layer

have a great effect on the final model, the general

trend being that the more binary classifiers are used, the better the
nominal prediction.

\textbf{Feature Encoding and Selection}

As some features are in the form of amino acid codes, these must be
encoded before they can be passed to a machine learning model. The
encoding strategy often determines how efficiently the model learns and
how much information can be extracted. Different strategies were
employed to represent amino acids as a numerical value: one-hot
encoding, BLOSUM62 encoding, NLF encoding and a 4-feature physiochemical
encoding method (see methods section). The effect of encoding strategy
on the ML model's performance was evaluated. It was

\includegraphics[width=7.25in,height=3.81111in]{media/image16.png}found
that one-hot encoding was the least effective,

followed by BLOSUM62 and NLF encoding. The physiochemical encoding
strategy was implemented for all models, being the most effective.
However, PCA-3 BLOSUM62, a dimensionality-reduced BLOSUM62 encoding
method achieved comparable results.

Feature selection was conducted to improve the ML model's learning
capacity. A high-dimensional feature dataset bears the risk of
introducing excessive noise, facilitating model overfitting and can be
responsible for an overall decrease in model performance and stability.
Each additionally inputted feature forces the model to handle a more
complex task, which consumes excess computational power and time and
leads to overfitting of the model.

Our model is trained on different feature sets selected using manual
selection as well as algorithmic selection strategies (see appendix), in
order to determine the most effective feature selection method. None of
the feature selection methods was a best fit for all models. However,
the

After the data is processed, it can be fed into different machine
learning models. Different model types are investigated, as the most
suited model-type has to be heuristically determined. We decided on the
following list, which includes some of the most commonly used
algorithms: logistic regression, linear discriminant analysis, K-nearest
neighbours classifier, decision tree classifier, Gaussian NB, random
forest classifier, support vector machine, probability-based voting
(also known as soft voting) and extreme gradient boosting
(XGBoost)\textsuperscript{28}.

The best model, and its best hyperparameters, are then determined for
each binary RMSD target. The set of binary models outputs a number of
predictions that give the likelihood of the model having an RMSD above
the threshold value of the respective model. These predictions are then
added to the feature set, which a top-layer classifier is then trained
on. Thus, a quasi-voting-system is incorporated into the final
classifier, in which a set of weaker classifiers vote on the model
quality.

\textbf{Hyperparameter Optimization}

In the process of hyperparameter optimization, the configuration of
model parameters which results in best performance is selected. This is
usually a computationally expensive and manual procedure.

In an effort to automate this process, a population is defined for each
model type, so hyperparameter optimization can be conducted
automatically for each model and seamlessly integrated into the full
model creation process. Two different methods for hyperparameter
optimization were tested. The first is a hybrid approach of randomized
search and grid search, the second uses a genetic algorithm for
optimization. The genetic algorithm was found to achieve slightly better
results and was selected for all models.

\textbf{Model Performance}

The overall best final model is composed of several different binary
classifiers, with an extreme gradient boosting (XGBoost) top-layer
nominal classifier. Features were selected using random forest feature
selection. A final MCC value of 0.64 could be achieved.

The classifier predicts whether a model has an RMSD of 0-2Å (`class 0'),
2-4Å (`class 1') or above 4Å (`class 2'). These cut-off values were
selected based on the observation that abYmod generally produces a model
with RMSD below 4Å. Incorrectly modelled structures (such as the ones
seen in Fig 2.) may be identified by screening for `class 2'. If a very
high-quality model is needed one should find this in `class 0'.

\hypertarget{section}{%
\section{}\label{section}}

\hypertarget{discussion}{%
\section{DISCUSSION}\label{discussion}}

\hypertarget{section-1}{%
\section{}\label{section-1}}

The results suggest that our presented classifier can differentiate
between well-modelled and less well-modelled CDR-H3 loop structures. An
MCC value of 0.63 was achieved, which underlines this ability for
accurate discrimination. Different methods for data pre-processing,
feature encoding, feature selection and hyperparameter optimization were
tested.

Feature encoding methods that were very high-dimensional
(one-hot-encoding, BLOSUM62, NLF) were found to be unfavorable.
Dimensionality reduction methods (Principal Component Analysis (PCA),
Independent Component Analysis (ICA), projection-based methods e.g.
t-SNE) were used on BLOSUM62 encoded matrices, which lead to significant
improvement. However, a physiochemical encoding strategy was most
effective.

The selection of features incorporated in the training set seemed to be
most important for effective learning. A multitude of methods were
tested. No one-fit-for-all method for the different models could be
found. However, for our top-layer classifier in our final model
recursive feature elimination worked best.

A set of commonly used machine learning algorithms were tested, and the
best ML models were incorporated into the final ensemble model. A
stacked model approach (consisting of 23 binary classifiers and a single
top-layer nominal classifier) was shown to outperform single ML models.

An MCC value of 0.63 was achieved for a classifier predicting whether an
input-model has an RMSD value below 2Å, 2Å-4Å or above 4Å.

Further research may enable additional optimization of the classifier
making it more reliable.

Given that abYbank/AbDb is soon to be expanded by an additional ca. 2000
structures, classifier performance may be improved by a larger dataset.

At a later stage the model could provide an abYmod user with information
on the generated model's quality in the CDR-H3 region via a
web-interface.

It is conceivable that the described predictor may also be incorporated
in the antibody modelling process as a low-quality filter in the future,
flagging certain structures for re-modelling.

In a future research project residue patterns in correlation with RMSD
may be analyzed. Possibly, one might identify certain sequence patterns
that make accurate modelling with abYmod more difficult. Furthermore,
separate classifiers according to loop length can be built. Given that
loop length is the most important determinant of model quality, this
approach may yield some insight into the challenges of modelling shorter
vs longer loops.

One could also conduct an analysis of the predictor's behaviour when
abYmod is forced to use LoopDB-based modelling. This might shed light on
whether the ML model presented in this paper is biased towards abYmod's
used source of template structures. It would also give an indication of
how well the predictor would work in combination with other modelling
software.

\hypertarget{experimental-procedures}{%
\section{EXPERIMENTAL PROCEDURES}\label{experimental-procedures}}

\hypertarget{section-2}{%
\section{}\label{section-2}}

\textbf{Computing}

All machine learning and, feature selection and hyperparameter
optimization algorithms were implemented in Python. The Scikit-learn
library was used for training models, the
Yellowbrick\textsuperscript{29} library was utilized for visualization.
All code is available at
\url{https://github.com/LilianDenzler/qualiloop} .

The code was run under CentOS 7 on an 8-core virtual machine on an Intel
Xeon 4208 CPU with 16Gig RAM.

\begin{longtable}[]{@{}lll@{}}
\toprule
Feature Name & Description & Method of Calculation\tabularnewline
\midrule
\endhead
Sequence & Amino acid sequence of the CDR-H3 loop. & Sequence is given
in one-letter amino acid codes.\tabularnewline
Length & Number of residues in the CDRH3-loop, which is located at
residues H95-H102. & The number of residues are counted.\tabularnewline
Sequence identity & Sequence identity of selected template (SeqA) with
input loop sequence (SeqB)) is determined after sequence alignment.
Calculated by abYmod during modelling. &
\(\text{Identity}\left( \text{Seq}A,SeqB \right) = 100\%*\frac{\text{identical\ residues}}{length(alignment)}\)\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\raggedright
Sequence similarity\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
Sequence similarity of selected template (SeqA) with input loop sequence
(SeqB) is determined after sequence alignment. Calculated by abYmod
during modelling.

Similar residues are residues that have undergone conservative
substitution.\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
\[\text{Simialrity}\left( \text{Seq}A,SeqB \right) = 100\%*\frac{identical\ residues + similar\ residues}{length(alignment)}\]\strut
\end{minipage}\tabularnewline
Loop protrusion & Distance of loop residue further away from the loop
base. & Geometrical calculations, see \emph{fig. 8}\tabularnewline
Protruding residue & The amino acid code of the most protruding loop
residue & Using the previously determined point furthest away from the
loop base, the residue at this coordinate is determined and given as a
one-letter amino acid code.\tabularnewline
Charge & Total charge of the loop & Sum of charges of all residues in
loop\tabularnewline
Charge difference & Difference in total charge compared to template
sequence & Difference between the two summed charges\tabularnewline
Hydrophobicity & Mean of hydrophobicity values of loop & Based Eisenberg
consensus values\textsuperscript{30}\tabularnewline
Hydrophobicity difference & Sum of absolute differences between loop
sequence and template loop & Based Eisenberg consensus
values\textsuperscript{30}\tabularnewline
Accessibility & Total and average accessibility for the loop. &
Lee-Richards method \textsuperscript{31} implemented using the pdbsolv
method from the BiopTools library \textsuperscript{32}\tabularnewline
Side-chain Accessibility & Total and average side-chain accessibility
for the loop. & Lee-Richards method \textsuperscript{31} implemented
using the pdbsolv method from the BiopTools library
\textsuperscript{32}\tabularnewline
Relative Accessibility & Total and average relative accessibility for
the loop. & Lee-Richards method \textsuperscript{31} implemented using
the pdbsolv method from the BiopTools library
\textsuperscript{32}\tabularnewline
Relative side-chain accessibility & Total and average relative
side-chain accessibility for the loop. & Lee-Richards method
\textsuperscript{31} implemented using the pdbsolv method from the
BiopTools library \textsuperscript{32}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\raggedright
Happiness\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
Happiness score, taking accessibility and hydrophobicity into account.
If a residue is `happy' it will not be a buried hydrophilic or a surface
hydrophobic residue.\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
Hydrophobicity values (see above) are normalized to a range of -1 to +1.
Mean accessibility values are calculated as above.

If Hydrophobicity of loop is \textless0:

\[Happiness = 1 + (Hydrophobicity*(1 - Accessibility)\]

Otherwise:

\[Happiness = 1 - (Hydrophobicity*Accessibility)\]\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\textbf{Feature Calculations}

\begin{longtable}[]{@{}lll@{}}
\toprule
\begin{minipage}[b]{0.30\columnwidth}\raggedright
Nr. Of contacts\strut
\end{minipage} & \begin{minipage}[b]{0.30\columnwidth}\raggedright
Nr of contacts made by the residue of the loop within a range of 3.5Å.
Includes mainchain as well as sidechain atoms. Contacts made with
residue within and outside of the loop are counted separately and as
total.

The ratio of inside vs outside is also calculated.\strut
\end{minipage} & \begin{minipage}[b]{0.30\columnwidth}\raggedright
Modified version of the rangecontacts method in the BiopTools library
\textsuperscript{32}.\strut
\end{minipage}\tabularnewline
\midrule
\endhead
Energy & Potential energy of the model. & Calculated by
Gromacs\textsuperscript{33} during energy minimization step in abYmod
modelling.\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\raggedright
Lowest BLOSUM 62 Scoring Residue Pair\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
Each possible residue pair in the CDR-H3 loop is scored by their BLOSUM
62 score. The lowest scoring pair's BLOSUM62 value will be combined with
their residue separation to form the metric.\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
With separation being the number of residues between the worst residue
pair, and the worst score being the lowest BLOSUM62 score achieved by a
residue pair, the metric is calculated as follows:

\[WorstBLOSUM = - \log_{2}\left( \text{separation} \right)*worst\ score\ \]\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\includegraphics[width=6.47569in,height=2.2744in]{media/image18.png}

\textbf{Data Pre-Processing and Preparation}

{\emph{Handling Null Values and Duplicates}\textbf{: }}The dataset
containing target RMSD values, and the calculated features was screened
for null values. If a feature column contained more than 5\% null
values, it was dropped (none removed). Rows that contained any null
values were removed from the dataset (11 rows in total).

{Duplicate Screening}: Using AbDb's redundancy information it was
ensured that no antibodies were present in the dataset more than once.
The dataset is additionally screened for duplicate instances.

{Scaling:} Normalization and Standardization are tested as scaling
methods. Both approaches are greatly influenced by outliers, and such
datapoints are ideally removed for optimal scaling. Here we define
outliers as datapoints that lie over 1.5 times the interquartile range
(IQR) below the first quartile or above the third

quartile. The IQR is defined as the range between quartile 1, i.e. the
median of the lower half of the data, and quartile 3, i.e. the median of
the upper half of the

data. However, across all features there are a total of 632 outlier
values and removing such a large number of datapoints is not a viable
option. A robust scaler was also used, which uses statistics that are
robust to outliers. The median is set to zero and numerical features are
scaled to the interquartile range.

{BLOSUM 62 encoding:} The BLOSUM62 matrix reflects the frequencies of
amino acid substitutions within a locally aligned, conserved regions of
proteins with at least 62\% similarity. Each amino acid is represented
by a row (or column) of the BLOSUM62 matrix. Dimensionality reduction
techniques are employed: Principal Component Analysis (PCA), Independent
Component Analysis (ICA), projection-based methods (t-SNE, Isomap).
Three components were used as features.

{Physiochemical Feature Encoding\emph{:}} In a paper by L. Nanni and
A.Lumini a new encoding technique is

presented which was developed for machine learning classifiers. Many
physiochemical properties are calculated and transformed using a
non-linear Fisher transform for dimensionality reduction. A vector of
length 19 is produced for each amino acid\textsuperscript{34}.

In a paper on designing a neural network for predicting the packing
angle of the light and heavy variable chain of an antibodies, A.C.R.
Martin and K.R. Abhinandan introduce an encoding method that produces a
four-dimensional physiochemical feature vector\textsuperscript{25}. The
amino acid properties used are 1) the total number of side-chain atoms,
2) the number of side-chain atoms in the shortest path from Cα to the
most distal atom, 3) the Eisenberg consensus
hydrophobicity\textsuperscript{30}, 4) the charge.

\textbf{Dataset-splitting}: The final model was evaluated using a test
set, separated from the training set at the start in a 30/70 split
(lock-box principle) \textsuperscript{35}. The performance of all
individual sub-models of the first layer are determined using stratified
K-folds cross-validation (k=10) as the dataset is imbalanced, being
skewed towards lower RMSD values. The method is differentiable from
K-folds cross validation as it uses stratified sampling instead of
random sampling. This ensures each class is represented, as the
percentage of samples for each class are preserved.

A validation set, usually used for testing during the optimization stage
will be omitted in favour of stratified K-folds cross-validation (k=10)
\textsuperscript{36,37}.

\textbf{Model Assessment:} Model assessment must be considered at two
levels as performance metrics of binary and multi-class classifiers are
calculated differently and must thus be considered separately. The
Mathews Correlation Coefficient (MCC) \textsuperscript{38} is deemed the
most informative, taking the ratios of the four confusion matrix
categories into account \textsuperscript{39}and is thus more reliable
than the F1 score and accuracy . It is also consistent for both binary
and multi-class problems and therefore well suited for our purpose.

\hypertarget{section-3}{%
\section{}\label{section-3}}

\hypertarget{section-4}{%
\section{\texorpdfstring{\protect\includegraphics[width=3.66667in,height=3.35694in]{media/image19.png}}{}}\label{section-4}}

\hypertarget{section-5}{%
\section{}\label{section-5}}

\hypertarget{section-6}{%
\section{}\label{section-6}}

\hypertarget{section-7}{%
\section{}\label{section-7}}

\hypertarget{section-8}{%
\section{}\label{section-8}}

\hypertarget{section-9}{%
\section{}\label{section-9}}

\hypertarget{section-10}{%
\section{}\label{section-10}}

\hypertarget{section-11}{%
\section{}\label{section-11}}

\hypertarget{section-12}{%
\section{}\label{section-12}}

\hypertarget{section-13}{%
\section{}\label{section-13}}

\hypertarget{section-14}{%
\section{}\label{section-14}}

\hypertarget{section-15}{%
\section{}\label{section-15}}

\hypertarget{section-16}{%
\section{}\label{section-16}}

\hypertarget{section-17}{%
\section{}\label{section-17}}

\hypertarget{section-18}{%
\section{}\label{section-18}}

\hypertarget{section-19}{%
\section{}\label{section-19}}

\hypertarget{section-20}{%
\section{}\label{section-20}}

\hypertarget{section-21}{%
\section{}\label{section-21}}

\hypertarget{section-22}{%
\section{}\label{section-22}}

\hypertarget{section-23}{%
\section{}\label{section-23}}

\hypertarget{section-24}{%
\section{}\label{section-24}}

\hypertarget{section-25}{%
\section{}\label{section-25}}

\hypertarget{references}{%
\section{REFERENCES}\label{references}}

\hypertarget{section-26}{%
\section{}\label{section-26}}

\hypertarget{charles-a-janeway-j.-travers-p.-walport-m.-shlomchik-m.-j.-the-interaction-of-the-antibody-molecule-with-specific-antigen.-immunobiology-the-immune-system-in-health-and-disease.-garland-science-2001.2.-lu-r.-m.-et-al.-development-of-therapeutic-antibodies-for-the-treatment-of-diseases.-journal-of-biomedical-science-vol.-27-130-2020.3.-antibodies-market-size-share-trends-growth-forecast-2020-to-2025.-httpswww.marketdataforecast.commarket-reportsantibodies-market.4.-urquhart-l.-top-companies-and-drugs-by-sales-in-2020.-nat.-rev.-drug-discov.-2021-doi10.1038d41573-021-00050-6.5.-abhinandan-k.-r.-martin-a.-c.-r.-analyzing-the-degree-of-humanness-of-antibody-sequences.-j.-mol.-biol.-369-852862-2007.6.-north-b.-lehmann-a.-dunbrack-r.-l.-a-new-clustering-of-antibody-cdr-loop-conformations.-j.-mol.-biol.-406-228256-2011.7.-weitzner-b.-d.-dunbrack-r.-l.-gray-j.-j.-the-origin-of-cdr-h3-structural-diversity.-structure-23-302311-2015.8.-finn-j.-a.-et-al.-improving-loop-modeling-of-the-antibody-complementarity-determining-region-3-using-knowledge-based-restraints.-plos-one-11-e0154811-2016.9.-regep-c.-georges-g.-shi-j.-popovic-b.-deane-c.-m.-the-h3-loop-of-antibodies-shows-unique-structural-characteristics.-proteins-struct.-funct.-bioinforma.-85-13111318-2017.10.-maccallum-r.-m.-martin-a.-c.-r.-thornton-j.-m.-antibody-antigen-interactions-contact-analysis-and-binding-site-topography.-j.-mol.-biol.-262-732745-1996.11.-xu-j.-l.-davis-m.-m.-diversity-in-the-cdr3-region-of-vh-is-sufficient-for-most-antibody-specificities.-immunity-13-3745-2000.12.-kabat-e.-wu-t.-te-perry-h.-foeller-c.-gottesman-k.-sequences-of-proteins-of-immunological-interest.-1992.13.-almagro-j.-c.-et-al.-second-antibody-modeling-assessment-ama-ii.-proteins-structure-function-and-bioinformatics-vol.-82-15531562-2014.14.-almagro-j.-c.-et-al.-antibody-modeling-assessment.-proteins-struct.-funct.-bioinforma.-79-30503066-2011.15.-sircar-a.-kim-e.-t.-gray-j.-j.-rosettaantibody-antibody-variable-region-homology-modeling-server.-nucleic-acids-res.-37-w474w479-2009.16.-sivasubramanian-a.-sircar-a.-chaudhury-s.-gray-j.-j.-toward-high-resolution-homology-modeling-of-antibody-f-v-regions-and-application-to-antibody-antigen-docking.-proteins-struct.-funct.-bioinforma.-74-497514-2009.17.-leem-j.-dunbar-j.-georges-g.-shi-j.-deane-c.-m.-abodybuilder-automated-antibody-structure-prediction-with-datadriven-accuracy-estimation.-mabs-8-12591268-2016.18.-lepore-r.-olimpieri-p.-p.-messih-m.-a.-tramontano-a.-pigspro-prediction-of-immunoglobulin-structures-v2.-nucleic-acids-res.-45-w17w23-2017.19.-schoeder-c.-t.-et-al.-modeling-immunity-with-rosetta-methods-for-antibody-and-antigen-design.-60.20.-weitzner-b.-d.-gray-j.-j.-accurate-structure-prediction-of-cdr-h3-loops-enabled-by-a-novel-structure-based-c-terminal-constraint.-j.-immunol.-198-505515-2017.21.-choi-y.-deane-c.-m.-fread-revisited-accurate-loop-structure-prediction-using-a-database-search-algorithm.-proteins-struct.-funct.-bioinforma.-78-14311440-2010.22.-martin-a.-c.-r.-thornton-j.-m.-structural-families-in-loops-of-homologous-proteins-automatic-classification-modelling-and-application-to-antibodies.-j.-mol.-biol.-263-800815-1996.23.-almagro-j.-c.-et-al.-antibody-modeling-assessment.-proteins-struct.-funct.-bioinforma.-79-30503066-2011.24.-ferdous-s.-martin-a.-c.-r.-abdb-antibody-structure-databasea-database-of-pdb-derived-antibody-structures.-database-2018-2018.25.-abhinandan-k.-r.-martin-a.-c.-r.-analysis-and-prediction-of-vhvl-packing-in-antibodies.-protein-eng.-des.-sel.-23-689697-2010.26.-thomsen-m.-c.-f.-nielsen-m.-seq2logo-a-method-for-construction-and-visualization-of-amino-acid-binding-motifs-and-sequence-profiles-including-sequence-weighting-pseudo-counts-and-two-sided-representation-of-amino-acid-enrichment-and-depletion.-nucleic-acids-res.-40-2012.27.-shaner-m.-c.-blairs-i.-m.-schneider-t.-d.-sequence-logos-a-powerful-yet-simple-tool.28.-chen-t.-guestrin-c.-xgboost-a-scalable-tree-boosting-system.-in-proceedings-of-the-acm-sigkdd-international-conference-on-knowledge-discovery-and-data-mining-vols-13-17-august-2016-785794-association-for-computing-machinery-2016.29.-bengfort-b.-et-al.-yellowbrick-v1.3.-2021-doi10.5281zenodo.4525724.30.-eisenberg-d.-weiss-r.-m.-terwilliger-t.-c.-wilcox-w.-hydrophobic-moments-and-protein-structure.-in-faraday-symposia-of-the-chemical-society-vol.-17-109120-the-royal-society-of-chemistry-1982.31.-lee-b.-richards-f.-m.-the-interpretation-of-protein-structures-estimation-of-static-accessibility.-j.-mol.-biol.-55-379-in4-1971.32.-porter-c.-t.-martin-a.-c.-r.-bioplib-and-bioptools---a-c-programming-library-and-toolset-for-manipulating-protein-structure.-bioinformatics-31-40174019-2015.33.-van-der-spoel-d.-et-al.-gromacs-fast-flexible-and-free.-j.-comput.-chem.-26-17011718-2005.34.-nanni-l.-lumini-a.-a-new-encoding-technique-for-peptide-classification.-expert-syst.-appl.-38-31853191-2011.35.-wong-t.-t.-performance-evaluation-of-classification-algorithms-by-k-fold-and-leave-one-out-cross-validation.-pattern-recognit.-48-28392846-2015.36.-krstajic-d.-buturovic-l.-j.-leahy-d.-e.-thomas-s.-cross-validation-pitfalls-when-selecting-and-assessing-regression-and-classification-models.-j.-cheminform.-6-10-2014.37.-kohavi-r.-a-study-of-cross-validation-and-bootstrap-for-accuracy-estimation-and-model-selection.-httprobotics.stanford.eduronnyk-1995.38.-structure-b.-m.-b.-et-b.-a.-bba-p.-1975-undefined.-comparison-of-the-predicted-and-observed-secondary-structure-of-t4-phage-lysozyme.-elsevier.39.-chicco-d.-ten-quick-tips-for-machine-learning-in-computational-biology.-biodata-mining-vol.-10-35-2017.40.-morris-j.-the-precise-effect-of-multicollinearity-on-classification-prediction-ridge-regression-view-project-curriculum-based-vam-view-project.-httpswww.researchgate.netpublication336561703-2014.41.-handling-multi-collinearity-in-ml-models-by-vishwa-pardeshi-towards-data-science.-httpstowardsdatascience.comhandling-multi-collinearity-6579eb99fd81.42.-jin-lee-c.-park-c.-s.-seok-kim-j.-baek-j.-g.-a-study-on-improving-classification-performance-for-manufacturing-process-data-with-multicollinearity-and-imbalanced-distribution.-41-2533-2015.43.-box-p.-o.-van-der-maaten-l.-postma-e.-van-den-herik-j.-tilburg-centre-for-creative-computing-dimensionality-reduction-a-comparative-review-dimensionality-reduction-a-comparative-review.-httpwww.uvt.nlticc-2009.44.-vlachos-m.-et-al.-non-linear-dimensionality-reduction-techniques-for-classification-and-visualization.-2002.45.-sorzano-c.-o.-s.-vargas-j.-pascual-montano-a.-a-survey-of-dimensionality-reduction-techniques.46.-rifai-s.-vincent-p.-muller-x.-glorot-x.-bengio-y.-contractive-auto-encoders-explicit-invariance-during-feature-extraction.-2011.47.-chicco-d.-jurman-g.-the-advantages-of-the-matthews-correlation-coefficient-mcc-over-f1-score-and-accuracy-in-binary-classification-evaluation.-bmc-genomics-21-6-2020.48.-brown-j.-b.-classifiers-and-their-metrics-quantified.-mol.-inform.-37-1700127-2018.49.-delgado-r.-tibau-x.-a.-why-cohens-kappa-should-be-avoided-as-performance-measure-in-classification.-plos-one-14-e0222916-2019.50.-gorodkin-j.-comparing-two-k-category-assignments-by-a-k-category-correlation-coefficient.-comput.-biol.-chem.-28-367374-2004.51.-wong-w.-k.-leem-j.-deane-c.-m.-comparative-analysis-of-the-cdr-loops-of-antigen-receptors-protein-structure-prediction-view-project-comparative-analysis-of-the-cdr-loops-of-antigen.-doi10.1101709840.}{%
\section{\texorpdfstring{1. Charles A Janeway, J., Travers, P., Walport,
M. \& Shlomchik, M. J. \emph{The interaction of the antibody molecule
with specific antigen}. \emph{Immunobiology: The Immune System in Health
and Disease.} (Garland Science, 2001).2. Lu, R. M. \emph{et al.}
Development of therapeutic antibodies for the treatment of diseases.
\emph{Journal of Biomedical Science} vol. 27 1--30 (2020).3. Antibodies
Market Size, Share Trends, Growth, Forecast \textbar{} 2020 to 2025.
https://www.marketdataforecast.com/market-reports/antibodies-market.4.
Urquhart, L. Top companies and drugs by sales in 2020. \emph{Nat. Rev.
Drug Discov.} (2021) doi:10.1038/d41573-021-00050-6.5. Abhinandan, K. R.
\& Martin, A. C. R. Analyzing the `Degree of Humanness' of Antibody
Sequences. \emph{J. Mol. Biol.} \textbf{369}, 852--862 (2007).6. North,
B., Lehmann, A. \& Dunbrack, R. L. A new clustering of antibody CDR loop
conformations. \emph{J. Mol. Biol.} \textbf{406}, 228--256 (2011).7.
Weitzner, B. D., Dunbrack, R. L. \& Gray, J. J. The origin of CDR H3
structural diversity. \emph{Structure} \textbf{23}, 302--311 (2015).8.
Finn, J. A. \emph{et al.} Improving Loop Modeling of the Antibody
Complementarity-Determining Region 3 Using Knowledge-Based Restraints.
\emph{PLoS One} \textbf{11}, e0154811 (2016).9. Regep, C., Georges, G.,
Shi, J., Popovic, B. \& Deane, C. M. The H3 loop of antibodies shows
unique structural characteristics. \emph{Proteins Struct. Funct.
Bioinforma.} \textbf{85}, 1311--1318 (2017).10. MacCallum, R. M.,
Martin, A. C. R. \& Thornton, J. M. Antibody-antigen interactions:
Contact analysis and binding site topography. \emph{J. Mol. Biol.}
\textbf{262}, 732--745 (1996).11. Xu, J. L. \& Davis, M. M. Diversity in
the CDR3 region of V(H) is sufficient for most antibody specificities.
\emph{Immunity} \textbf{13}, 37--45 (2000).12. Kabat, E., Wu, T. Te,
Perry, H., Foeller, C. \& Gottesman, K. Sequences of proteins of
immunological interest. (1992).13. Almagro, J. C. \emph{et al.} Second
Antibody Modeling Assessment (AMA-II). \emph{Proteins: Structure,
Function and Bioinformatics} vol. 82 1553--1562 (2014).14. Almagro, J.
C. \emph{et al.} Antibody modeling assessment. \emph{Proteins Struct.
Funct. Bioinforma.} \textbf{79}, 3050--3066 (2011).15. Sircar, A., Kim,
E. T. \& Gray, J. J. RosettaAntibody: Antibody variable region homology
modeling server. \emph{Nucleic Acids Res.} \textbf{37}, W474--W479
(2009).16. Sivasubramanian, A., Sircar, A., Chaudhury, S. \& Gray, J. J.
Toward high-resolution homology modeling of antibody F \textsubscript{v}
regions and application to antibody-antigen docking. \emph{Proteins
Struct. Funct. Bioinforma.} \textbf{74}, 497--514 (2009).17. Leem, J.,
Dunbar, J., Georges, G., Shi, J. \& Deane, C. M. ABodyBuilder: Automated
antibody structure prediction with data--driven accuracy estimation.
\emph{MAbs} \textbf{8}, 1259--1268 (2016).18. Lepore, R., Olimpieri, P.
P., Messih, M. A. \& Tramontano, A. PIGSPro: Prediction of
immunoGlobulin structures v2. \emph{Nucleic Acids Res.} \textbf{45},
W17--W23 (2017).19. Schoeder, C. T. \emph{et al.} Modeling Immunity with
Rosetta: Methods for Antibody and Antigen Design. \textbf{60},.20.
Weitzner, B. D. \& Gray, J. J. Accurate Structure Prediction of CDR H3
Loops Enabled by a Novel Structure-Based C-Terminal Constraint. \emph{J.
Immunol.} \textbf{198}, 505--515 (2017).21. Choi, Y. \& Deane, C. M.
FREAD revisited: Accurate loop structure prediction using a database
search algorithm. \emph{Proteins Struct. Funct. Bioinforma.}
\textbf{78}, 1431--1440 (2010).22. Martin, A. C. R. \& Thornton, J. M.
Structural families in loops of homologous proteins: Automatic
classification, modelling and application to antibodies. \emph{J. Mol.
Biol.} \textbf{263}, 800--815 (1996).23. Almagro, J. C. \emph{et al.}
Antibody modeling assessment. \emph{Proteins Struct. Funct. Bioinforma.}
\textbf{79}, 3050--3066 (2011).24. Ferdous, S. \& Martin, A. C. R. AbDb:
antibody structure database---a database of PDB-derived antibody
structures. \emph{Database} \textbf{2018}, (2018).25. Abhinandan, K. R.
\& Martin, A. C. R. Analysis and prediction of VH/VL packing in
antibodies. \emph{Protein Eng. Des. Sel.} \textbf{23}, 689--697
(2010).26. Thomsen, M. C. F. \& Nielsen, M. Seq2Logo: A method for
construction and visualization of amino acid binding motifs and sequence
profiles including sequence weighting, pseudo counts and two-sided
representation of amino acid enrichment and depletion. \emph{Nucleic
Acids Res.} \textbf{40}, (2012).27. Shaner, M. C., Blair's, I. M. \&
Schneider, T. D. \emph{Sequence Logos: A Powerful, Yet Simple, Tool}.28.
Chen, T. \& Guestrin, C. XGBoost: A scalable tree boosting system. in
\emph{Proceedings of the ACM SIGKDD International Conference on
Knowledge Discovery and Data Mining} vols 13-17-August-2016 785--794
(Association for Computing Machinery, 2016).29. Bengfort, B. \emph{et
al.} Yellowbrick v1.3. (2021) doi:10.5281/ZENODO.4525724.30. Eisenberg,
D., Weiss, R. M., Terwilliger, T. C. \& Wilcox, W. Hydrophobic moments
and protein structure. in \emph{Faraday Symposia of the Chemical
Society} vol. 17 109--120 (The Royal Society of Chemistry, 1982).31.
Lee, B. \& Richards, F. M. The interpretation of protein structures:
Estimation of static accessibility. \emph{J. Mol. Biol.} \textbf{55},
379-IN4 (1971).32. Porter, C. T. \& Martin, A. C. R. BiopLib and
BiopTools - A C programming library and toolset for manipulating protein
structure. \emph{Bioinformatics} \textbf{31}, 4017--4019 (2015).33. Van
Der Spoel, D. \emph{et al.} GROMACS: Fast, flexible, and free. \emph{J.
Comput. Chem.} \textbf{26}, 1701--1718 (2005).34. Nanni, L. \& Lumini,
A. A new encoding technique for peptide classification. \emph{Expert
Syst. Appl.} \textbf{38}, 3185--3191 (2011).35. Wong, T. T. Performance
evaluation of classification algorithms by k-fold and leave-one-out
cross validation. \emph{Pattern Recognit.} \textbf{48}, 2839--2846
(2015).36. Krstajic, D., Buturovic, L. J., Leahy, D. E. \& Thomas, S.
Cross-validation pitfalls when selecting and assessing regression and
classification models. \emph{J. Cheminform.} \textbf{6}, 10 (2014).37.
Kohavi, R. \emph{A Study of Cross-Validation and Bootstrap for Accuracy
Estimation and Model Selection}.
http://robotics.stanford.edu/\textasciitilde ronnyk (1995).38.
Structure, B. M.-B. et B. A. (BBA)-P. \& 1975, undefined. Comparison of
the predicted and observed secondary structure of T4 phage lysozyme.
\emph{Elsevier}.39. Chicco, D. Ten quick tips for machine learning in
computational biology. \emph{BioData Mining} vol. 10 35 (2017).40.
Morris, J. \emph{The Precise Effect of Multicollinearity on
Classification Prediction Ridge Regression View project Curriculum-Based
VAM View project}. https://www.researchgate.net/publication/336561703
(2014).41. Handling Multi-Collinearity in ML Models \textbar{} by Vishwa
Pardeshi \textbar{} Towards Data Science.
https://towardsdatascience.com/handling-multi-collinearity-6579eb99fd81.42.
Jin Lee, C., Park, C.-S., Seok Kim, J. \& Baek, J.-G. A Study on
Improving Classification Performance for Manufacturing Process Data with
Multicollinearity and Imbalanced Distribution. \textbf{41}, 25--33
(2015).43. Box, P. O., Van Der Maaten, L., Postma, E. \& Van Den Herik,
J. \emph{Tilburg centre for Creative Computing Dimensionality Reduction:
A Comparative Review Dimensionality Reduction: A Comparative Review}.
http://www.uvt.nl/ticc (2009).44. Vlachos, M. \emph{et al.}
\emph{Non-Linear Dimensionality Reduction Techniques for Classification
and Visualization}. (2002).45. Sorzano, C. O. S., Vargas, J. \&
Pascual-Montano, A. \emph{A survey of dimensionality reduction
techniques}.46. Rifai, S., Vincent, P., Muller, X., Glorot, X. \&
Bengio, Y. \emph{Contractive Auto-Encoders: Explicit Invariance During
Feature Extraction}. (2011).47. Chicco, D. \& Jurman, G. The advantages
of the Matthews correlation coefficient (MCC) over F1 score and accuracy
in binary classification evaluation. \emph{BMC Genomics} \textbf{21}, 6
(2020).48. Brown, J. B. Classifiers and their Metrics Quantified.
\emph{Mol. Inform.} \textbf{37}, 1700127 (2018).49. Delgado, R. \&
Tibau, X. A. Why Cohen's Kappa should be avoided as performance measure
in classification. \emph{PLoS One} \textbf{14}, e0222916 (2019).50.
Gorodkin, J. Comparing two K-category assignments by a K-category
correlation coefficient. \emph{Comput. Biol. Chem.} \textbf{28},
367--374 (2004).51. Wong, W. K., Leem, J. \& Deane, C. M. Comparative
analysis of the CDR loops of antigen receptors Protein structure
prediction View project Comparative analysis of the CDR loops of
antigen.
doi:10.1101/709840.}{1. Charles A Janeway, J., Travers, P., Walport, M. \& Shlomchik, M. J. The interaction of the antibody molecule with specific antigen. Immunobiology: The Immune System in Health and Disease. (Garland Science, 2001).2. Lu, R. M. et al. Development of therapeutic antibodies for the treatment of diseases. Journal of Biomedical Science vol. 27 1--30 (2020).3. Antibodies Market Size, Share Trends, Growth, Forecast \textbar{} 2020 to 2025. https://www.marketdataforecast.com/market-reports/antibodies-market.4. Urquhart, L. Top companies and drugs by sales in 2020. Nat. Rev. Drug Discov. (2021) doi:10.1038/d41573-021-00050-6.5. Abhinandan, K. R. \& Martin, A. C. R. Analyzing the `Degree of Humanness' of Antibody Sequences. J. Mol. Biol. 369, 852--862 (2007).6. North, B., Lehmann, A. \& Dunbrack, R. L. A new clustering of antibody CDR loop conformations. J. Mol. Biol. 406, 228--256 (2011).7. Weitzner, B. D., Dunbrack, R. L. \& Gray, J. J. The origin of CDR H3 structural diversity. Structure 23, 302--311 (2015).8. Finn, J. A. et al. Improving Loop Modeling of the Antibody Complementarity-Determining Region 3 Using Knowledge-Based Restraints. PLoS One 11, e0154811 (2016).9. Regep, C., Georges, G., Shi, J., Popovic, B. \& Deane, C. M. The H3 loop of antibodies shows unique structural characteristics. Proteins Struct. Funct. Bioinforma. 85, 1311--1318 (2017).10. MacCallum, R. M., Martin, A. C. R. \& Thornton, J. M. Antibody-antigen interactions: Contact analysis and binding site topography. J. Mol. Biol. 262, 732--745 (1996).11. Xu, J. L. \& Davis, M. M. Diversity in the CDR3 region of V(H) is sufficient for most antibody specificities. Immunity 13, 37--45 (2000).12. Kabat, E., Wu, T. Te, Perry, H., Foeller, C. \& Gottesman, K. Sequences of proteins of immunological interest. (1992).13. Almagro, J. C. et al. Second Antibody Modeling Assessment (AMA-II). Proteins: Structure, Function and Bioinformatics vol. 82 1553--1562 (2014).14. Almagro, J. C. et al. Antibody modeling assessment. Proteins Struct. Funct. Bioinforma. 79, 3050--3066 (2011).15. Sircar, A., Kim, E. T. \& Gray, J. J. RosettaAntibody: Antibody variable region homology modeling server. Nucleic Acids Res. 37, W474--W479 (2009).16. Sivasubramanian, A., Sircar, A., Chaudhury, S. \& Gray, J. J. Toward high-resolution homology modeling of antibody F v regions and application to antibody-antigen docking. Proteins Struct. Funct. Bioinforma. 74, 497--514 (2009).17. Leem, J., Dunbar, J., Georges, G., Shi, J. \& Deane, C. M. ABodyBuilder: Automated antibody structure prediction with data--driven accuracy estimation. MAbs 8, 1259--1268 (2016).18. Lepore, R., Olimpieri, P. P., Messih, M. A. \& Tramontano, A. PIGSPro: Prediction of immunoGlobulin structures v2. Nucleic Acids Res. 45, W17--W23 (2017).19. Schoeder, C. T. et al. Modeling Immunity with Rosetta: Methods for Antibody and Antigen Design. 60,.20. Weitzner, B. D. \& Gray, J. J. Accurate Structure Prediction of CDR H3 Loops Enabled by a Novel Structure-Based C-Terminal Constraint. J. Immunol. 198, 505--515 (2017).21. Choi, Y. \& Deane, C. M. FREAD revisited: Accurate loop structure prediction using a database search algorithm. Proteins Struct. Funct. Bioinforma. 78, 1431--1440 (2010).22. Martin, A. C. R. \& Thornton, J. M. Structural families in loops of homologous proteins: Automatic classification, modelling and application to antibodies. J. Mol. Biol. 263, 800--815 (1996).23. Almagro, J. C. et al. Antibody modeling assessment. Proteins Struct. Funct. Bioinforma. 79, 3050--3066 (2011).24. Ferdous, S. \& Martin, A. C. R. AbDb: antibody structure database---a database of PDB-derived antibody structures. Database 2018, (2018).25. Abhinandan, K. R. \& Martin, A. C. R. Analysis and prediction of VH/VL packing in antibodies. Protein Eng. Des. Sel. 23, 689--697 (2010).26. Thomsen, M. C. F. \& Nielsen, M. Seq2Logo: A method for construction and visualization of amino acid binding motifs and sequence profiles including sequence weighting, pseudo counts and two-sided representation of amino acid enrichment and depletion. Nucleic Acids Res. 40, (2012).27. Shaner, M. C., Blair's, I. M. \& Schneider, T. D. Sequence Logos: A Powerful, Yet Simple, Tool.28. Chen, T. \& Guestrin, C. XGBoost: A scalable tree boosting system. in Proceedings of the ACM SIGKDD International Conference on Knowledge Discovery and Data Mining vols 13-17-August-2016 785--794 (Association for Computing Machinery, 2016).29. Bengfort, B. et al. Yellowbrick v1.3. (2021) doi:10.5281/ZENODO.4525724.30. Eisenberg, D., Weiss, R. M., Terwilliger, T. C. \& Wilcox, W. Hydrophobic moments and protein structure. in Faraday Symposia of the Chemical Society vol. 17 109--120 (The Royal Society of Chemistry, 1982).31. Lee, B. \& Richards, F. M. The interpretation of protein structures: Estimation of static accessibility. J. Mol. Biol. 55, 379-IN4 (1971).32. Porter, C. T. \& Martin, A. C. R. BiopLib and BiopTools - A C programming library and toolset for manipulating protein structure. Bioinformatics 31, 4017--4019 (2015).33. Van Der Spoel, D. et al. GROMACS: Fast, flexible, and free. J. Comput. Chem. 26, 1701--1718 (2005).34. Nanni, L. \& Lumini, A. A new encoding technique for peptide classification. Expert Syst. Appl. 38, 3185--3191 (2011).35. Wong, T. T. Performance evaluation of classification algorithms by k-fold and leave-one-out cross validation. Pattern Recognit. 48, 2839--2846 (2015).36. Krstajic, D., Buturovic, L. J., Leahy, D. E. \& Thomas, S. Cross-validation pitfalls when selecting and assessing regression and classification models. J. Cheminform. 6, 10 (2014).37. Kohavi, R. A Study of Cross-Validation and Bootstrap for Accuracy Estimation and Model Selection. http://robotics.stanford.edu/\textasciitilde ronnyk (1995).38. Structure, B. M.-B. et B. A. (BBA)-P. \& 1975, undefined. Comparison of the predicted and observed secondary structure of T4 phage lysozyme. Elsevier.39. Chicco, D. Ten quick tips for machine learning in computational biology. BioData Mining vol. 10 35 (2017).40. Morris, J. The Precise Effect of Multicollinearity on Classification Prediction Ridge Regression View project Curriculum-Based VAM View project. https://www.researchgate.net/publication/336561703 (2014).41. Handling Multi-Collinearity in ML Models \textbar{} by Vishwa Pardeshi \textbar{} Towards Data Science. https://towardsdatascience.com/handling-multi-collinearity-6579eb99fd81.42. Jin Lee, C., Park, C.-S., Seok Kim, J. \& Baek, J.-G. A Study on Improving Classification Performance for Manufacturing Process Data with Multicollinearity and Imbalanced Distribution. 41, 25--33 (2015).43. Box, P. O., Van Der Maaten, L., Postma, E. \& Van Den Herik, J. Tilburg centre for Creative Computing Dimensionality Reduction: A Comparative Review Dimensionality Reduction: A Comparative Review. http://www.uvt.nl/ticc (2009).44. Vlachos, M. et al. Non-Linear Dimensionality Reduction Techniques for Classification and Visualization. (2002).45. Sorzano, C. O. S., Vargas, J. \& Pascual-Montano, A. A survey of dimensionality reduction techniques.46. Rifai, S., Vincent, P., Muller, X., Glorot, X. \& Bengio, Y. Contractive Auto-Encoders: Explicit Invariance During Feature Extraction. (2011).47. Chicco, D. \& Jurman, G. The advantages of the Matthews correlation coefficient (MCC) over F1 score and accuracy in binary classification evaluation. BMC Genomics 21, 6 (2020).48. Brown, J. B. Classifiers and their Metrics Quantified. Mol. Inform. 37, 1700127 (2018).49. Delgado, R. \& Tibau, X. A. Why Cohen's Kappa should be avoided as performance measure in classification. PLoS One 14, e0222916 (2019).50. Gorodkin, J. Comparing two K-category assignments by a K-category correlation coefficient. Comput. Biol. Chem. 28, 367--374 (2004).51. Wong, W. K., Leem, J. \& Deane, C. M. Comparative analysis of the CDR loops of antigen receptors Protein structure prediction View project Comparative analysis of the CDR loops of antigen. doi:10.1101/709840.}}\label{charles-a-janeway-j.-travers-p.-walport-m.-shlomchik-m.-j.-the-interaction-of-the-antibody-molecule-with-specific-antigen.-immunobiology-the-immune-system-in-health-and-disease.-garland-science-2001.2.-lu-r.-m.-et-al.-development-of-therapeutic-antibodies-for-the-treatment-of-diseases.-journal-of-biomedical-science-vol.-27-130-2020.3.-antibodies-market-size-share-trends-growth-forecast-2020-to-2025.-httpswww.marketdataforecast.commarket-reportsantibodies-market.4.-urquhart-l.-top-companies-and-drugs-by-sales-in-2020.-nat.-rev.-drug-discov.-2021-doi10.1038d41573-021-00050-6.5.-abhinandan-k.-r.-martin-a.-c.-r.-analyzing-the-degree-of-humanness-of-antibody-sequences.-j.-mol.-biol.-369-852862-2007.6.-north-b.-lehmann-a.-dunbrack-r.-l.-a-new-clustering-of-antibody-cdr-loop-conformations.-j.-mol.-biol.-406-228256-2011.7.-weitzner-b.-d.-dunbrack-r.-l.-gray-j.-j.-the-origin-of-cdr-h3-structural-diversity.-structure-23-302311-2015.8.-finn-j.-a.-et-al.-improving-loop-modeling-of-the-antibody-complementarity-determining-region-3-using-knowledge-based-restraints.-plos-one-11-e0154811-2016.9.-regep-c.-georges-g.-shi-j.-popovic-b.-deane-c.-m.-the-h3-loop-of-antibodies-shows-unique-structural-characteristics.-proteins-struct.-funct.-bioinforma.-85-13111318-2017.10.-maccallum-r.-m.-martin-a.-c.-r.-thornton-j.-m.-antibody-antigen-interactions-contact-analysis-and-binding-site-topography.-j.-mol.-biol.-262-732745-1996.11.-xu-j.-l.-davis-m.-m.-diversity-in-the-cdr3-region-of-vh-is-sufficient-for-most-antibody-specificities.-immunity-13-3745-2000.12.-kabat-e.-wu-t.-te-perry-h.-foeller-c.-gottesman-k.-sequences-of-proteins-of-immunological-interest.-1992.13.-almagro-j.-c.-et-al.-second-antibody-modeling-assessment-ama-ii.-proteins-structure-function-and-bioinformatics-vol.-82-15531562-2014.14.-almagro-j.-c.-et-al.-antibody-modeling-assessment.-proteins-struct.-funct.-bioinforma.-79-30503066-2011.15.-sircar-a.-kim-e.-t.-gray-j.-j.-rosettaantibody-antibody-variable-region-homology-modeling-server.-nucleic-acids-res.-37-w474w479-2009.16.-sivasubramanian-a.-sircar-a.-chaudhury-s.-gray-j.-j.-toward-high-resolution-homology-modeling-of-antibody-f-v-regions-and-application-to-antibody-antigen-docking.-proteins-struct.-funct.-bioinforma.-74-497514-2009.17.-leem-j.-dunbar-j.-georges-g.-shi-j.-deane-c.-m.-abodybuilder-automated-antibody-structure-prediction-with-datadriven-accuracy-estimation.-mabs-8-12591268-2016.18.-lepore-r.-olimpieri-p.-p.-messih-m.-a.-tramontano-a.-pigspro-prediction-of-immunoglobulin-structures-v2.-nucleic-acids-res.-45-w17w23-2017.19.-schoeder-c.-t.-et-al.-modeling-immunity-with-rosetta-methods-for-antibody-and-antigen-design.-60.20.-weitzner-b.-d.-gray-j.-j.-accurate-structure-prediction-of-cdr-h3-loops-enabled-by-a-novel-structure-based-c-terminal-constraint.-j.-immunol.-198-505515-2017.21.-choi-y.-deane-c.-m.-fread-revisited-accurate-loop-structure-prediction-using-a-database-search-algorithm.-proteins-struct.-funct.-bioinforma.-78-14311440-2010.22.-martin-a.-c.-r.-thornton-j.-m.-structural-families-in-loops-of-homologous-proteins-automatic-classification-modelling-and-application-to-antibodies.-j.-mol.-biol.-263-800815-1996.23.-almagro-j.-c.-et-al.-antibody-modeling-assessment.-proteins-struct.-funct.-bioinforma.-79-30503066-2011.24.-ferdous-s.-martin-a.-c.-r.-abdb-antibody-structure-databasea-database-of-pdb-derived-antibody-structures.-database-2018-2018.25.-abhinandan-k.-r.-martin-a.-c.-r.-analysis-and-prediction-of-vhvl-packing-in-antibodies.-protein-eng.-des.-sel.-23-689697-2010.26.-thomsen-m.-c.-f.-nielsen-m.-seq2logo-a-method-for-construction-and-visualization-of-amino-acid-binding-motifs-and-sequence-profiles-including-sequence-weighting-pseudo-counts-and-two-sided-representation-of-amino-acid-enrichment-and-depletion.-nucleic-acids-res.-40-2012.27.-shaner-m.-c.-blairs-i.-m.-schneider-t.-d.-sequence-logos-a-powerful-yet-simple-tool.28.-chen-t.-guestrin-c.-xgboost-a-scalable-tree-boosting-system.-in-proceedings-of-the-acm-sigkdd-international-conference-on-knowledge-discovery-and-data-mining-vols-13-17-august-2016-785794-association-for-computing-machinery-2016.29.-bengfort-b.-et-al.-yellowbrick-v1.3.-2021-doi10.5281zenodo.4525724.30.-eisenberg-d.-weiss-r.-m.-terwilliger-t.-c.-wilcox-w.-hydrophobic-moments-and-protein-structure.-in-faraday-symposia-of-the-chemical-society-vol.-17-109120-the-royal-society-of-chemistry-1982.31.-lee-b.-richards-f.-m.-the-interpretation-of-protein-structures-estimation-of-static-accessibility.-j.-mol.-biol.-55-379-in4-1971.32.-porter-c.-t.-martin-a.-c.-r.-bioplib-and-bioptools---a-c-programming-library-and-toolset-for-manipulating-protein-structure.-bioinformatics-31-40174019-2015.33.-van-der-spoel-d.-et-al.-gromacs-fast-flexible-and-free.-j.-comput.-chem.-26-17011718-2005.34.-nanni-l.-lumini-a.-a-new-encoding-technique-for-peptide-classification.-expert-syst.-appl.-38-31853191-2011.35.-wong-t.-t.-performance-evaluation-of-classification-algorithms-by-k-fold-and-leave-one-out-cross-validation.-pattern-recognit.-48-28392846-2015.36.-krstajic-d.-buturovic-l.-j.-leahy-d.-e.-thomas-s.-cross-validation-pitfalls-when-selecting-and-assessing-regression-and-classification-models.-j.-cheminform.-6-10-2014.37.-kohavi-r.-a-study-of-cross-validation-and-bootstrap-for-accuracy-estimation-and-model-selection.-httprobotics.stanford.eduronnyk-1995.38.-structure-b.-m.-b.-et-b.-a.-bba-p.-1975-undefined.-comparison-of-the-predicted-and-observed-secondary-structure-of-t4-phage-lysozyme.-elsevier.39.-chicco-d.-ten-quick-tips-for-machine-learning-in-computational-biology.-biodata-mining-vol.-10-35-2017.40.-morris-j.-the-precise-effect-of-multicollinearity-on-classification-prediction-ridge-regression-view-project-curriculum-based-vam-view-project.-httpswww.researchgate.netpublication336561703-2014.41.-handling-multi-collinearity-in-ml-models-by-vishwa-pardeshi-towards-data-science.-httpstowardsdatascience.comhandling-multi-collinearity-6579eb99fd81.42.-jin-lee-c.-park-c.-s.-seok-kim-j.-baek-j.-g.-a-study-on-improving-classification-performance-for-manufacturing-process-data-with-multicollinearity-and-imbalanced-distribution.-41-2533-2015.43.-box-p.-o.-van-der-maaten-l.-postma-e.-van-den-herik-j.-tilburg-centre-for-creative-computing-dimensionality-reduction-a-comparative-review-dimensionality-reduction-a-comparative-review.-httpwww.uvt.nlticc-2009.44.-vlachos-m.-et-al.-non-linear-dimensionality-reduction-techniques-for-classification-and-visualization.-2002.45.-sorzano-c.-o.-s.-vargas-j.-pascual-montano-a.-a-survey-of-dimensionality-reduction-techniques.46.-rifai-s.-vincent-p.-muller-x.-glorot-x.-bengio-y.-contractive-auto-encoders-explicit-invariance-during-feature-extraction.-2011.47.-chicco-d.-jurman-g.-the-advantages-of-the-matthews-correlation-coefficient-mcc-over-f1-score-and-accuracy-in-binary-classification-evaluation.-bmc-genomics-21-6-2020.48.-brown-j.-b.-classifiers-and-their-metrics-quantified.-mol.-inform.-37-1700127-2018.49.-delgado-r.-tibau-x.-a.-why-cohens-kappa-should-be-avoided-as-performance-measure-in-classification.-plos-one-14-e0222916-2019.50.-gorodkin-j.-comparing-two-k-category-assignments-by-a-k-category-correlation-coefficient.-comput.-biol.-chem.-28-367374-2004.51.-wong-w.-k.-leem-j.-deane-c.-m.-comparative-analysis-of-the-cdr-loops-of-antigen-receptors-protein-structure-prediction-view-project-comparative-analysis-of-the-cdr-loops-of-antigen.-doi10.1101709840.}}

\textbf{APPENDIX}

\end{document}

### 2022-09-28 elsarticle-template-num.tex
Add files via upload

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%% 
%%
%% $Id: elsarticle-template-num.tex 190 2020-11-23 11:12:32Z rishi $
%%
%%
%Path relative to the .tex file containing the \includegraphics command

\documentclass[preprint,12pt]{elsarticle}
\usepackage{graphicx}
\graphicspath{ {./Images/} }
%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{XXXXX}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%% \fntext[label3]{}

\title{Predicting the Quality of CDRH3 Antibody Loop Structural Models}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

\author[inst1]{Lilian M Denzler}

\affiliation[inst1]{organization={Department of Structural and Molecular Biology, 
University College of London},%Department and Organization
            addressline={Gower Street}, 
            city={London},
            postcode={WC1E 6BT}, ,
            country={UK}}

\author[inst1]{Andrew CR Martin}

\begin{abstract}
%% Text of abstract
Therapeutic antibodies have shown an unprecedented pace of development and have brought new hope for the treatment of numerous diseases. The bioinformatic tools for modelling antibody structures have become invaluable for antibody engineering and the development of therapeutic antibodies. The antigen-binding site consists of six hypervariable loops, also known as the Complementary Determining Regions (CDR), all of which can be modelled with adequate accuracy, except for one. It remains markedly difficult to model the third CDR loop of the antibody heavy chain. The CDRH3 differs in length, has far greater sequence variability and has such a great structural diversity that modelling it is considerably harder. 
Many sophisticated approaches for antibody modelling, such as the abYmod software, have been developed. Although such efforts have improved prediction accuracy the results for the CDRH3 loop are still inconsistent and require further improvement. Providing a confidence score for the structure predictions would aid in differentiating well-modelled structures from incorrectly modelled structures, giving the abYmod user a clearer understanding of the generated model reliability. 
We present a model quality predictor, combining domain knowledge with machine learning techniques to predict the accuracy of CDRH3 models generated by antibody modelling software such as abYmod. The newly developed predictor scored a Mathews Correlation Coefficient of 0.99, and can thus be described as highly reliable. The predictor is made available at \url{http://www.bioinf.org.uk/abs/qualiloop/}.

\end{abstract}

%%Graphical abstract
%%\begin{graphicalabstract}
%%\includegraphics{grabs}
%%\end{graphicalabstract}

%%Research highlights
%%\begin{highlights}
%%\item Research highlight 1
%%\item Research highlight 2
%%\end{highlights}

%%\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%%keyword one \sep keyword two
%% PACS codes here, in the form: \PACS code \sep code
%%\PACS 0000 \sep 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%%\MSC 0000 \sep 1111
%%\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
\label{sec:sample1}
Antibodies are highly specialized proteins of the immune system that are produced in response to a foreign substance, called an antigen. A mature antibody binds a specific antigen with high affinity, while only weakly interacting with other antigens, or not at all. This high affinity, high specificity sets it apart from other pharmaceuticals. Furthermore, in contrast with small drug molecules, antibodies can not only bind pockets, but also flat, concave or even convex surfaces \cite{Tavers2001}. Their unique characteristics have enabled researchers to develop efficient antibody drugs for treating cancers, autoimmune disorders, infectious diseases and many more \cite{Lu2020}. Their ability to target an immense variety of antigens allows for endless possibilities in application. The global market size was valued at USD 130.9 billion in 2020, estimated to grow 223.7 billion by the end of 2025 at a compound annual growth rate of 11.31\% \cite{market2020}. Four of the top 10 best-selling drugs in 2020 were monoclonal antibodies \cite{Urquhart2021}.  
In order to rationally design therapeutic antibodies, knowledge of their structure is essential. The acquired structural information can be used to increase binding affinity to a target of interest, predicting both the exact binding site and the antibody stability as well as assessing immunogenicity \cite{Abhinandan2007}. As experimental structure determination is very costly and time consuming, computational predictions of an antibody’s structure are used to streamline the process.  
Antibodies consist of a heavy and a light chain, which are linked by disulphide bonds. The N-terminal domain of each makes up the variable fragment (Fv), which contains the complementarity determining regions (CDRs). The antigen binding site is composed of six CDRs, also known as hypervariable loops. All except one of these loops can be clustered into a limited number of canonical structures. Therefore, modelling these loops with adequate accuracy is commonly achievable \cite{North2011},\cite{Weitzner2015}. However, the CDR loop 3 of the heavy chain (CDRH3) has a far greater sequence variability due to the processes of V(D)J recombination and somatic hyper‐mutation and its structure has remained unclassifiable \cite{Finn2016}. The variety in structure is so great, that its structural diversity is remarkable even compared to other protein loops \cite{Regep2017}. It was found that over 75\% of CDRH3 loops do not have a sub-Angstrom non-antibody structural neighbour, as well as that 30\% of CDRH3 loops have a completely unique structure compared with under 3\% for all other loops on average \cite{Regep2017}. 
Apart from being the most structurally diverse, the H3 loop is also the most important for antigen binding, being located at the center of the binding site and forming the most contacts to the antigen \cite{MacCallum1996}. In fact, it was demonstrated that differences in this loop alone were sufficient to enable otherwise identical antibodies to distinguish between various antigens \cite{Xu2000}. 
 According to the Kabat definition, the CDRH3 loop is made up of the residues 95-105 (Kabat numbering scheme\cite{Kabat1992}) in the heavy chain, with a potential insertion site at position 100. The possibility of such an insertion of a varying number of residues leads to a large range of loop lengths, with bovine antibodies being exceptionally long \ref{fig:loopdist}.
\begin{figure}[h!]
  \includegraphics[scale=1]{loopdist.png}
  \centering
  \caption { Distribution of CDR-H3 loop lengths in mouse (left), human (centre) and cow (right). Mouse and human antibody CDRH3s have a unimodal, yet almost normal distribution with a range of ca. 4-28 and 4-38 respectively. The length cut-off for CDRH3s depicted above is 30 amino acids. Bovine antibodies with significantly longer CDR-H3 loops than depicted here exist, reaching a length of 67 amino acids and above. \cite{Wong2015}}
  \label{fig:loopdist}
\end{figure}

For shorter loops, a higher prediction accuracy can be achieved than for longer CDRH3 loops. This was also shown by the Antibody Modelling Assessments (AMA), two blind contests that required researchers to build structural models from antibody sequences. The CDR-H3 loop modelling quality achieved at the contests was on average much lower for loops of longer lengths \cite{Almagro2011},\cite{Almagro2014}. 
Several different approaches for generating three-dimensional structure models from antibody sequences exist such as RosettaAntibody \cite{Sircar2009},\cite{Sivasubramanian2009}, ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017} and abYmod, UCL’s in-house software developed by Prof. Martin. One of the most used methods is RosettaAntibody, which implements template selection and ab initio CDR-H3 loop modelling using loop fragments and employing specific angle restraints which bias the conformational space towards so-called ‘kinked’ loops\cite{Schoeder2021},\cite{Weitzner2017}. In contrast, ABodyBuilder uses a database search algorithm (FREAD\cite{Choi2010}) for CDR loop modelling. 
In this project abYmod is used, which is to be found at http://abymod.abysis.org/. The program utilizes extensive canonical class definitions, VH/VL angle prediction and a large database of loop structures (LoopDB) for CDR-H3 modelling to achieve optimal results. Upon inputting an antibody sequence, abYmod assigns the canonical class using a set of key residues \cite{Martin1996}and where an exact match is not possible, a nearest match is made. Then, the program identifies the 10 best overall-matching PDB files according to sequence identity for the light and heavy chain. Of these, the best template is then identified for each CDR using sequence similarity and identity. In general, modelling the antibody using the single best overall-matching template works best and the CDR-specific templates are used if there is no canonical match. The VH/VL packing angle is then determined either using machine learning or the chosen template structure for one of the chains. CDR specific templates, if selected, are grafted onto the framework. If there is no template of the correct length for CDR-H3, the loop is built using the LoopDB database, containing CDRH3-like loops from all proteins. Finally, Gromacs energy minimization software is used to optimize the model. This method has proven very effective and preliminary analysis suggests the method achieves comparable results or outperforms other modelling software (see results section). 
 Using these mentioned modelling methods, framework regions can generally be predicted with great accuracy (with better than 1Å RMSD\cite{Almagro2014}), as one can often find a very similar structure for the homology modelling process.  However, the CDR loops are not as easily predicted due to their great diversity. If the canonical conformation of CDR loops 1-5 can be identified, they too can be modelled rather well, often within 1Å RMSD, for CDR-H3 loops the average is usually above 3Å \cite{Almagro2011}. 
ABodyBuilder is a modelling server that provides the user with a confidence score for each region (e.g.CDR-H2) of the antibody model. The given score is the probability that a specific region (e.g. CDR-H2) will be will be modeled within a specific RMSD threshold \cite{Leem2016}}. Thus, it can be used to obtain an expected RMSD value for a given probability (default 75\%). For the CDR-H3 this score is calculated as a function of the loop length.  The confidence scorer is described as robust, but less accurate in the case of CDR loops due to the lack of data.\cite{Leem2016} ABLooper also provides a confidence metric for the CDR-H3 loop model, which is estimated by the diversity of a set of predicted conformations for the same loop\cite{Abanades2022}.However, it remains unclear whether a high prediction diversity score points towards loops with multiple conformations or a low quality model. Furthermore, it remains unclear how well the generated diversity score reflects model quality\cite{Abanades2022}.

Modelling the H3 loop is a hurdle for in silico development of therapeutic antibodies. Currently, there is no definite, reliable way to determine how accurate a generated structural model is within the H3 region. Therefore, the aim of this project will be to produce a user-friendly predictor of H3 model quality. The predictor will give the user an RMSD-range in Ångstöms, in which the generated model lies with a high probability. Making such a confidence score available via the web interface of the in-house modelling software abYmod is a future goal. Such a score is not provided by most modelling programs and would thus be a novel addition.  This information can guide the user in the antibody engineering process. The user has the choice to determine whether the model is to be used in the intended way, or whether the model should be re-worked.

\section{Results}
\label{sec:sample2}
To asses the predictive power regarding the CDR-H3 loop, the software was tested on a test-set of antibody structures used in the 2014 and 2011 Antibody Modelling Assessments \cite{Almagro2014},\cite{Almagro2011}. As the results depicted in \ref{fig:AMA} show, abYmod achieves results similar to, or better than other modelling programs. However, the outliers with very high RMSD values increase abYmod’s RMSD average. The predictor in this work would aim to identify such outlier models.
The predictive power of any machine learning model is largely dependent on the quality and size of the dataset it was trained on. As this is a non-linear, complex, multi-class classification problem, a substantial amount of data was required. Thus, an extensive, verified dataset of antibody structures called abYbank/AbDb\cite{Almagro2011}, established by Prof. Andrew Martin, was utilised (1924 non-redundant structures). The root-mean-square deviation (RMSD) value, a measure of distance between backbone C-α atoms of superimposed crystal structures and modelled structures, is calculated (see methods). This metric for model quality was used to classify models. 
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.3]{AMA}
  \caption {RMSD values of the CDR-H3 loop for structures from the Antibody Modelling Assessment I
(2011) and AMAII (2014). abYmod outperforms other modelling software in some instances, but
also has much lower accuracy in few outlier cases. (left: an abYmod structure for C705 could be
generated, yet the RMSD calculation failed. Right: Ab01 is the rabbit antibody PDB:4MA3,
which was excluded in the CDR-H3 modelling stage in AMAII due to difficulties modelling the
overall structure previously. Ab01 is shown for the methods, where generated models were
adequate for RMSD calculation.)}
  \label{fig:AMA}
\end{figure}
The full pipeline for creating the final machine learning model that will predict model quality by giving its RMSD range starts with a feature-set calculation using the antibody sequence. The feature set includes many different attributes linked to sequence, physical characteristics, interactions, etc. within as well as outside of the loop. There is a plethora of information to train our classifier on, including packing quality, protrusion, hydrophobicity, pseudo-energy (see protrusion, hydrophobicity, pseudo-energy (see methods for details). The sequence logo \ref{fig:logo} visualizes amino acid occurrence within the loop sequence, elements of which can be extracted as features \cite{Thomsen2012},\cite{Shaner1993}.

\begin{figure}[h!]
  \includegraphics[scale=0.9]{logo.png}
  \caption {Sequence Logo of the CDRH3 loop sequence. Data on amino acid occurrence taken from http://abymod.abysis.org/. Visualized using Seq2Logo.}
  \label{fig:logo}
\end{figure}
After creating the feature dataset, it is pre-processed (cleaning, scaling, encoding, see methods for details). Structures with a resolution below 4Å were removed given their low quality. Identical whole antibody structures were removed from the dataset, while instances of different antibodies that matched in loop sequence were not removed. Models of some of these structures with the same loop sequence differ significantly. The few large RMSD ranges may stem from low resolution, e.g. the highest datapoint contains a structure with a resolution of 3.00 Å.  Residue differences near the loop may also explain the conformational difference. Some of these structures are complexed while others are not, which may also affect the loop structure.

The dataset was also screened for any models which abYmod created using a template sequence from LoopDB, a database of CDR-H3 like loops from all proteins. This was not the case for any of our structures. 
The target data (i.e. RMSD values) are then transformed from numerical values to nominal values so that they can be used for classification. In order to define these nominal categories, the total RMSD range must be divided into categories. This is done either by creating uniform classes i.e. 1-2Å, 2-3Å (the optimal size of which must be determined), etc. or by creating balanced classes. When creating balanced classes, the upper and lower thresholds of a category are chosen in such a way that each class contains an equal number of instances. This approach is chosen to counteract the skewness of the RMSD distribution. However, this was found to negatively affect the final model’s predictive power. Therefore, uniform classes were used. 
They are also transformed into a set of binary values according to a list of RMSD thresholds. This is done so that binary models can be trained, which will predict the probability e.g. that the model’s RMSD is above 2Å, 2.2Å, 2.4Å, and so on. The number of binary classifiers incorporated into the first layer have a great effect on the final model, the general 
trend being that the more binary classifiers are used, the better the nominal prediction. 
\subsection{Feature Encoding and Selection}
\label{sec:sample2}

As some features are in the form of amino acid codes, these must be encoded before they can be passed to a machine learning model. The encoding strategy often determines how efficiently the model learns and how much information can be extracted. Different strategies were employed to represent followed by BLOSUM62 and NLF encoding. The physiochemical encoding strategy was implemented for all models, being the most effective. However, PCA-3 BLOSUM62, a dimensionality-reduced BLOSUM62 encoding method achieved comparable results. 
Feature selection was conducted to improve the ML model’s learning capacity. A high-dimensional feature dataset bears the risk of introducing excessive noise, facilitating model overfitting and can be responsible for an overall decrease in model performance and stability. Each additionally inputted feature forces the model to handle a more complex task, which consumes excess computational power and time and leads to overfitting of the model.

Our model is trained on different feature sets selected using manual selection as well as algorithmic selection strategies, in order to determine the most effective feature selection method. None of the feature selection methods was a best fit for all models.

After the data is processed, it can be fed into different machine learning models. Different model types are investigated, as the most suited model-type has to be heuristically determined. We decided on the following list, which includes some of the most commonly used algorithms: logistic regression, linear discriminant analysis, K-nearest neighbours classifier, decision tree classifier, Gaussian NB, random forest classifier, support vector machine, probability-based voting (also known as soft voting) and extreme gradient boosting (XGBoost)\cite{Chen2016}.

The best model, and its best hyperparameters, are then determined for each binary RMSD target. The set of binary models outputs a number of predictions that give the likelihood of the model having an RMSD above the threshold value of the respective model. These predictions are then added to the feature set, which a top-layer classifier is then trained on. Thus, a quasi-voting-system is incorporated into the final classifier, in which a set of weaker classifiers vote on the model quality.

\subsection{Hyperparameter Optimization}
\label{sec:sample2}
In the process of hyperparameter optimization, the configuration of model parameters which results in best performance is selected. This is usually a computationally expensive and manual procedure.
In an effort to automate this process, a population is defined for each model type, so hyperparameter optimization can be conducted automatically for each model and seamlessly integrated into the full model creation process. Two different methods for hyperparameter optimization were tested. The first is a hybrid approach of randomized search and grid search, the second uses a genetic algorithm for optimization. The genetic algorithm was found to achieve slightly better results and was selected for all models.

\subsection{Model Performance}
\label{sec:sample2}
The overall best final model is composed of several different binary classifiers, with an extreme gradient boosting (XGBoost) top-layer nominal classifier. Features were selected using random forest feature selection. A final MCC value of 0.99 could be achieved for a model using the abYmod log file as input as well as the loop model file itself. This value slightly dropped to 0.92 if no such log file was given. This is mainly due to the fact that the template sequence abYmod used to generate the model is unknown in the latter case. 
The classifier predicts whether a model has an RMSD of below 2Å, between 2-4Å,or above 4Å. These cut-off values were selected based on the observation that abYmod generally produces a model with RMSD below 4Å. Incorrectly modelled structures (\ref{fig:AMA}) may be identified by screening for structures estimated to have an RMSD above 4Å. If a very high-quality model is needed one should also exclude models above 2Å.

\section{Discussion}
The results suggest that our presented classifier can differentiate between well-modelled and less well-modelled CDR-H3 loop structures. An MCC value of 0.99 was achieved, which underlines this ability for accurate discrimination. Different methods for data pre-processing, feature encoding, feature selection and hyperparameter optimization were tested. 
Feature encoding methods that were very high-dimensional (one-hot-encoding, BLOSUM62, NLF) were found to be unfavorable. Dimensionality reduction methods (Principal Component Analysis (PCA), Independent Component Analysis (ICA), projection-based methods e.g. t-SNE) were used on BLOSUM62 encoded matrices, which lead to significant improvement. However, a physiochemical encoding strategy was most effective. 
The selection of features incorporated in the training set seemed to be most important for effective learning. A multitude of methods were tested. No one-fit-for-all method for the different models could be found. However, for our top-layer classifier in our final model recursive feature elimination worked best. 
A set of commonly used machine learning algorithms were tested, and the best ML models were incorporated into the final ensemble model. A stacked model approach (consisting of 23 binary classifiers and a single top-layer nominal classifier) was shown to outperform single ML models.
An MCC value of 0.99 was achieved for a classifier predicting whether an input-model has an RMSD value below 2Å, 2Å-4Å or above 4Å. 
Given that abYbank/AbDb is soon to be expanded by an additional ca. 2000 structures, classifier performance on models without a known abYmod-template sequence may be improved by a larger dataset. 
It is conceivable that the described predictor may also be incorporated in the antibody modelling process as a low-quality filter in the future, flagging certain structures for re-modelling.

 In a future research project residue patterns in correlation with RMSD may be analyzed. Possibly, one might identify certain sequence patterns that make accurate modelling with abYmod more difficult. Furthermore, separate classifiers according to loop length can be built. Given that loop length is the most important determinant of model quality, this approach may yield some insight into the challenges of modelling shorter vs longer loops. 
One could also conduct an analysis of the predictor’s behaviour when abYmod is forced to use LoopDB-based modelling. This might shed light on whether the ML model presented in this paper is biased towards abYmod’s used source of template structures. It would also give an indication of how well the predictor would work in combination with other modelling software.

\bibliographystyle{elsarticle-num} 
\bibliography{references}

\appendix{}
\section{Experimental Procedures}
\subsection{Computing}
All machine learning and, feature selection and hyperparameter optimization algorithms were implemented in Python. The Scikit-learn library was used for training models, the Yellowbrick\cite{Bengfort2021} library was utilized for visualization. All code is available at https://github.com/LilianDenzler/qualiloop . 
The code was run under CentOS 7 on an 8-core virtual machine on an Intel Xeon 4208 CPU with 16Gig RAM.

\subsection{Data Pre-Processing and Preparation}
Handling Null Values and Duplicates: The dataset containing target RMSD values, and the calculated features was screened for null values. If a feature column contained more than 5\% null values, it was dropped (none removed). Rows that contained any null values were removed from the dataset (11 rows in total).

\subsubsection{Duplicate Screening} Using AbDb’s redundancy information it was ensured that no antibodies were present in the dataset more than once. The dataset is additionally screened for duplicate instances.

\subsubsection{Scaling} Normalization and Standardization are tested as scaling methods. Both approaches are greatly influenced by outliers, and such datapoints are ideally removed for optimal scaling. Here we define outliers as datapoints that lie over 1.5 times the interquartile range (IQR) below the first quartile or above the third quartile. The IQR is defined as the range between quartile 1, i.e. the median of the lower half of the data, and quartile 3, i.e. the median of the upper half of the 
data. However, across all features there are a total of 632 outlier values and removing such a large number of datapoints is not a viable option. A robust scaler was also used, which uses statistics that are robust to outliers. The median is set to zero and numerical features are scaled to the interquartile range.

\subsubsection{BLOSUM 62 encoding} The BLOSUM62 matrix reflects the frequencies of amino acid substitutions within a locally aligned, conserved regions of proteins with at least 62\% similarity. Each amino acid is represented by a row (or column) of the BLOSUM62 matrix. Dimensionality reduction techniques are employed: Principal Component Analysis (PCA), Independent Component Analysis (ICA), projection-based methods (t-SNE, Isomap). Three components were used as features.

\subsubsection{Physiochemical Feature Encoding} In a paper by L. Nanni and A.Lumini a new encoding technique is 
presented which was developed for machine learning classifiers. Many physiochemical properties are calculated and transformed using a non-linear Fisher transform for dimensionality reduction.  A vector of length 19 is produced for each amino acid34.  
In a paper on designing a neural network for predicting the packing angle of the light and heavy variable chain of an antibodies, A.C.R. Martin and K.R. Abhinandan introduce an encoding method that produces a four-dimensional physiochemical feature vector25. The amino acid properties used are 1) the total number of side-chain atoms, 2) the number of side-chain atoms in the shortest path from Cα to the most distal atom, 3) the Eisenberg consensus hydrophobicity\cite{Eisenberg1982}, 4) the charge.

\subsection{Dataset-splitting}
 The final model was evaluated using a test set, separated from the training set at the start in a 30/70 split (lock-box principle) 35. The performance of all individual sub-models of the first layer are determined using stratified K-folds cross-validation (k=10) as the dataset is imbalanced, being skewed towards lower RMSD values. The method is differentiable from K-folds cross validation as it uses stratified sampling instead of random sampling. This ensures each class is represented, as the percentage of samples for each class are preserved. 
A validation set, usually used for testing during the optimization stage will be omitted in favour of stratified K-folds cross-validation (k=10) \cite{Krstajic2014} \cite{Kohavi1995}.

\subsection{Model Assessment} 
Model assessment must be considered at two levels as performance metrics of binary and multi-class classifiers are calculated differently and must thus be considered separately. The Mathews Correlation Coefficient (MCC) \cite{Matthews1975} is deemed the most informative, taking the ratios of the four confusion matrix categories into account 39and is thus more reliable than the F1 score and accuracy . It is also consistent for both binary and multi-class problems and therefore well suited for our purpose.

\subsection{Feature Calculations}
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.49]{feature_table.png}
  \caption {A summary of how different feature values were calculated.}
  \label{fig:feature_table}
\end{figure}

\begin{figure}[h!]
  \includegraphics[scale=0.6]{angle.png}
  \caption {Diagram visualizing the process underlying the protrusion calculation. First, the base residues (i.e H95 and H102, shown as red spheres) of the CDR-H3 (shown in red) are identified. Then, a line is drawn between the two Cα atoms of these residues (yellow dashed line). The distance of the Cα-atom of each residue in the CDR-H3 loop to this line is calculated. The residue which has the greatest distance to the line (shown as green sphere) is outputted as one-letter amino acid code and used as feature. The distance in Å (depicted as yellow arrow) is used as the ‘protrusion’ feature. }
  \label{fig:angle}
\end{figure}

\begin{figure}[h!]
  \includegraphics[scale=0.45]{method.png}
  \caption {Simplified pipeline for creating the final machine learning model that will predict model quality by giving its RMSD range.}
  \label{fig:method}
\end{figure}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%

\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2022-10-05 paper.tex
Changed paper to standard LaTeX and split lines

--- 2022-09-28 elsarticle-template-num.tex
@@
-%% 
-%% Copyright 2007-2020 Elsevier Ltd
-%% 
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%%
-
-%% Template article for Elsevier's document class `elsarticle'
-%% with numbered style bibliographic references
-%% SP 2008/03/01
-%%
-%% 
-%%
-%% $Id: elsarticle-template-num.tex 190 2020-11-23 11:12:32Z rishi $
-%%
-%%
-%Path relative to the .tex file containing the \includegraphics command
-
-\documentclass[preprint,12pt]{elsarticle}
+\documentclass[12pt]{article}
+\bibliographystyle{unsrt}
 \usepackage{graphicx}
-\graphicspath{ {./Images/} }
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-%% please give \usepackage{epsfig}
-
+\usepackage{url}
 %% The amssymb package provides various useful mathematical symbols
 \usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
 
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-\journal{XXXXX}
+\title{Predicting the Quality of CDRH3 Antibody Loop Structural Models}
+\author{Lilian M.\ Denzler and Andrew C.R.\ Martin\\
+Structural and Molecular Biology, Division of Biosciences,\\
+University College of London,\\
+Gower Street,\\
+London WC1E 6BT, UK
+}
 
 \begin{document}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \affiliation{organization={},
-%%             addressline={},
-%%             city={},
-%%             postcode={},
-%%             state={},
-%%             country={}}
-%% \fntext[label3]{}
-
-\title{Predicting the Quality of CDRH3 Antibody Loop Structural Models}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \affiliation[label1]{organization={},
-%%             addressline={},
-%%             city={},
-%%             postcode={},
-%%             state={},
-%%             country={}}
-%%
-%% \affiliation[label2]{organization={},
-%%             addressline={},
-%%             city={},
-%%             postcode={},
-%%             state={},
-%%             country={}}
-
-\author[inst1]{Lilian M Denzler}
-
-\affiliation[inst1]{organization={Department of Structural and Molecular Biology, 
-University College of London},%Department and Organization
-            addressline={Gower Street}, 
-            city={London},
-            postcode={WC1E 6BT}, ,
-            country={UK}}
-
-\author[inst1]{Andrew CR Martin}
+\maketitle
 
 \begin{abstract}
-%% Text of abstract
-Therapeutic antibodies have shown an unprecedented pace of development and have brought new hope for the treatment of numerous diseases.
-The bioinformatic tools for modelling antibody structures have become invaluable for antibody engineering and the development of therapeutic antibodies.
-The antigen-binding site consists of six hypervariable loops, also known as the Complementary Determining Regions (CDR), all of which can be modelled with adequate accuracy, except for one.
-It remains markedly difficult to model the third CDR loop of the antibody heavy chain.
-The CDRH3 differs in length, has far greater sequence variability and has such a great structural diversity that modelling it is considerably harder.
-Many sophisticated approaches for antibody modelling, such as the abYmod software, have been developed.
-Although such efforts have improved prediction accuracy the results for the CDRH3 loop are still inconsistent and require further improvement.
-Providing a confidence score for the structure predictions would aid in differentiating well-modelled structures from incorrectly modelled structures, giving the abYmod user a clearer understanding of the generated model reliability.
-We present a model quality predictor, combining domain knowledge with machine learning techniques to predict the accuracy of CDRH3 models generated by antibody modelling software such as abYmod.
-The newly developed predictor scored a Mathews Correlation Coefficient of 0.99, and can thus be described as highly reliable.
-The predictor is made available at \url{http://www.bioinf.org.uk/abs/qualiloop/}.
+  Therapeutic antibodies have shown an unprecedented pace of
+  development and have brought new hope for the treatment of numerous
+  diseases. The bioinformatic tools for modelling antibody structures
+  have become invaluable for antibody engineering and the development
+  of therapeutic antibodies. The antigen-binding site consists of six
+  hypervariable loops, also known as the Complementary Determining
+  Regions (CDR), all of which can be modelled with adequate accuracy,
+  except for one. It remains markedly difficult to model the third CDR
+  loop of the antibody heavy chain. The CDRH3 differs in length, has
+  far greater sequence variability and has such a great structural
+  diversity that modelling it is considerably harder.
 
+  Many sophisticated approaches for antibody modelling, such as the
+  abYmod software, have been developed. Although such efforts have
+  improved prediction accuracy the results for the CDRH3 loop are
+  still inconsistent and require further improvement. Providing a
+  confidence score for the structure predictions would aid in
+  differentiating well-modelled structures from incorrectly modelled
+  structures, giving the abYmod user a clearer understanding of the
+  generated model reliability.
+
+  We present a model quality predictor, combining domain knowledge
+  with machine learning techniques to predict the accuracy of CDRH3
+  models generated by antibody modelling software such as abYmod. The
+  newly developed predictor scored a Mathews Correlation Coefficient
+  of 0.99, and can thus be described as highly reliable. The predictor
+  is made available at \url{http://www.bioinf.org.uk/abs/qualiloop/}
 \end{abstract}
 
-%%Graphical abstract
-%%\begin{graphicalabstract}
-%%\includegraphics{grabs}
-%%\end{graphicalabstract}
+\section{Introduction}
 
-%%Research highlights
-%%\begin{highlights}
-%%\item Research highlight 1
-%%\item Research highlight 2
-%%\end{highlights}
+Antibodies are highly specialized proteins of the immune system that
+are produced in response to a foreign substance, called an antigen. A
+mature antibody binds a specific antigen with high affinity, while
+only weakly interacting with other antigens, or not at all. This high
+affinity, high specificity sets it apart from other pharmaceuticals.
+Furthermore, in contrast with small drug molecules, antibodies can not
+only bind pockets, but also flat, concave or even convex surfaces
+\cite{Tavers2001}. Their unique characteristics have enabled
+researchers to develop efficient antibody drugs for treating cancers,
+autoimmune disorders, infectious diseases and many more \cite{Lu2020}.
+Their ability to target an immense variety of antigens allows for
+endless possibilities in application. The global market size was
+valued at USD 130.9 billion in 2020, estimated to grow 223.7 billion
+by the end of 2025 at a compound annual growth rate of 11.31\%
+\cite{market2020}. Four of the top 10 best-selling drugs in 2020 were
+monoclonal antibodies \cite{Urquhart2021}.
 
-%%\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-%%keyword one \sep keyword two
-%% PACS codes here, in the form: \PACS code \sep code
-%%\PACS 0000 \sep 1111
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-%%\MSC 0000 \sep 1111
-%%\end{keyword}
+In order to rationally design therapeutic antibodies, knowledge of
+their structure is essential. The acquired structural information can
+be used to increase binding affinity to a target of interest,
+predicting both the exact binding site and the antibody stability as
+well as assessing immunogenicity \cite{Abhinandan2007}. As
+experimental structure determination is very costly and time
+consuming, computational predictions of an antibody's structure are
+used to streamline the process.
 
-\end{frontmatter}
+Antibodies consist of a heavy and a light chain, which are linked by
+disulphide bonds. The N-terminal domain of each makes up the variable
+fragment (Fv), which contains the complementarity determining regions
+(CDRs). The antigen binding site is composed of six CDRs, also known
+as hypervariable loops. All except one of these loops can be clustered
+into a limited number of canonical structures. Therefore, modelling
+these loops with adequate accuracy is commonly achievable
+\cite{North2011},\cite{Weitzner2015}. However, the CDR loop 3 of the
+heavy chain (CDRH3) has a far greater sequence variability due to the
+processes of V(D)J recombination and somatic hyper‐mutation and its
+structure has remained unclassifiable \cite{Finn2016}. The variety in
+structure is so great, that its structural diversity is remarkable
+even compared to other protein loops \cite{Regep2017}. It was found
+that over 75\% of CDRH3 loops do not have a sub-Angstrom non-antibody
+structural neighbour, as well as that 30\% of CDRH3 loops have a
+completely unique structure compared with under 3\% for all other
+loops on average \cite{Regep2017}.
 
-%% \linenumbers
+Apart from being the most structurally diverse, the H3 loop is also
+the most important for antigen binding, being located at the center of
+the binding site and forming the most contacts to the antigen
+\cite{MacCallum1996}. In fact, it was demonstrated that differences in
+this loop alone were sufficient to enable otherwise identical
+antibodies to distinguish between various antigens \cite{Xu2000}.
 
-%% main text
-\section{Introduction}
-\label{sec:sample1}
-Antibodies are highly specialized proteins of the immune system that are produced in response to a foreign substance, called an antigen.
-A mature antibody binds a specific antigen with high affinity, while only weakly interacting with other antigens, or not at all.
-This high affinity, high specificity sets it apart from other pharmaceuticals.
-Furthermore, in contrast with small drug molecules, antibodies can not only bind pockets, but also flat, concave or even convex surfaces \cite{Tavers2001}.
-Their unique characteristics have enabled researchers to develop efficient antibody drugs for treating cancers, autoimmune disorders, infectious diseases and many more \cite{Lu2020}.
-Their ability to target an immense variety of antigens allows for endless possibilities in application.
-The global market size was valued at USD 130.9 billion in 2020, estimated to grow 223.7 billion by the end of 2025 at a compound annual growth rate of 11.31\% \cite{market2020}.
-Four of the top 10 best-selling drugs in 2020 were monoclonal antibodies \cite{Urquhart2021}.
-In order to rationally design therapeutic antibodies, knowledge of their structure is essential.
-The acquired structural information can be used to increase binding affinity to a target of interest, predicting both the exact binding site and the antibody stability as well as assessing immunogenicity \cite{Abhinandan2007}.
-As experimental structure determination is very costly and time consuming, computational predictions of an antibody’s structure are used to streamline the process.
-Antibodies consist of a heavy and a light chain, which are linked by disulphide bonds.
-The N-terminal domain of each makes up the variable fragment (Fv), which contains the complementarity determining regions (CDRs).
-The antigen binding site is composed of six CDRs, also known as hypervariable loops.
-All except one of these loops can be clustered into a limited number of canonical structures.
-Therefore, modelling these loops with adequate accuracy is commonly achievable \cite{North2011},\cite{Weitzner2015}.
-However, the CDR loop 3 of the heavy chain (CDRH3) has a far greater sequence variability due to the processes of V(D)J recombination and somatic hyper‐mutation and its structure has remained unclassifiable \cite{Finn2016}.
-The variety in structure is so great, that its structural diversity is remarkable even compared to other protein loops \cite{Regep2017}.
-It was found that over 75\% of CDRH3 loops do not have a sub-Angstrom non-antibody structural neighbour, as well as that 30\% of CDRH3 loops have a completely unique structure compared with under 3\% for all other loops on average \cite{Regep2017}.
-Apart from being the most structurally diverse, the H3 loop is also the most important for antigen binding, being located at the center of the binding site and forming the most contacts to the antigen \cite{MacCallum1996}.
-In fact, it was demonstrated that differences in this loop alone were sufficient to enable otherwise identical antibodies to distinguish between various antigens \cite{Xu2000}.
- According to the Kabat definition, the CDRH3 loop is made up of the residues 95-105 (Kabat numbering scheme\cite{Kabat1992}) in the heavy chain, with a potential insertion site at position 100.
-The possibility of such an insertion of a varying number of residues leads to a large range of loop lengths, with bovine antibodies being exceptionally long \ref{fig:loopdist}.
-\begin{figure}[h!]
-  \includegraphics[scale=1]{loopdist.png}
+According to the Kabat definition, the CDRH3 loop is made up of the
+residues 95-105 (Kabat numbering scheme\cite{Kabat1992}) in the heavy
+chain, with a potential insertion site at position 100. The
+possibility of such an insertion of a varying number of residues leads
+to a large range of loop lengths, with bovine antibodies being
+exceptionally long \ref{fig:loopdist}.
+
+\begin{figure}
+  \includegraphics[scale=1]{loopdist.eps}
   \centering
-  \caption { Distribution of CDR-H3 loop lengths in mouse (left), human (centre) and cow (right).
-Mouse and human antibody CDRH3s have a unimodal, yet almost normal distribution with a range of ca.
-4-28 and 4-38 respectively.
-The length cut-off for CDRH3s depicted above is 30 amino acids.
-Bovine antibodies with significantly longer CDR-H3 loops than depicted here exist, reaching a length of 67 amino acids and above.
-\cite{Wong2015}}
+  \caption { Distribution of CDR-H3 loop lengths in mouse (left),
+    human (centre) and cow (right). Mouse and human antibody CDRH3s
+    have a unimodal, yet almost normal distribution with a range of
+    ca. 4-28 and 4-38 respectively. The length cut-off for CDRH3s
+    depicted above is 30 amino acids. Bovine antibodies with
+    significantly longer CDR-H3 loops than depicted here exist,
+    reaching a length of 67 amino acids and
+    above. \protect\cite{Wong2015}}  
   \label{fig:loopdist}
@@
 
-For shorter loops, a higher prediction accuracy can be achieved than for longer CDRH3 loops.
-This was also shown by the Antibody Modelling Assessments (AMA), two blind contests that required researchers to build structural models from antibody sequences.
-The CDR-H3 loop modelling quality achieved at the contests was on average much lower for loops of longer lengths \cite{Almagro2011},\cite{Almagro2014}.
-Several different approaches for generating three-dimensional structure models from antibody sequences exist such as RosettaAntibody \cite{Sircar2009},\cite{Sivasubramanian2009}, ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017} and abYmod, UCL’s in-house software developed by Prof.
-Martin.
-One of the most used methods is RosettaAntibody, which implements template selection and ab initio CDR-H3 loop modelling using loop fragments and employing specific angle restraints which bias the conformational space towards so-called ‘kinked’ loops\cite{Schoeder2021},\cite{Weitzner2017}.
-In contrast, ABodyBuilder uses a database search algorithm (FREAD\cite{Choi2010}) for CDR loop modelling.
-In this project abYmod is used, which is to be found at http://abymod.abysis.org/.
-The program utilizes extensive canonical class definitions, VH/VL angle prediction and a large database of loop structures (LoopDB) for CDR-H3 modelling to achieve optimal results.
-Upon inputting an antibody sequence, abYmod assigns the canonical class using a set of key residues \cite{Martin1996}and where an exact match is not possible, a nearest match is made.
-Then, the program identifies the 10 best overall-matching PDB files according to sequence identity for the light and heavy chain.
-Of these, the best template is then identified for each CDR using sequence similarity and identity.
-In general, modelling the antibody using the single best overall-matching template works best and the CDR-specific templates are used if there is no canonical match.
-The VH/VL packing angle is then determined either using machine learning or the chosen template structure for one of the chains.
-CDR specific templates, if selected, are grafted onto the framework.
-If there is no template of the correct length for CDR-H3, the loop is built using the LoopDB database, containing CDRH3-like loops from all proteins.
-Finally, Gromacs energy minimization software is used to optimize the model.
-This method has proven very effective and preliminary analysis suggests the method achieves comparable results or outperforms other modelling software (see results section).
- Using these mentioned modelling methods, framework regions can generally be predicted with great accuracy (with better than 1Å RMSD\cite{Almagro2014}), as one can often find a very similar structure for the homology modelling process.
-However, the CDR loops are not as easily predicted due to their great diversity.
-If the canonical conformation of CDR loops 1-5 can be identified, they too can be modelled rather well, often within 1Å RMSD, for CDR-H3 loops the average is usually above 3Å \cite{Almagro2011}.
-ABodyBuilder is a modelling server that provides the user with a confidence score for each region (e.g.CDR-H2) of the antibody model.
-The given score is the probability that a specific region (e.g.
-CDR-H2) will be will be modeled within a specific RMSD threshold \cite{Leem2016}}.
-Thus, it can be used to obtain an expected RMSD value for a given probability (default 75\%).
-For the CDR-H3 this score is calculated as a function of the loop length.
-The confidence scorer is described as robust, but less accurate in the case of CDR loops due to the lack of data.\cite{Leem2016} ABLooper also provides a confidence metric for the CDR-H3 loop model, which is estimated by the diversity of a set of predicted conformations for the same loop\cite{Abanades2022}.However, it remains unclear whether a high prediction diversity score points towards loops with multiple conformations or a low quality model.
-Furthermore, it remains unclear how well the generated diversity score reflects model quality\cite{Abanades2022}.
+For shorter loops, a higher prediction accuracy can be achieved than
+for longer CDRH3 loops. This was also shown by the Antibody Modelling
+Assessments (AMA), two blind contests that required researchers to
+build structural models from antibody sequences. The CDR-H3 loop
+modelling quality achieved at the contests was on average much lower
+for loops of longer lengths \cite{Almagro2011},\cite{Almagro2014}.
 
-Modelling the H3 loop is a hurdle for in silico development of therapeutic antibodies.
-Currently, there is no definite, reliable way to determine how accurate a generated structural model is within the H3 region.
-Therefore, the aim of this project will be to produce a user-friendly predictor of H3 model quality.
-The predictor will give the user an RMSD-range in Ångstöms, in which the generated model lies with a high probability.
-Making such a confidence score available via the web interface of the in-house modelling software abYmod is a future goal.
-Such a score is not provided by most modelling programs and would thus be a novel addition.
-This information can guide the user in the antibody engineering process.
-The user has the choice to determine whether the model is to be used in the intended way, or whether the model should be re-worked.
+Several different approaches for generating three-dimensional
+structure models from antibody sequences exist such as RosettaAntibody
+\cite{Sircar2009},\cite{Sivasubramanian2009},
+ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017} and abYmod,
+UCL's in-house software developed by Prof. Martin. One of the most
+used methods is RosettaAntibody, which implements template selection
+and ab initio CDR-H3 loop modelling using loop fragments and employing
+specific angle restraints which bias the conformational space towards
+so-called ‘kinked' loops\cite{Schoeder2021},\cite{Weitzner2017}. In
+contrast, ABodyBuilder uses a database search algorithm
+(FREAD\cite{Choi2010}) for CDR loop modelling.
+
+In this project abYmod is used, which is to be found at
+http://abymod.abysis.org/. The program utilizes extensive canonical
+class definitions, VH/VL angle prediction and a large database of loop
+structures (LoopDB) for CDR-H3 modelling to achieve optimal
+results. Upon inputting an antibody sequence, abYmod assigns the
+canonical class using a set of key residues \cite{Martin1996}and where
+an exact match is not possible, a nearest match is made. Then, the
+program identifies the 10 best overall-matching PDB files according to
+sequence identity for the light and heavy chain. Of these, the best
+template is then identified for each CDR using sequence similarity and
+identity. In general, modelling the antibody using the single best
+overall-matching template works best and the CDR-specific templates
+are used if there is no canonical match. The VH/VL packing angle is
+then determined either using machine learning or the chosen template
+structure for one of the chains. CDR specific templates, if selected,
+are grafted onto the framework. If there is no template of the correct
+length for CDR-H3, the loop is built using the LoopDB database,
+containing CDRH3-like loops from all proteins. Finally, Gromacs energy
+minimization software is used to optimize the model. This method has
+proven very effective and preliminary analysis suggests the method
+achieves comparable results or outperforms other modelling software
+(see results section).
+
+Using these mentioned modelling methods, framework regions can
+generally be predicted with great accuracy (with better than 1\AA\
+RMSD\cite{Almagro2014}), as one can often find a very similar
+structure for the homology modelling process.  However, the CDR loops
+are not as easily predicted due to their great diversity. If the
+canonical conformation of CDR loops 1-5 can be identified, they too
+can be modelled rather well, often within 1\AA\ RMSD, for CDR-H3 loops
+the average is usually above 3\AA\cite{Almagro2011}.
+
+ABodyBuilder is a modelling server that provides the user with a
+confidence score for each region (e.g.CDR-H2) of the antibody
+model. The given score is the probability that a specific region
+(e.g. CDR-H2) will be will be modeled within a specific RMSD threshold
+\cite{Leem2016}. Thus, it can be used to obtain an expected RMSD
+value for a given probability (default 75\%). For the CDR-H3 this
+score is calculated as a function of the loop length.  The confidence
+scorer is described as robust, but less accurate in the case of CDR
+loops due to the lack of data.\cite{Leem2016} ABLooper also provides a
+confidence metric for the CDR-H3 loop model, which is estimated by the
+diversity of a set of predicted conformations for the same
+loop\cite{Abanades2022}.However, it remains unclear whether a high
+prediction diversity score points towards loops with multiple
+conformations or a low quality model. Furthermore, it remains unclear
+how well the generated diversity score reflects model
+quality\cite{Abanades2022}.
+
+Modelling the H3 loop is a hurdle for in silico development of
+therapeutic antibodies. Currently, there is no definite, reliable way
+to determine how accurate a generated structural model is within the
+H3 region. Therefore, the aim of this project will be to produce a
+user-friendly predictor of H3 model quality. The predictor will give
+the user an RMSD-range in {\AA}ngstr\"{o}ms, in which the generated model lies
+with a high probability. Making such a confidence score available via
+the web interface of the in-house modelling software abYmod is a
+future goal. Such a score is not provided by most modelling programs
+and would thus be a novel addition.  This information can guide the
+user in the antibody engineering process. The user has the choice to
+determine whether the model is to be used in the intended way, or
+whether the model should be re-worked.
 
 \section{Results}
-\label{sec:sample2}
-To asses the predictive power regarding the CDR-H3 loop, the software was tested on a test-set of antibody structures used in the 2014 and 2011 Antibody Modelling Assessments \cite{Almagro2014},\cite{Almagro2011}.
-As the results depicted in \ref{fig:AMA} show, abYmod achieves results similar to, or better than other modelling programs.
-However, the outliers with very high RMSD values increase abYmod’s RMSD average.
-The predictor in this work would aim to identify such outlier models.
-The predictive power of any machine learning model is largely dependent on the quality and size of the dataset it was trained on.
-As this is a non-linear, complex, multi-class classification problem, a substantial amount of data was required.
-Thus, an extensive, verified dataset of antibody structures called abYbank/AbDb\cite{Almagro2011}, established by Prof.
-Andrew Martin, was utilised (1924 non-redundant structures).
-The root-mean-square deviation (RMSD) value, a measure of distance between backbone C-α atoms of superimposed crystal structures and modelled structures, is calculated (see methods).
-This metric for model quality was used to classify models.
-\begin{figure}[h!]
+To asses the predictive power regarding the CDR-H3 loop, the software
+was tested on a test-set of antibody structures used in the 2014 and
+2011 Antibody Modelling Assessments
+\cite{Almagro2014},\cite{Almagro2011}. As the results depicted in
+\ref{fig:AMA} show, abYmod achieves results similar to, or better than
+other modelling programs. However, the outliers with very high RMSD
+values increase abYmod's RMSD average. The predictor in this work
+would aim to identify such outlier models.
+
+The predictive power of any machine learning model is largely
+dependent on the quality and size of the dataset it was trained on. As
+this is a non-linear, complex, multi-class classification problem, a
+substantial amount of data was required. Thus, an extensive, verified
+dataset of antibody structures called abYbank/AbDb\cite{Almagro2011},
+established by Prof. Andrew Martin, was utilised (1924 non-redundant
+structures). The root-mean-square deviation (RMSD) value, a measure of
+distance between backbone C-$\alpha$ atoms of superimposed crystal structures
+and modelled structures, is calculated (see methods). This metric for
+model quality was used to classify models.
+
+\begin{figure}
   \centering
-  \includegraphics[scale=0.3]{AMA}
-  \caption {RMSD values of the CDR-H3 loop for structures from the Antibody Modelling Assessment I
-(2011) and AMAII (2014). abYmod outperforms other modelling software in some instances, but
-also has much lower accuracy in few outlier cases. (left: an abYmod structure for C705 could be
-generated, yet the RMSD calculation failed. Right: Ab01 is the rabbit antibody PDB:4MA3,
-which was excluded in the CDR-H3 modelling stage in AMAII due to difficulties modelling the
-overall structure previously. Ab01 is shown for the methods, where generated models were
-adequate for RMSD calculation.)}
+  \includegraphics[scale=0.3]{AMA.eps}
+  \caption {RMSD values of the CDR-H3 loop for structures from the
+    Antibody Modelling Assessment I (2011) and AMAII (2014). abYmod
+    outperforms other modelling software in some instances, but also
+    has much lower accuracy in few outlier cases. (left: an abYmod
+    structure for C705 could be generated, yet the RMSD calculation
+    failed. Right: Ab01 is the rabbit antibody PDB:4MA3, which was
+    excluded in the CDR-H3 modelling stage in AMAII due to
+    difficulties modelling the overall structure previously. Ab01 is
+    shown for the methods, where generated models were adequate for
+    RMSD calculation.)}
   \label{fig:AMA}
 \end{figure}
-The full pipeline for creating the final machine learning model that will predict model quality by giving its RMSD range starts with a feature-set calculation using the antibody sequence.
-The feature set includes many different attributes linked to sequence, physical characteristics, interactions, etc.
-within as well as outside of the loop.
-There is a plethora of information to train our classifier on, including packing quality, protrusion, hydrophobicity, pseudo-energy (see protrusion, hydrophobicity, pseudo-energy (see methods for details).
-The sequence logo \ref{fig:logo} visualizes amino acid occurrence within the loop sequence, elements of which can be extracted as features \cite{Thomsen2012},\cite{Shaner1993}.
 
-\begin{figure}[h!]
-  \includegraphics[scale=0.9]{logo.png}
-  \caption {Sequence Logo of the CDRH3 loop sequence. Data on amino acid occurrence taken from http://abymod.abysis.org/. Visualized using Seq2Logo.}
+The full pipeline for creating the final machine learning model that
+will predict model quality by giving its RMSD range starts with a
+feature-set calculation using the antibody sequence. The feature set
+includes many different attributes linked to sequence, physical
+characteristics, interactions, etc. within as well as outside of the
+loop. There is a plethora of information to train our classifier on,
+including packing quality, protrusion, hydrophobicity, pseudo-energy
+(see protrusion, hydrophobicity, pseudo-energy (see methods for
+details). The sequence logo \ref{fig:logo} visualizes amino acid
+occurrence within the loop sequence, elements of which can be
+extracted as features \cite{Thomsen2012},\cite{Shaner1993}.
+
+\begin{figure}
+  \includegraphics[scale=0.9]{logo.eps}
+  \caption {Sequence Logo of the CDRH3 loop sequence. Data on amino
+    acid occurrence taken from http://abymod.abysis.org/. Visualized
+    using Seq2Logo.}
   \label{fig:logo}
 \end{figure}
-After creating the feature dataset, it is pre-processed (cleaning, scaling, encoding, see methods for details).
-Structures with a resolution below 4Å were removed given their low quality.
-Identical whole antibody structures were removed from the dataset, while instances of different antibodies that matched in loop sequence were not removed.
-Models of some of these structures with the same loop sequence differ significantly.
-The few large RMSD ranges may stem from low resolution, e.g.
-the highest datapoint contains a structure with a resolution of 3.00 Å.
-Residue differences near the loop may also explain the conformational difference.
-Some of these structures are complexed while others are not, which may also affect the loop structure.
 
-The dataset was also screened for any models which abYmod created using a template sequence from LoopDB, a database of CDR-H3 like loops from all proteins.
-This was not the case for any of our structures.
-The target data (i.e.
-RMSD values) are then transformed from numerical values to nominal values so that they can be used for classification.
-In order to define these nominal categories, the total RMSD range must be divided into categories.
-This is done either by creating uniform classes i.e.
-1-2Å, 2-3Å (the optimal size of which must be determined), etc.
-or by creating balanced classes.
-When creating balanced classes, the upper and lower thresholds of a category are chosen in such a way that each class contains an equal number of instances.
-This approach is chosen to counteract the skewness of the RMSD distribution.
-However, this was found to negatively affect the final model’s predictive power.
-Therefore, uniform classes were used.
-They are also transformed into a set of binary values according to a list of RMSD thresholds.
-This is done so that binary models can be trained, which will predict the probability e.g.
-that the model’s RMSD is above 2Å, 2.2Å, 2.4Å, and so on.
-The number of binary classifiers incorporated into the first layer have a great effect on the final model, the general
-trend being that the more binary classifiers are used, the better the nominal prediction. 
+After creating the feature dataset, it is pre-processed (cleaning,
+scaling, encoding, see methods for details). Structures with a
+resolution below 4\AA\ were removed given their low quality. Identical
+whole antibody structures were removed from the dataset, while
+instances of different antibodies that matched in loop sequence were
+not removed. Models of some of these structures with the same loop
+sequence differ significantly. The few large RMSD ranges may stem from
+low resolution, e.g. the highest datapoint contains a structure with a
+resolution of 3.00 \AA.  Residue differences near the loop may also
+explain the conformational difference. Some of these structures are
+complexed while others are not, which may also affect the loop
+structure.
+
+The dataset was also screened for any models which abYmod created
+using a template sequence from LoopDB, a database of CDR-H3 like loops
+from all proteins. This was not the case for any of our structures.
+
+The target data (i.e. RMSD values) are then transformed from numerical
+values to nominal values so that they can be used for
+classification. In order to define these nominal categories, the total
+RMSD range must be divided into categories. This is done either by
+creating uniform classes i.e. 1-2\AA, 2-3\AA\ (the optimal size of which
+must be determined), etc. or by creating balanced classes. When
+creating balanced classes, the upper and lower thresholds of a
+category are chosen in such a way that each class contains an equal
+number of instances. This approach is chosen to counteract the
+skewness of the RMSD distribution. However, this was found to
+negatively affect the final model's predictive power. Therefore,
+uniform classes were used.
+
+They are also transformed into a set of binary values according to a
+list of RMSD thresholds. This is done so that binary models can be
+trained, which will predict the probability e.g. that the model's RMSD
+is above 2\AA, 2.2\AA, 2.4\AA, and so on. The number of binary
+classifiers incorporated into the first layer have a great effect on
+the final model, the general trend being that the more binary
+classifiers are used, the better the nominal prediction.
+
 \subsection{Feature Encoding and Selection}
-\label{sec:sample2}
 
-As some features are in the form of amino acid codes, these must be encoded before they can be passed to a machine learning model.
-The encoding strategy often determines how efficiently the model learns and how much information can be extracted.
-Different strategies were employed to represent followed by BLOSUM62 and NLF encoding.
-The physiochemical encoding strategy was implemented for all models, being the most effective.
-However, PCA-3 BLOSUM62, a dimensionality-reduced BLOSUM62 encoding method achieved comparable results.
-Feature selection was conducted to improve the ML model’s learning capacity.
-A high-dimensional feature dataset bears the risk of introducing excessive noise, facilitating model overfitting and can be responsible for an overall decrease in model performance and stability.
-Each additionally inputted feature forces the model to handle a more complex task, which consumes excess computational power and time and leads to overfitting of the model.
+As some features are in the form of amino acid codes, these must be
+encoded before they can be passed to a machine learning model. The
+encoding strategy often determines how efficiently the model learns
+and how much information can be extracted. Different strategies were
+employed to represent followed by BLOSUM62 and NLF encoding. The
+physiochemical encoding strategy was implemented for all models, being
+the most effective. However, PCA-3 BLOSUM62, a dimensionality-reduced
+BLOSUM62 encoding method achieved comparable results.
 
-Our model is trained on different feature sets selected using manual selection as well as algorithmic selection strategies, in order to determine the most effective feature selection method.
-None of the feature selection methods was a best fit for all models.
+Feature selection was conducted to improve the ML model's learning
+capacity. A high-dimensional feature dataset bears the risk of
+introducing excessive noise, facilitating model overfitting and can be
+responsible for an overall decrease in model performance and
+stability. Each additionally inputted feature forces the model to
+handle a more complex task, which consumes excess computational power
+and time and leads to overfitting of the model.
 
-After the data is processed, it can be fed into different machine learning models.
-Different model types are investigated, as the most suited model-type has to be heuristically determined.
-We decided on the following list, which includes some of the most commonly used algorithms: logistic regression, linear discriminant analysis, K-nearest neighbours classifier, decision tree classifier, Gaussian NB, random forest classifier, support vector machine, probability-based voting (also known as soft voting) and extreme gradient boosting (XGBoost)\cite{Chen2016}.
+Our model is trained on different feature sets selected using manual
+selection as well as algorithmic selection strategies, in order to
+determine the most effective feature selection method. None of the
+feature selection methods was a best fit for all models.
 
-The best model, and its best hyperparameters, are then determined for each binary RMSD target.
-The set of binary models outputs a number of predictions that give the likelihood of the model having an RMSD above the threshold value of the respective model.
-These predictions are then added to the feature set, which a top-layer classifier is then trained on.
-Thus, a quasi-voting-system is incorporated into the final classifier, in which a set of weaker classifiers vote on the model quality.
+After the data is processed, it can be fed into different machine
+learning models. Different model types are investigated, as the most
+suited model-type has to be heuristically determined. We decided on
+the following list, which includes some of the most commonly used
+algorithms: logistic regression, linear discriminant analysis,
+K-nearest neighbours classifier, decision tree classifier, Gaussian
+NB, random forest classifier, support vector machine,
+probability-based voting (also known as soft voting) and extreme
+gradient boosting (XGBoost)\cite{Chen2016}.
+
+The best model, and its best hyperparameters, are then determined for
+each binary RMSD target. The set of binary models outputs a number of
+predictions that give the likelihood of the model having an RMSD above
+the threshold value of the respective model. These predictions are
+then added to the feature set, which a top-layer classifier is then
+trained on. Thus, a quasi-voting-system is incorporated into the final
+classifier, in which a set of weaker classifiers vote on the model
+quality.
 
 \subsection{Hyperparameter Optimization}
-\label{sec:sample2}
-In the process of hyperparameter optimization, the configuration of model parameters which results in best performance is selected. This is usually a computationally expensive and manual procedure.
-In an effort to automate this process, a population is defined for each model type, so hyperparameter optimization can be conducted automatically for each model and seamlessly integrated into the full model creation process.
-Two different methods for hyperparameter optimization were tested.
-The first is a hybrid approach of randomized search and grid search, the second uses a genetic algorithm for optimization.
-The genetic algorithm was found to achieve slightly better results and was selected for all models.
+In the process of hyperparameter optimization, the configuration of
+model parameters which results in best performance is selected. This
+is usually a computationally expensive and manual procedure.
+
+In an effort to automate this process, a population is defined for
+each model type, so hyperparameter optimization can be conducted
+automatically for each model and seamlessly integrated into the full
+model creation process. Two different methods for hyperparameter
+optimization were tested. The first is a hybrid approach of randomized
+search and grid search, the second uses a genetic algorithm for
+optimization. The genetic algorithm was found to achieve slightly
+better results and was selected for all models.
 
 \subsection{Model Performance}
-\label{sec:sample2}
-The overall best final model is composed of several different binary classifiers, with an extreme gradient boosting (XGBoost) top-layer nominal classifier.
-Features were selected using random forest feature selection.
-A final MCC value of 0.99 could be achieved for a model using the abYmod log file as input as well as the loop model file itself.
-This value slightly dropped to 0.92 if no such log file was given.
-This is mainly due to the fact that the template sequence abYmod used to generate the model is unknown in the latter case.
-The classifier predicts whether a model has an RMSD of below 2Å, between 2-4Å,or above 4Å.
-These cut-off values were selected based on the observation that abYmod generally produces a model with RMSD below 4Å.
-Incorrectly modelled structures (\ref{fig:AMA}) may be identified by screening for structures estimated to have an RMSD above 4Å.
-If a very high-quality model is needed one should also exclude models above 2Å.
+The overall best final model is composed of several different binary
+classifiers, with an extreme gradient boosting (XGBoost) top-layer
+nominal classifier. Features were selected using random forest feature
+selection. A final MCC value of 0.99 could be achieved for a model
+using the abYmod log file as input as well as the loop model file
+itself. This value slightly dropped to 0.92 if no such log file was
+given. This is mainly due to the fact that the template sequence
+abYmod used to generate the model is unknown in the latter case.
 
-\section{Discussion}
-The results suggest that our presented classifier can differentiate between well-modelled and less well-modelled CDR-H3 loop structures.
-An MCC value of 0.99 was achieved, which underlines this ability for accurate discrimination.
-Different methods for data pre-processing, feature encoding, feature selection and hyperparameter optimization were tested.
-Feature encoding methods that were very high-dimensional (one-hot-encoding, BLOSUM62, NLF) were found to be unfavorable.
-Dimensionality reduction methods (Principal Component Analysis (PCA), Independent Component Analysis (ICA), projection-based methods e.g.
-t-SNE) were used on BLOSUM62 encoded matrices, which lead to significant improvement.
-However, a physiochemical encoding strategy was most effective.
-The selection of features incorporated in the training set seemed to be most important for effective learning.
-A multitude of methods were tested.
-No one-fit-for-all method for the different models could be found.
-However, for our top-layer classifier in our final model recursive feature elimination worked best.
-A set of commonly used machine learning algorithms were tested, and the best ML models were incorporated into the final ensemble model.
-A stacked model approach (consisting of 23 binary classifiers and a single top-layer nominal classifier) was shown to outperform single ML models.
-An MCC value of 0.99 was achieved for a classifier predicting whether an input-model has an RMSD value below 2Å, 2Å-4Å or above 4Å. 
-Given that abYbank/AbDb is soon to be expanded by an additional ca. 2000 structures, classifier performance on models without a known abYmod-template sequence may be improved by a larger dataset. 
-It is conceivable that the described predictor may also be incorporated in the antibody modelling process as a low-quality filter in the future, flagging certain structures for re-modelling.
+The classifier predicts whether a model has an RMSD of below 2\AA,
+between 2-4\AA, or above 4\AA. These cut-off values were selected
+based on the observation that abYmod generally produces a model with
+RMSD below 4\AA. Incorrectly modelled structures (\ref{fig:AMA}) may
+be identified by screening for structures estimated to have an RMSD
+above 4\AA. If a very high-quality model is needed one should also
+exclude models above 2\AA.
 
- In a future research project residue patterns in correlation with RMSD may be analyzed.
-Possibly, one might identify certain sequence patterns that make accurate modelling with abYmod more difficult.
-Furthermore, separate classifiers according to loop length can be built.
-Given that loop length is the most important determinant of model quality, this approach may yield some insight into the challenges of modelling shorter vs longer loops.
-One could also conduct an analysis of the predictor’s behaviour when abYmod is forced to use LoopDB-based modelling.
-This might shed light on whether the ML model presented in this paper is biased towards abYmod’s used source of template structures.
-It would also give an indication of how well the predictor would work in combination with other modelling software.
+\section{Methods}
 
-\bibliographystyle{elsarticle-num} 
-\bibliography{references}
+\subsection{Computing}
+All machine learning and, feature selection and hyperparameter
+optimization algorithms were implemented in Python. The Scikit-learn
+library was used for training models, the
+Yellowbrick\cite{Bengfort2021} library was utilized for
+visualization. All code is available at
+https://github.com/LilianDenzler/qualiloop .
 
-\appendix{}
-\section{Experimental Procedures}
-\subsection{Computing}
-All machine learning and, feature selection and hyperparameter optimization algorithms were implemented in Python.
-The Scikit-learn library was used for training models, the Yellowbrick\cite{Bengfort2021} library was utilized for visualization.
-All code is available at https://github.com/LilianDenzler/qualiloop .
-The code was run under CentOS 7 on an 8-core virtual machine on an Intel Xeon 4208 CPU with 16Gig RAM.
+The code was run under CentOS 7 on an 8-core virtual machine on an
+Intel Xeon 4208 CPU with 16Gig RAM.
 
 \subsection{Data Pre-Processing and Preparation}
-Handling Null Values and Duplicates: The dataset containing target RMSD values, and the calculated features was screened for null values.
-If a feature column contained more than 5\% null values, it was dropped (none removed).
-Rows that contained any null values were removed from the dataset (11 rows in total).
+Handling Null Values and Duplicates: The dataset containing target
+RMSD values, and the calculated features was screened for null
+values. If a feature column contained more than 5\% null values, it
+was dropped (none removed). Rows that contained any null values were
+removed from the dataset (11 rows in total).
 
-\subsubsection{Duplicate Screening} Using AbDb’s redundancy information it was ensured that no antibodies were present in the dataset more than once.
-The dataset is additionally screened for duplicate instances.
+\subsubsection{Duplicate Screening}
+Using AbDb's redundancy information it was ensured that no antibodies
+were present in the dataset more than once. The dataset is
+additionally screened for duplicate instances.
 
-\subsubsection{Scaling} Normalization and Standardization are tested as scaling methods.
-Both approaches are greatly influenced by outliers, and such datapoints are ideally removed for optimal scaling.
-Here we define outliers as datapoints that lie over 1.5 times the interquartile range (IQR) below the first quartile or above the third quartile.
-The IQR is defined as the range between quartile 1, i.e.
-the median of the lower half of the data, and quartile 3, i.e.
-the median of the upper half of the
-data.
-However, across all features there are a total of 632 outlier values and removing such a large number of datapoints is not a viable option.
-A robust scaler was also used, which uses statistics that are robust to outliers.
-The median is set to zero and numerical features are scaled to the interquartile range.
+\subsubsection{Scaling}
+Normalization and Standardization are tested as scaling methods. Both
+approaches are greatly influenced by outliers, and such datapoints are
+ideally removed for optimal scaling. Here we define outliers as
+datapoints that lie over 1.5 times the interquartile range (IQR) below
+the first quartile or above the third quartile. The IQR is defined as
+the range between quartile 1, i.e. the median of the lower half of the
+data, and quartile 3, i.e. the median of the upper half of the
+data. However, across all features there are a total of 632 outlier
+values and removing such a large number of datapoints is not a viable
+option. A robust scaler was also used, which uses statistics that are
+robust to outliers. The median is set to zero and numerical features
+are scaled to the interquartile range.
 
-\subsubsection{BLOSUM 62 encoding} The BLOSUM62 matrix reflects the frequencies of amino acid substitutions within a locally aligned, conserved regions of proteins with at least 62\% similarity.
-Each amino acid is represented by a row (or column) of the BLOSUM62 matrix.
-Dimensionality reduction techniques are employed: Principal Component Analysis (PCA), Independent Component Analysis (ICA), projection-based methods (t-SNE, Isomap).
-Three components were used as features.
+\subsubsection{BLOSUM 62 encoding}
+The BLOSUM62 matrix reflects the frequencies of amino acid
+substitutions within a locally aligned, conserved regions of proteins
+with at least 62\% similarity. Each amino acid is represented by a row
+(or column) of the BLOSUM62 matrix. Dimensionality reduction
+techniques are employed: Principal Component Analysis (PCA),
+Independent Component Analysis (ICA), projection-based methods (t-SNE,
+Isomap). Three components were used as features.
 
-\subsubsection{Physiochemical Feature Encoding} In a paper by L. Nanni and A.Lumini a new encoding technique is 
-presented which was developed for machine learning classifiers.
-Many physiochemical properties are calculated and transformed using a non-linear Fisher transform for dimensionality reduction.
-A vector of length 19 is produced for each amino acid34.
-In a paper on designing a neural network for predicting the packing angle of the light and heavy variable chain of an antibodies, A.C.R.
-Martin and K.R.
-Abhinandan introduce an encoding method that produces a four-dimensional physiochemical feature vector25.
-The amino acid properties used are 1) the total number of side-chain atoms, 2) the number of side-chain atoms in the shortest path from Cα to the most distal atom, 3) the Eisenberg consensus hydrophobicity\cite{Eisenberg1982}, 4) the charge.
+\subsubsection{Physiochemical Feature Encoding}
+In a paper by L. Nanni and A.Lumini a new encoding technique is
+presented which was developed for machine learning classifiers. Many
+physiochemical properties are calculated and transformed using a
+non-linear Fisher transform for dimensionality reduction.  A vector of
+length 19 is produced for each amino acid34.  In a paper on designing
+a neural network for predicting the packing angle of the light and
+heavy variable chain of an antibodies, A.C.R. Martin and
+K.R. Abhinandan introduce an encoding method that produces a
+four-dimensional physiochemical feature vector25. The amino acid
+properties used are 1) the total number of side-chain atoms, 2) the
+number of side-chain atoms in the shortest path from C$\alpha$ to the most
+distal atom, 3) the Eisenberg consensus
+hydrophobicity\cite{Eisenberg1982}, 4) the charge.
 
 \subsection{Dataset-splitting}
- The final model was evaluated using a test set, separated from the training set at the start in a 30/70 split (lock-box principle) 35.
-The performance of all individual sub-models of the first layer are determined using stratified K-folds cross-validation (k=10) as the dataset is imbalanced, being skewed towards lower RMSD values.
-The method is differentiable from K-folds cross validation as it uses stratified sampling instead of random sampling.
-This ensures each class is represented, as the percentage of samples for each class are preserved.
-A validation set, usually used for testing during the optimization stage will be omitted in favour of stratified K-folds cross-validation (k=10) \cite{Krstajic2014} \cite{Kohavi1995}.
+The final model was evaluated using a test set, separated from the
+training set at the start in a 30/70 split (lock-box principle)
+35. The performance of all individual sub-models of the first layer
+are determined using stratified K-folds cross-validation (k=10) as the
+dataset is imbalanced, being skewed towards lower RMSD values. The
+method is differentiable from K-folds cross validation as it uses
+stratified sampling instead of random sampling. This ensures each
+class is represented, as the percentage of samples for each class are
+preserved.
+
+A validation set, usually used for testing during the optimization
+stage will be omitted in favour of stratified K-folds cross-validation
+(k=10) \cite{Krstajic2014} \cite{Kohavi1995}.
 
 \subsection{Model Assessment} 
-Model assessment must be considered at two levels as performance metrics of binary and multi-class classifiers are calculated differently and must thus be considered separately.
-The Mathews Correlation Coefficient (MCC) \cite{Matthews1975} is deemed the most informative, taking the ratios of the four confusion matrix categories into account 39and is thus more reliable than the F1 score and accuracy .
-It is also consistent for both binary and multi-class problems and therefore well suited for our purpose.
+Model assessment must be considered at two levels as performance
+metrics of binary and multi-class classifiers are calculated
+differently and must thus be considered separately. The Mathews
+Correlation Coefficient (MCC) \cite{Matthews1975} is deemed the most
+informative, taking the ratios of the four confusion matrix categories
+into account 39and is thus more reliable than the F1 score and
+accuracy . It is also consistent for both binary and multi-class
+problems and therefore well suited for our purpose.
 
 \subsection{Feature Calculations}
-\begin{figure}[h!]
+\begin{figure}
   \centering
-  \includegraphics[scale=0.49]{feature_table.png}
+  \includegraphics[scale=0.49]{feature_table.eps}
   \caption {A summary of how different feature values were calculated.}
@@
 
-\begin{figure}[h!]
-  \includegraphics[scale=0.6]{angle.png}
-  \caption {Diagram visualizing the process underlying the protrusion calculation.
-First, the base residues (i.e H95 and H102, shown as red spheres) of the CDR-H3 (shown in red) are identified.
-Then, a line is drawn between the two Cα atoms of these residues (yellow dashed line).
-The distance of the Cα-atom of each residue in the CDR-H3 loop to this line is calculated.
-The residue which has the greatest distance to the line (shown as green sphere) is outputted as one-letter amino acid code and used as feature.
-The distance in Å (depicted as yellow arrow) is used as the ‘protrusion’ feature.
-}
+\begin{figure}
+  \includegraphics[scale=0.6]{angle.eps}
+  \caption {Diagram visualizing the process underlying the protrusion
+    calculation. First, the base residues (i.e H95 and H102, shown as
+    red spheres) of the CDR-H3 (shown in red) are identified. Then, a
+    line is drawn between the two C$\alpha$ atoms of these residues (yellow
+    dashed line). The distance of the C$\alpha$-atom of each residue in the
+    CDR-H3 loop to this line is calculated. The residue which has the
+    greatest distance to the line (shown as green sphere) is outputted
+    as one-letter amino acid code and used as feature. The distance in
+    \AA\ (depicted as yellow arrow) is used as the ‘protrusion'
+    feature. }
   \label{fig:angle}
@@
 
-\begin{figure}[h!]
-  \includegraphics[scale=0.45]{method.png}
-  \caption {Simplified pipeline for creating the final machine learning model that will predict model quality by giving its RMSD range.}
+\begin{figure}
+  \includegraphics[scale=0.45]{method.eps}
+  \caption {Simplified pipeline for creating the final machine
+    learning model that will predict model quality by giving its RMSD
+    range.}
   \label{fig:method}
@@
 
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
+\section{Discussion}
+The results suggest that our presented classifier can differentiate
+between well-modelled and less well-modelled CDR-H3 loop
+structures. An MCC value of 0.99 was achieved, which underlines this
+ability for accurate discrimination. Different methods for data
+pre-processing, feature encoding, feature selection and hyperparameter
+optimization were tested.
 
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
+Feature encoding methods that were very high-dimensional
+(one-hot-encoding, BLOSUM62, NLF) were found to be
+unfavorable. Dimensionality reduction methods (Principal Component
+Analysis (PCA), Independent Component Analysis (ICA), projection-based
+methods e.g. t-SNE) were used on BLOSUM62 encoded matrices, which lead
+to significant improvement. However, a physiochemical encoding
+strategy was most effective.
+
+The selection of features incorporated in the training set seemed to
+be most important for effective learning. A multitude of methods were
+tested. No one-fit-for-all method for the different models could be
+found. However, for our top-layer classifier in our final model
+recursive feature elimination worked best.
+
+A set of commonly used machine learning algorithms were tested, and
+the best ML models were incorporated into the final ensemble model. A
+stacked model approach (consisting of 23 binary classifiers and a
+single top-layer nominal classifier) was shown to outperform single ML
+models.
+
+An MCC value of 0.99 was achieved for a classifier predicting whether
+an input-model has an RMSD value below 2\AA, 2\AA--4\AA\ or above
+4\AA.
+
+Given that abYbank/AbDb is soon to be expanded by an additional
+ca. 2000 structures, classifier performance on models without a known
+abYmod-template sequence may be improved by a larger dataset.
+
+It is conceivable that the described predictor may also be
+incorporated in the antibody modelling process as a low-quality filter
+in the future, flagging certain structures for re-modelling.
+
+In a future research project residue patterns in correlation with RMSD
+may be analyzed. Possibly, one might identify certain sequence
+patterns that make accurate modelling with abYmod more
+difficult. Furthermore, separate classifiers according to loop length
+can be built. Given that loop length is the most important determinant
+of model quality, this approach may yield some insight into the
+challenges of modelling shorter vs longer loops.
+
+One could also conduct an analysis of the predictor's behaviour when
+abYmod is forced to use LoopDB-based modelling. This might shed light
+on whether the ML model presented in this paper is biased towards
+abYmod's used source of template structures. It would also give an
+indication of how well the predictor would work in combination with
+other modelling software.
+
+\bibliography{references}
 
 \end{document}
-\endinput
-%%
-%% End of file `elsarticle-template-num.tex'.

### 2022-10-05 paper.tex
A4 and CDR-H3 standardization

@@
 \bibliographystyle{unsrt}
+\usepackage{a4}
 \usepackage{graphicx}
@@
   except for one. It remains markedly difficult to model the third CDR
-  loop of the antibody heavy chain. The CDRH3 differs in length, has
+  loop of the antibody heavy chain. The CDR-H3 differs in length, has
   far greater sequence variability and has such a great structural
@@
   abYmod software, have been developed. Although such efforts have
-  improved prediction accuracy the results for the CDRH3 loop are
+  improved prediction accuracy the results for the CDR-H3 loop are
   still inconsistent and require further improvement. Providing a
@@
   We present a model quality predictor, combining domain knowledge
-  with machine learning techniques to predict the accuracy of CDRH3
+  with machine learning techniques to predict the accuracy of CDR-H3
   models generated by antibody modelling software such as abYmod. The
@@
 \cite{North2011},\cite{Weitzner2015}. However, the CDR loop 3 of the
-heavy chain (CDRH3) has a far greater sequence variability due to the
+heavy chain (CDR-H3) has a far greater sequence variability due to the
 processes of V(D)J recombination and somatic hyper‐mutation and its
@@
 even compared to other protein loops \cite{Regep2017}. It was found
-that over 75\% of CDRH3 loops do not have a sub-Angstrom non-antibody
-structural neighbour, as well as that 30\% of CDRH3 loops have a
+that over 75\% of CDR-H3 loops do not have a sub-Angstrom non-antibody
+structural neighbour, as well as that 30\% of CDR-H3 loops have a
 completely unique structure compared with under 3\% for all other
@@
 
-Apart from being the most structurally diverse, the H3 loop is also
+Apart from being the most structurally diverse, the CDR-H3 loop is also
 the most important for antigen binding, being located at the center of
@@
 
-According to the Kabat definition, the CDRH3 loop is made up of the
+According to the Kabat definition, the CDR-H3 loop is made up of the
 residues 95-105 (Kabat numbering scheme\cite{Kabat1992}) in the heavy
@@
   \caption { Distribution of CDR-H3 loop lengths in mouse (left),
-    human (centre) and cow (right). Mouse and human antibody CDRH3s
+    human (centre) and cow (right). Mouse and human antibody CDR-H3s
     have a unimodal, yet almost normal distribution with a range of
-    ca. 4-28 and 4-38 respectively. The length cut-off for CDRH3s
+    ca. 4-28 and 4-38 respectively. The length cut-off for CDR-H3s
     depicted above is 30 amino acids. Bovine antibodies with
@@
 For shorter loops, a higher prediction accuracy can be achieved than
-for longer CDRH3 loops. This was also shown by the Antibody Modelling
+for longer CDR-H3 loops. This was also shown by the Antibody Modelling
 Assessments (AMA), two blind contests that required researchers to
@@
 length for CDR-H3, the loop is built using the LoopDB database,
-containing CDRH3-like loops from all proteins. Finally, Gromacs energy
+containing CDR-H3-like loops from all proteins. Finally, Gromacs energy
 minimization software is used to optimize the model. This method has
@@
 
-Modelling the H3 loop is a hurdle for in silico development of
+Modelling the CDR-H3 loop is a hurdle for in silico development of
 therapeutic antibodies. Currently, there is no definite, reliable way
@@
 H3 region. Therefore, the aim of this project will be to produce a
-user-friendly predictor of H3 model quality. The predictor will give
+user-friendly predictor of CDR-H3 model quality. The predictor will give
 the user an RMSD-range in {\AA}ngstr\"{o}ms, in which the generated model lies
@@
   \includegraphics[scale=0.9]{logo.eps}
-  \caption {Sequence Logo of the CDRH3 loop sequence. Data on amino
+  \caption {Sequence Logo of the CDR-H3 loop sequence. Data on amino
     acid occurrence taken from http://abymod.abysis.org/. Visualized

### 2022-10-05 paper.tex
Standardized citations

@@
 Furthermore, in contrast with small drug molecules, antibodies can not
-only bind pockets, but also flat, concave or even convex surfaces
-\cite{Tavers2001}. Their unique characteristics have enabled
+only bind pockets, but also flat, concave or even convex surfaces\cite{Tavers2001}. Their unique characteristics have enabled
 researchers to develop efficient antibody drugs for treating cancers,
-autoimmune disorders, infectious diseases and many more \cite{Lu2020}.
+autoimmune disorders, infectious diseases and many more\cite{Lu2020}.
 Their ability to target an immense variety of antigens allows for
@@
 valued at USD 130.9 billion in 2020, estimated to grow 223.7 billion
-by the end of 2025 at a compound annual growth rate of 11.31\%
-\cite{market2020}. Four of the top 10 best-selling drugs in 2020 were
-monoclonal antibodies \cite{Urquhart2021}.
+by the end of 2025 at a compound annual growth rate of 11.31\%\cite{market2020}. Four of the top 10 best-selling drugs in 2020 were
+monoclonal antibodies\cite{Urquhart2021}.
 
@@
 predicting both the exact binding site and the antibody stability as
-well as assessing immunogenicity \cite{Abhinandan2007}. As
+well as assessing immunogenicity\cite{Abhinandan2007}. As
 experimental structure determination is very costly and time
@@
 into a limited number of canonical structures. Therefore, modelling
-these loops with adequate accuracy is commonly achievable
-\cite{North2011},\cite{Weitzner2015}. However, the CDR loop 3 of the
+these loops with adequate accuracy is commonly achievable\cite{North2011,Weitzner2015}. However, the CDR loop 3 of the
 heavy chain (CDR-H3) has a far greater sequence variability due to the
 processes of V(D)J recombination and somatic hyper‐mutation and its
-structure has remained unclassifiable \cite{Finn2016}. The variety in
+structure has remained unclassifiable\cite{Finn2016}. The variety in
 structure is so great, that its structural diversity is remarkable
-even compared to other protein loops \cite{Regep2017}. It was found
+even compared to other protein loops\cite{Regep2017}. It was found
 that over 75\% of CDR-H3 loops do not have a sub-Angstrom non-antibody
@@
 completely unique structure compared with under 3\% for all other
-loops on average \cite{Regep2017}.
+loops on average\cite{Regep2017}.
 
@@
 the most important for antigen binding, being located at the center of
-the binding site and forming the most contacts to the antigen
-\cite{MacCallum1996}. In fact, it was demonstrated that differences in
+the binding site and forming the most contacts to the antigen\cite{MacCallum1996}. In fact, it was demonstrated that differences in
 this loop alone were sufficient to enable otherwise identical
-antibodies to distinguish between various antigens \cite{Xu2000}.
+antibodies to distinguish between various antigens\cite{Xu2000}.
 
@@
     reaching a length of 67 amino acids and
-    above. \protect\cite{Wong2015}}  
+    above\protect\cite{Wong2015}.}  
   \label{fig:loopdist}
@@
 modelling quality achieved at the contests was on average much lower
-for loops of longer lengths \cite{Almagro2011},\cite{Almagro2014}.
+for loops of longer lengths\cite{Almagro2011,Almagro2014}.
 
 Several different approaches for generating three-dimensional
-structure models from antibody sequences exist such as RosettaAntibody
-\cite{Sircar2009},\cite{Sivasubramanian2009},
+structure models from antibody sequences exist such as RosettaAntibody\cite{Sircar2009,Sivasubramanian2009},
 ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017} and abYmod,
@@
 specific angle restraints which bias the conformational space towards
-so-called ‘kinked' loops\cite{Schoeder2021},\cite{Weitzner2017}. In
+so-called `kinked' loops\cite{Schoeder2021,Weitzner2017}. In
 contrast, ABodyBuilder uses a database search algorithm
@@
 results. Upon inputting an antibody sequence, abYmod assigns the
-canonical class using a set of key residues \cite{Martin1996}and where
+canonical class using a set of key residues\cite{Martin1996}and where
 an exact match is not possible, a nearest match is made. Then, the
@@
 model. The given score is the probability that a specific region
-(e.g. CDR-H2) will be will be modeled within a specific RMSD threshold
-\cite{Leem2016}. Thus, it can be used to obtain an expected RMSD
+(e.g. CDR-H2) will be will be modeled within a specific RMSD threshold\cite{Leem2016}. Thus, it can be used to obtain an expected RMSD
 value for a given probability (default 75\%). For the CDR-H3 this
@@
 scorer is described as robust, but less accurate in the case of CDR
-loops due to the lack of data.\cite{Leem2016} ABLooper also provides a
+loops due to the lack of data\cite{Leem2016}. ABLooper also provides a
 confidence metric for the CDR-H3 loop model, which is estimated by the
 diversity of a set of predicted conformations for the same
-loop\cite{Abanades2022}.However, it remains unclear whether a high
+loop\cite{Abanades2022}. However, it remains unclear whether a high
 prediction diversity score points towards loops with multiple
@@
 2011 Antibody Modelling Assessments
-\cite{Almagro2014},\cite{Almagro2011}. As the results depicted in
+\cite{Almagro2011,Almagro2014}. As the results depicted in
 \ref{fig:AMA} show, abYmod achieves results similar to, or better than
@@
 substantial amount of data was required. Thus, an extensive, verified
-dataset of antibody structures called abYbank/AbDb\cite{Almagro2011},
+dataset of antibody structures called abYbank/AbDb\cite{XXXX},
 established by Prof. Andrew Martin, was utilised (1924 non-redundant
@@
 occurrence within the loop sequence, elements of which can be
-extracted as features \cite{Thomsen2012},\cite{Shaner1993}.
+extracted as features \cite{Thomsen2012,Shaner1993}.
 
@@
 stage will be omitted in favour of stratified K-folds cross-validation
-(k=10) \cite{Krstajic2014} \cite{Kohavi1995}.
+(k=10)\cite{Krstajic2014,Kohavi1995}.
 
@@
 differently and must thus be considered separately. The Mathews
-Correlation Coefficient (MCC) \cite{Matthews1975} is deemed the most
+Correlation Coefficient (MCC)\cite{Matthews1975} is deemed the most
 informative, taking the ratios of the four confusion matrix categories
@@
     as one-letter amino acid code and used as feature. The distance in
-    \AA\ (depicted as yellow arrow) is used as the ‘protrusion'
+    \AA\ (depicted as yellow arrow) is used as the `protrusion'
     feature. }

### 2022-10-05 paper.tex
Reformatted
Added C-alpha macro

@@
 \usepackage{url}
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
+\newcommand{\ca}{\mbox{C$\alpha$}}
 
@@
 Furthermore, in contrast with small drug molecules, antibodies can not
-only bind pockets, but also flat, concave or even convex surfaces\cite{Tavers2001}. Their unique characteristics have enabled
+only bind pockets, but also flat, concave or even convex
+surfaces\cite{Tavers2001}. Their unique characteristics have enabled 
 researchers to develop efficient antibody drugs for treating cancers,
@@
 valued at USD 130.9 billion in 2020, estimated to grow 223.7 billion
-by the end of 2025 at a compound annual growth rate of 11.31\%\cite{market2020}. Four of the top 10 best-selling drugs in 2020 were
-monoclonal antibodies\cite{Urquhart2021}.
+by the end of 2025 at a compound annual growth rate of
+11.31\%\cite{market2020}. Four of the top 10 best-selling drugs in
+2020 were monoclonal antibodies\cite{Urquhart2021}.
 
@@
 
-Apart from being the most structurally diverse, the CDR-H3 loop is also
-the most important for antigen binding, being located at the center of
-the binding site and forming the most contacts to the antigen\cite{MacCallum1996}. In fact, it was demonstrated that differences in
-this loop alone were sufficient to enable otherwise identical
-antibodies to distinguish between various antigens\cite{Xu2000}.
+Apart from being the most structurally diverse, the CDR-H3 loop is
+also the most important for antigen binding, being located at the
+center of the binding site and forming the most contacts to the
+antigen\cite{MacCallum1996}. In fact, it was demonstrated that
+differences in this loop alone were sufficient to enable otherwise
+identical antibodies to distinguish between various
+antigens\cite{Xu2000}.
 
@@
 Several different approaches for generating three-dimensional
-structure models from antibody sequences exist such as RosettaAntibody\cite{Sircar2009,Sivasubramanian2009},
+structure models from antibody sequences exist such as
+RosettaAntibody\cite{Sircar2009,Sivasubramanian2009}, 
 ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017} and abYmod,
@@
 model. The given score is the probability that a specific region
-(e.g. CDR-H2) will be will be modeled within a specific RMSD threshold\cite{Leem2016}. Thus, it can be used to obtain an expected RMSD
-value for a given probability (default 75\%). For the CDR-H3 this
+(e.g. CDR-H2) will be will be modeled within a specific RMSD
+threshold\cite{Leem2016}. Thus, it can be used to obtain an expected
+RMSD value for a given probability (default 75\%). For the CDR-H3 this
 score is calculated as a function of the loop length.  The confidence
@@
 structures). The root-mean-square deviation (RMSD) value, a measure of
-distance between backbone C-$\alpha$ atoms of superimposed crystal structures
+distance between backbone \ca\ atoms of superimposed crystal structures
 and modelled structures, is calculated (see methods). This metric for
@@
 properties used are 1) the total number of side-chain atoms, 2) the
-number of side-chain atoms in the shortest path from C$\alpha$ to the most
+number of side-chain atoms in the shortest path from \ca\ to the most
 distal atom, 3) the Eisenberg consensus
@@
     red spheres) of the CDR-H3 (shown in red) are identified. Then, a
-    line is drawn between the two C$\alpha$ atoms of these residues (yellow
-    dashed line). The distance of the C$\alpha$-atom of each residue in the
+    line is drawn between the two \ca\ atoms of these residues (yellow
+    dashed line). The distance of the \ca-atom of each residue in the
     CDR-H3 loop to this line is calculated. The residue which has the

### 2022-10-05 paper.tex
Fixed i.e. and e.g.

@@
 ABodyBuilder is a modelling server that provides the user with a
-confidence score for each region (e.g.CDR-H2) of the antibody
+confidence score for each region (e.g.\ CDR-H2) of the antibody
 model. The given score is the probability that a specific region
-(e.g. CDR-H2) will be will be modeled within a specific RMSD
+(e.g.\ CDR-H2) will be will be modeled within a specific RMSD
 threshold\cite{Leem2016}. Thus, it can be used to obtain an expected
@@
 sequence differ significantly. The few large RMSD ranges may stem from
-low resolution, e.g. the highest datapoint contains a structure with a
+low resolution, e.g.\ the highest datapoint contains a structure with a
 resolution of 3.00 \AA.  Residue differences near the loop may also
@@
 
-The target data (i.e. RMSD values) are then transformed from numerical
+The target data (i.e.\ RMSD values) are then transformed from numerical
 values to nominal values so that they can be used for
@@
 RMSD range must be divided into categories. This is done either by
-creating uniform classes i.e. 1-2\AA, 2-3\AA\ (the optimal size of which
+creating uniform classes i.e.\ 1-2\AA, 2-3\AA\ (the optimal size of which
 must be determined), etc. or by creating balanced classes. When
@@
 list of RMSD thresholds. This is done so that binary models can be
-trained, which will predict the probability e.g. that the model's RMSD
+trained, which will predict the probability e.g.\ that the model's RMSD
 is above 2\AA, 2.2\AA, 2.4\AA, and so on. The number of binary
@@
 the first quartile or above the third quartile. The IQR is defined as
-the range between quartile 1, i.e. the median of the lower half of the
-data, and quartile 3, i.e. the median of the upper half of the
+the range between quartile 1, i.e.\ the median of the lower half of the
+data, and quartile 3, i.e.\ the median of the upper half of the
 data. However, across all features there are a total of 632 outlier
@@
 Analysis (PCA), Independent Component Analysis (ICA), projection-based
-methods e.g. t-SNE) were used on BLOSUM62 encoded matrices, which lead
+methods e.g.\ t-SNE) were used on BLOSUM62 encoded matrices, which lead
 to significant improvement. However, a physiochemical encoding

### 2022-10-05 paper.tex
Fixed Figure references

@@
 to a large range of loop lengths, with bovine antibodies being
-exceptionally long \ref{fig:loopdist}.
+exceptionally long (Figure~\ref{fig:loopdist}).
 
@@
 \cite{Almagro2011,Almagro2014}. As the results depicted in
-\ref{fig:AMA} show, abYmod achieves results similar to, or better than
+Figure~\ref{fig:AMA} show, abYmod achieves results similar to, or better than
 other modelling programs. However, the outliers with very high RMSD
@@
 (see protrusion, hydrophobicity, pseudo-energy (see methods for
-details). The sequence logo \ref{fig:logo} visualizes amino acid
+details). The sequence logo (Figure~\ref{fig:logo}) visualizes amino acid
 occurrence within the loop sequence, elements of which can be
@@
 based on the observation that abYmod generally produces a model with
-RMSD below 4\AA. Incorrectly modelled structures (\ref{fig:AMA}) may
+RMSD below 4\AA. Incorrectly modelled structures (Figure~\ref{fig:AMA}) may
 be identified by screening for structures estimated to have an RMSD

### 2022-10-05 paper.tex
Fixed all full-stops commas and dashes

@@
 into a limited number of canonical structures. Therefore, modelling
-these loops with adequate accuracy is commonly achievable\cite{North2011,Weitzner2015}. However, the CDR loop 3 of the
+these loops with adequate accuracy is commonly
+achievable\cite{North2011,Weitzner2015}. However, the CDR loop 3 of
+the 
 heavy chain (CDR-H3) has a far greater sequence variability due to the
@@
 ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017} and abYmod,
-UCL's in-house software developed by Prof. Martin. One of the most
+UCL's in-house software developed by Prof.\ Martin. One of the most
 used methods is RosettaAntibody, which implements template selection
@@
 dataset of antibody structures called abYbank/AbDb\cite{XXXX},
-established by Prof. Andrew Martin, was utilised (1924 non-redundant
+established by Prof.\ Andrew Martin, was utilised (1924 non-redundant
 structures). The root-mean-square deviation (RMSD) value, a measure of
@@
 includes many different attributes linked to sequence, physical
-characteristics, interactions, etc. within as well as outside of the
+characteristics, interactions, etc., within as well as outside of the
 loop. There is a plethora of information to train our classifier on,
@@
   \caption {Sequence Logo of the CDR-H3 loop sequence. Data on amino
-    acid occurrence taken from http://abymod.abysis.org/. Visualized
+    acid occurrence taken from http://abymod.abysis.org/ Visualized
     using Seq2Logo.}
@@
 low resolution, e.g.\ the highest datapoint contains a structure with a
-resolution of 3.00 \AA.  Residue differences near the loop may also
+resolution of 3.00~\AA.  Residue differences near the loop may also
 explain the conformational difference. Some of these structures are
@@
 RMSD range must be divided into categories. This is done either by
-creating uniform classes i.e.\ 1-2\AA, 2-3\AA\ (the optimal size of which
+creating uniform classes i.e.\ 1-2~\AA, 2-3~\AA\ (the optimal size of which
 must be determined), etc. or by creating balanced classes. When
@@
 trained, which will predict the probability e.g.\ that the model's RMSD
-is above 2\AA, 2.2\AA, 2.4\AA, and so on. The number of binary
+is above 2~\AA, 2.2~\AA, 2.4~\AA, and so on. The number of binary
 classifiers incorporated into the first layer have a great effect on
@@
 
-The classifier predicts whether a model has an RMSD of below 2\AA,
-between 2-4\AA, or above 4\AA. These cut-off values were selected
+The classifier predicts whether a model has an RMSD of below 2~\AA,
+between 2-4~\AA, or above 4~\AA. These cut-off values were selected
 based on the observation that abYmod generally produces a model with
-RMSD below 4\AA. Incorrectly modelled structures (Figure~\ref{fig:AMA}) may
+RMSD below 4~\AA. Incorrectly modelled structures (Figure~\ref{fig:AMA}) may
 be identified by screening for structures estimated to have an RMSD
-above 4\AA. If a very high-quality model is needed one should also
-exclude models above 2\AA.
+above 4~\AA. If a very high-quality model is needed one should also
+exclude models above 2~\AA.
 
@@
 visualization. All code is available at
-https://github.com/LilianDenzler/qualiloop .
+https://github.com/LilianDenzler/qualiloop
 
@@
 \subsubsection{Physiochemical Feature Encoding}
-In a paper by L. Nanni and A.Lumini a new encoding technique is
+In a paper by L.~Nanni and A.~Lumini a new encoding technique is
 presented which was developed for machine learning classifiers. Many
@@
 a neural network for predicting the packing angle of the light and
-heavy variable chain of an antibodies, A.C.R. Martin and
-K.R. Abhinandan introduce an encoding method that produces a
+heavy variable chain of an antibodies, A.C.R.~Martin and
+K.R.~Abhinandan introduce an encoding method that produces a
 four-dimensional physiochemical feature vector25. The amino acid
@@
 into account 39and is thus more reliable than the F1 score and
-accuracy . It is also consistent for both binary and multi-class
+accuracy. It is also consistent for both binary and multi-class
 problems and therefore well suited for our purpose.
@@
   \caption {Diagram visualizing the process underlying the protrusion
-    calculation. First, the base residues (i.e H95 and H102, shown as
+    calculation. First, the base residues (i.e.\ H95 and H102, shown as
     red spheres) of the CDR-H3 (shown in red) are identified. Then, a
@@
     \AA\ (depicted as yellow arrow) is used as the `protrusion'
-    feature. }
+    feature.}
   \label{fig:angle}
@@
 Given that abYbank/AbDb is soon to be expanded by an additional
-ca. 2000 structures, classifier performance on models without a known
+$\sim$2000 structures, classifier performance on models without a known
 abYmod-template sequence may be improved by a larger dataset.

### 2022-10-05 paper.tex
Fixed all full-stops commas and dashes

@@
 even compared to other protein loops\cite{Regep2017}. It was found
-that over 75\% of CDR-H3 loops do not have a sub-Angstrom non-antibody
+that over 75\% of CDR-H3 loops do not have a sub-{\AA}ngstr\"{o}m non-antibody
 structural neighbour, as well as that 30\% of CDR-H3 loops have a
@@
 According to the Kabat definition, the CDR-H3 loop is made up of the
-residues 95-105 (Kabat numbering scheme\cite{Kabat1992}) in the heavy
+residues 95--105 (Kabat numbering scheme\cite{Kabat1992}) in the heavy
 chain, with a potential insertion site at position 100. The
@@
     have a unimodal, yet almost normal distribution with a range of
-    ca. 4-28 and 4-38 respectively. The length cut-off for CDR-H3s
+    $\sim$4--28 and 4--38 respectively. The length cut-off for CDR-H3s
     depicted above is 30 amino acids. Bovine antibodies with
@@
 are not as easily predicted due to their great diversity. If the
-canonical conformation of CDR loops 1-5 can be identified, they too
+canonical conformation of CDR loops 1--5 can be identified, they too
 can be modelled rather well, often within 1\AA\ RMSD, for CDR-H3 loops
@@
 RMSD range must be divided into categories. This is done either by
-creating uniform classes i.e.\ 1-2~\AA, 2-3~\AA\ (the optimal size of which
-must be determined), etc. or by creating balanced classes. When
+creating uniform classes i.e.\ 1--2~\AA, 2--3~\AA\ (the optimal size of which
+must be determined), etc.\ or by creating balanced classes. When
 creating balanced classes, the upper and lower thresholds of a
@@
 The classifier predicts whether a model has an RMSD of below 2~\AA,
-between 2-4~\AA, or above 4~\AA. These cut-off values were selected
+between 2--4~\AA, or above 4~\AA. These cutoff values were selected
 based on the observation that abYmod generally produces a model with
@@
 \subsection{Computing}
-All machine learning and, feature selection and hyperparameter
+All machine learning and feature selection and hyperparameter
 optimization algorithms were implemented in Python. The Scikit-learn
@@
 four-dimensional physiochemical feature vector25. The amino acid
-properties used are 1) the total number of side-chain atoms, 2) the
-number of side-chain atoms in the shortest path from \ca\ to the most
+properties used are 1) the total number of sidechain atoms, 2) the
+number of sidechain atoms in the shortest path from \ca\ to the most
 distal atom, 3) the Eisenberg consensus
@@
 be most important for effective learning. A multitude of methods were
-tested. No one-fit-for-all method for the different models could be
+tested. No one fit-for-all method for the different models could be
 found. However, for our top-layer classifier in our final model

### 2022-10-05 paper.tex
Added \url to all URLs

@@
 In this project abYmod is used, which is to be found at
-http://abymod.abysis.org/. The program utilizes extensive canonical
+\url{http://abymod.abysis.org/}. The program utilizes extensive canonical
 class definitions, VH/VL angle prediction and a large database of loop
@@
   \caption {Sequence Logo of the CDR-H3 loop sequence. Data on amino
-    acid occurrence taken from http://abymod.abysis.org/ Visualized
+    acid occurrence taken from \protect\url{http://abymod.abysis.org/} Visualized
     using Seq2Logo.}
@@
 visualization. All code is available at
-https://github.com/LilianDenzler/qualiloop
+\url{https://github.com/LilianDenzler/qualiloop}
 

### 2022-10-05 paper.tex
Centred all figures and full width
Added more macros

@@
 \usepackage{url}
+\usepackage{color}
 \newcommand{\ca}{\mbox{C$\alpha$}}
+\newcommand{\VH}{\mbox{V\kern-.1667em \lower.5ex\hbox{\scriptsize H}}}
+\newcommand{\VL}{\mbox{V\kern-.1667em \lower.5ex\hbox{\scriptsize L}}}
+\newcommand{\VHVL}{\mbox{\VH/\VL}}
+\newcommand{\CH}[1]{\mbox{C\lower.5ex\hbox{\scriptsize H}#1}}
+\newcommand{\CL}{\mbox{C\kern-.0833em \lower.5ex\hbox{\scriptsize L}}}
+\newcommand{\FV}{\mbox{\it Fv}}
+\newcommand{\Fab}{\mbox{\it Fab}}
+
+\newcommand{\e}[1]{\mbox{$\times 10^{#1}$}}
+\newcommand{\etal}{~\emph{et al.}}
+\newcommand{\degree}{\mbox{${}^{\circ}$}}
+\newcommand{\lilian}[1]{{\color{red}\sout{#1}}}
+\newcommand{\andrew}[1]{{\color{green}\uline{#1}}}
 
@@
 \begin{figure}
-  \includegraphics[scale=1]{loopdist.eps}
   \centering
+  \includegraphics[width=\linewidth]{loopdist.eps}
   \caption { Distribution of CDR-H3 loop lengths in mouse (left),
@@
 \url{http://abymod.abysis.org/}. The program utilizes extensive canonical
-class definitions, VH/VL angle prediction and a large database of loop
+class definitions, \VHVL\ angle prediction and a large database of loop
 structures (LoopDB) for CDR-H3 modelling to achieve optimal
@@
 overall-matching template works best and the CDR-specific templates
-are used if there is no canonical match. The VH/VL packing angle is
+are used if there is no canonical match. The \VHVL\ packing angle is
 then determined either using machine learning or the chosen template
@@
   \centering
-  \includegraphics[scale=0.3]{AMA.eps}
+  \includegraphics[width=\linewidth]{AMA.eps}
   \caption {RMSD values of the CDR-H3 loop for structures from the
@@
 \begin{figure}
-  \includegraphics[scale=0.9]{logo.eps}
+  \centering
+  \includegraphics[width=\linewidth]{logo.eps}
   \caption {Sequence Logo of the CDR-H3 loop sequence. Data on amino
@@
   \centering
-  \includegraphics[scale=0.49]{feature_table.eps}
+  \includegraphics[width=\linewidth]{feature_table.eps}
   \caption {A summary of how different feature values were calculated.}
@@
 \begin{figure}
-  \includegraphics[scale=0.6]{angle.eps}
+  \centering
+  \includegraphics[width=\linewidth]{angle.eps}
   \caption {Diagram visualizing the process underlying the protrusion
@@
 \begin{figure}
-  \includegraphics[scale=0.45]{method.eps}
+  \centering
+  \includegraphics[width=\linewidth]{method.eps}
   \caption {Simplified pipeline for creating the final machine

### 2022-10-05 paper.tex
First set of changes and queries

@@
 \newcommand{\degree}{\mbox{${}^{\circ}$}}
-\newcommand{\lilian}[1]{{\color{red}\sout{#1}}}
-\newcommand{\andrew}[1]{{\color{green}\uline{#1}}}
+\newcommand{\lilian}[1]{{\color{red}{\bfseries Lilian:} #1}}
+\newcommand{\andrew}[1]{{\color{green}{\bfseries Andrew:} #1}}
+\newcommand{\rewrite}[1]{{\color{blue}{\bfseries Andrew to rewrite:} #1}}
+\newcommand{\highlight}[1]{{\color{cyan} #1}}
 
@@
   development and have brought new hope for the treatment of numerous
-  diseases. The bioinformatic tools for modelling antibody structures
+  diseases. Bioinformatics tools for modelling antibody structures
   have become invaluable for antibody engineering and the development
@@
   hypervariable loops, also known as the Complementary Determining
-  Regions (CDR), all of which can be modelled with adequate accuracy,
-  except for one. It remains markedly difficult to model the third CDR
-  loop of the antibody heavy chain. The CDR-H3 differs in length, has
-  far greater sequence variability and has such a great structural
-  diversity that modelling it is considerably harder.
+  Regions (CDRs), all of which can be modelled with adequate accuracy,
+  except for one. It remains remarkably difficult to model the third CDR
+  loop of the antibody heavy chain. CDR-H3 has
+  far greater length and sequence variability, with such great structural
+  diversity, that modelling it is considerably harder.
 
-  Many sophisticated approaches for antibody modelling, such as the
+  Many approaches for antibody modelling, such as our
   abYmod software, have been developed. Although such efforts have
-  improved prediction accuracy the results for the CDR-H3 loop are
+  improved prediction accuracy the results for CDR-H3 are
   still inconsistent and require further improvement. Providing a
@@
 mature antibody binds a specific antigen with high affinity, while
-only weakly interacting with other antigens, or not at all. This high
-affinity, high specificity sets it apart from other pharmaceuticals.
+only weakly interacting with other antigens, or not at all. \lilian{Introduce the use as drugs} This high
+affinity and high specificity sets it apart from other pharmaceuticals.
 Furthermore, in contrast with small drug molecules, antibodies can not
-only bind pockets, but also flat, concave or even convex
+only bind pockets, but also flat, concave or convex
 surfaces\cite{Tavers2001}. Their unique characteristics have enabled 
@@
 Their ability to target an immense variety of antigens allows for
-endless possibilities in application. The global market size was
-valued at USD 130.9 billion in 2020, estimated to grow 223.7 billion
-by the end of 2025 at a compound annual growth rate of
-11.31\%\cite{market2020}. Four of the top 10 best-selling drugs in
+endless possibilities in application. 
+Four of the top 10 best-selling drugs in
 2020 were monoclonal antibodies\cite{Urquhart2021}.
 
-In order to rationally design therapeutic antibodies, knowledge of
+In order to design therapeutic antibodies rationally, knowledge of
 their structure is essential. The acquired structural information can
@@
 well as assessing immunogenicity\cite{Abhinandan2007}. As
-experimental structure determination is very costly and time
+experimental structure determination is costly and time
 consuming, computational predictions of an antibody's structure are
@@
 
-Antibodies consist of a heavy and a light chain, which are linked by
-disulphide bonds. The N-terminal domain of each makes up the variable
-fragment (Fv), which contains the complementarity determining regions
-(CDRs). The antigen binding site is composed of six CDRs, also known
-as hypervariable loops. All except one of these loops can be clustered
-into a limited number of canonical structures. Therefore, modelling
+The variable
+fragment (Fv) of an antibody contains the six complementarity determining regions
+(CDRs, also known as hypervariable loops) which form the antigen binding site.
+All except one of these loops can be clustered
+into a limited number of `canonical structures'\cite{XXXX}. Therefore, modelling
 these loops with adequate accuracy is commonly
-achievable\cite{North2011,Weitzner2015}. However, the CDR loop 3 of
-the 
+achievable\cite{North2011,Weitzner2015}. \lilian{Is the second reference relevant here?} However, the CDR loop 3 of the 
 heavy chain (CDR-H3) has a far greater sequence variability due to the
@@
 that over 75\% of CDR-H3 loops do not have a sub-{\AA}ngstr\"{o}m non-antibody
-structural neighbour, as well as that 30\% of CDR-H3 loops have a
-completely unique structure compared with under 3\% for all other
-loops on average\cite{Regep2017}.
+structural neighbour, while 30\% of CDR-H3 loops have a
+completely unique structure compared with under 3\% for all non-antibody
+loops\cite{Regep2017}.
 
@@
 also the most important for antigen binding, being located at the
-center of the binding site and forming the most contacts to the
-antigen\cite{MacCallum1996}. In fact, it was demonstrated that
-differences in this loop alone were sufficient to enable otherwise
+center of the binding site and forming the most contacts with the
+antigen\cite{MacCallum1996}. It was demonstrated that
+differences in this loop alone are sufficient to enable otherwise
 identical antibodies to distinguish between various
@@
 According to the Kabat definition, the CDR-H3 loop is made up of the
-residues 95--105 (Kabat numbering scheme\cite{Kabat1992}) in the heavy
+residues 95--105 (using the Kabat\cite{Kabat1992}, Chothia\cite{XXXX} or Martin\cite{XXXX} numbering schemes) in the heavy
 chain, with a potential insertion site at position 100. The
@@
   \includegraphics[width=\linewidth]{loopdist.eps}
-  \caption { Distribution of CDR-H3 loop lengths in mouse (left),
+  \caption{Distribution of CDR-H3 loop lengths in mouse (left),
     human (centre) and cow (right). Mouse and human antibody CDR-H3s
@@
     reaching a length of 67 amino acids and
-    above\protect\cite{Wong2015}.}  
+    above\protect\cite{Wong2015}. \lilian{Do we need this?}}  
   \label{fig:loopdist}
@@
 RosettaAntibody\cite{Sircar2009,Sivasubramanian2009}, 
-ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017} and abYmod,
-UCL's in-house software developed by Prof.\ Martin. One of the most
+ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017} \lilian{Lyra, AbLooper} and our own abYmod.
+One of the most
 used methods is RosettaAntibody, which implements template selection
-and ab initio CDR-H3 loop modelling using loop fragments and employing
+and \emph{ab initio} CDR-H3 loop modelling using loop fragments and employing
 specific angle restraints which bias the conformational space towards
@@
 (FREAD\cite{Choi2010}) for CDR loop modelling.
-
-In this project abYmod is used, which is to be found at
-\url{http://abymod.abysis.org/}. The program utilizes extensive canonical
+abYmod \url{http://abymod.abysis.org/} utilizes extensive canonical
 class definitions, \VHVL\ angle prediction and a large database of loop
-structures (LoopDB) for CDR-H3 modelling to achieve optimal
-results. Upon inputting an antibody sequence, abYmod assigns the
-canonical class using a set of key residues\cite{Martin1996}and where
-an exact match is not possible, a nearest match is made. Then, the
+structures (LoopDB) for CDR-H3 modelling.
+Upon inputting an antibody sequence, abYmod assigns the
+canonical class using a set of key residues\cite{Martin1996} and where
+an exact match is not possible, a nearest match is made. \rewrite{Then, the
 program identifies the 10 best overall-matching PDB files according to
@@
 overall-matching template works best and the CDR-specific templates
-are used if there is no canonical match. The \VHVL\ packing angle is
-then determined either using machine learning or the chosen template
+are used if there is no canonical match.}
+
+The \VHVL\ packing angle is
+then determined either using machine learning \lilian{not yet!} or the chosen template
 structure for one of the chains. CDR specific templates, if selected,
 are grafted onto the framework. If there is no template of the correct
-length for CDR-H3, the loop is built using the LoopDB database,
+length for CDR-H3, the loop is built using LoopDB,
 containing CDR-H3-like loops from all proteins. Finally, Gromacs energy
@@
 Using these mentioned modelling methods, framework regions can
-generally be predicted with great accuracy (with better than 1\AA\
+generally be predicted with great accuracy (with better than 1~\AA\
 RMSD\cite{Almagro2014}), as one can often find a very similar
@@
 are not as easily predicted due to their great diversity. If the
-canonical conformation of CDR loops 1--5 can be identified, they too
-can be modelled rather well, often within 1\AA\ RMSD, for CDR-H3 loops
-the average is usually above 3\AA\cite{Almagro2011}.
+canonical conformation of CDR loops CDR-L1--L3 and CDR-H1--H2 can be identified, they too
+can be modelled rather well, often within 1~\AA\ RMSD, for CDR-H3 loops
+the \lilian{not sure what average and usually mean} average is usually above 3~\AA\cite{Almagro2011}.
 
@@
 
-Modelling the CDR-H3 loop is a hurdle for in silico development of
+Modelling the CDR-H3 loop is a hurdle for \emph{in silico} development of
 therapeutic antibodies. Currently, there is no definite, reliable way
 to determine how accurate a generated structural model is within the
-H3 region. Therefore, the aim of this project will be to produce a
+H3 region. Therefore, we have produced a
 user-friendly predictor of CDR-H3 model quality. The predictor will give
 the user an RMSD-range in {\AA}ngstr\"{o}ms, in which the generated model lies
-with a high probability. Making such a confidence score available via
-the web interface of the in-house modelling software abYmod is a
-future goal. Such a score is not provided by most modelling programs
-and would thus be a novel addition.  This information can guide the
+with a high probability.
+This information can guide the
 user in the antibody engineering process. The user has the choice to
-determine whether the model is to be used in the intended way, or
+determine whether the model is to be used as is, or
 whether the model should be re-worked.
@@
 \section{Results}
-To asses the predictive power regarding the CDR-H3 loop, the software
+The software
 was tested on a test-set of antibody structures used in the 2014 and
@@
 \cite{Almagro2011,Almagro2014}. As the results depicted in
-Figure~\ref{fig:AMA} show, abYmod achieves results similar to, or better than
+Figure~\ref{fig:AMA} show, abYmod achieves results similar to, or better than,
 other modelling programs. However, the outliers with very high RMSD
@@
 The predictive power of any machine learning model is largely
-dependent on the quality and size of the dataset it was trained on. As
+dependent on the quality and size of the dataset on which it was trained. As
 this is a non-linear, complex, multi-class classification problem, a
@@
 dataset of antibody structures called abYbank/AbDb\cite{XXXX},
-established by Prof.\ Andrew Martin, was utilised (1924 non-redundant
-structures). The root-mean-square deviation (RMSD) value, a measure of
-distance between backbone \ca\ atoms of superimposed crystal structures
-and modelled structures, is calculated (see methods). This metric for
-model quality was used to classify models.
+was utilised (1924 non-redundant
+structures). The \ca\ root-mean-square deviation (RMSD) value
+between the crystal structures
+and modelled structures was calculated (see Methods) and
+was used to classify models.
 
@@
     outperforms other modelling software in some instances, but also
-    has much lower accuracy in few outlier cases. (left: an abYmod
+    has much lower accuracy in few outlier cases. Left: an abYmod
     structure for C705 could be generated, yet the RMSD calculation
-    failed. Right: Ab01 is the rabbit antibody PDB:4MA3, which was
+    failed \lilian{Why? I'm sure we can resolve this!}.
+    Right: Ab01 is the rabbit antibody PDB:4MA3, which was
     excluded in the CDR-H3 modelling stage in AMAII due to
@@
     shown for the methods, where generated models were adequate for
-    RMSD calculation.)}
+    RMSD calculation. \lilian{This needs better explanation}}
   \label{fig:AMA}
@@
 
-The full pipeline for creating the final machine learning model that
-will predict model quality by giving its RMSD range starts with a
+The full pipeline for creating the final machine learning model
+starts with 
 feature-set calculation using the antibody sequence. The feature set
-includes many different attributes linked to sequence, physical
-characteristics, interactions, etc., within as well as outside of the
-loop. There is a plethora of information to train our classifier on,
-including packing quality, protrusion, hydrophobicity, pseudo-energy
-(see protrusion, hydrophobicity, pseudo-energy (see methods for
-details). The sequence logo (Figure~\ref{fig:logo}) visualizes amino acid
+includes attributes linked to sequence, structure, physical
+characteristics, interactions, etc., within, as well as outside, the
+loop. 
+The sequence logo (Figure~\ref{fig:logo}) visualizes amino acid
 occurrence within the loop sequence, elements of which can be
@@
     acid occurrence taken from \protect\url{http://abymod.abysis.org/} Visualized
-    using Seq2Logo.}
+    using Seq2Logo. \lilian{What's the X-axis numbering? IMGT? Can you highlight the CDR residues (95--122) What range of lengths is included?}}
   \label{fig:logo}
@@
 scaling, encoding, see methods for details). Structures with a
-resolution below 4\AA\ were removed given their low quality. Identical
-whole antibody structures were removed from the dataset, while
+resolution worse than 4~\AA\ were removed.
+\lilian{You already said it was a non-redundant set?} \highlight{Identical
+whole antibody structures were removed from the dataset}, \lilian{I don't understand this bit!} \highlight{while
 instances of different antibodies that matched in loop sequence were
-not removed. Models of some of these structures with the same loop
+not removed}. Models of some of these structures with the same loop
 sequence differ significantly. The few large RMSD ranges may stem from
-low resolution, e.g.\ the highest datapoint contains a structure with a
-resolution of 3.00~\AA.  Residue differences near the loop may also
-explain the conformational difference. Some of these structures are
+low resolution. For example, the \highlight{highest} \lilian{What does `highest' mean?} datapoint contains a structure with a
+resolution of 3.00~\AA.  \lilian{Explain} \highlight{Residue differences near the loop may also
+explain the conformational difference}. Some of these structures are
 complexed while others are not, which may also affect the loop
-structure.
+structure (manuscript in preparation).
 
-The dataset was also screened for any models which abYmod created
-using a template sequence from LoopDB, a database of CDR-H3 like loops
-from all proteins. This was not the case for any of our structures.
-
-The target data (i.e.\ RMSD values) are then transformed from numerical
+The target data (i.e.\ RMSD values) are transformed from numerical
 values to nominal values so that they can be used for
@@
 RMSD range must be divided into categories. This is done either by
-creating uniform classes i.e.\ 1--2~\AA, 2--3~\AA\ (the optimal size of which
-must be determined), etc.\ or by creating balanced classes. When
+creating uniform classes i.e.\ 1--2~\AA, 2--3~\AA, etc., (the optimal size of which
+must be determined), or by creating balanced classes. When
 creating balanced classes, the upper and lower thresholds of a
 category are chosen in such a way that each class contains an equal
-number of instances. This approach is chosen to counteract the
+number of instances. This approach was chosen to counteract the
 skewness of the RMSD distribution. However, this was found to
-negatively affect the final model's predictive power. Therefore,
+affect the final model's predictive power negatively. Therefore,
 uniform classes were used.
 
-They are also transformed into a set of binary values according to a
+They are also transformed \lilian{explain?} into a set of binary values according to a
 list of RMSD thresholds. This is done so that binary models can be
@@
 is above 2~\AA, 2.2~\AA, 2.4~\AA, and so on. The number of binary
-classifiers incorporated into the first layer have a great effect on
+classifiers incorporated into the first layer has a great effect on
 the final model, the general trend being that the more binary
-classifiers are used, the better the nominal prediction.
+classifiers are used, the better the nominal prediction. \lilian{Data?}
 
@@
 
-As some features are in the form of amino acid codes, these must be
+As some features are in the form of amino acid names, these must be
 encoded before they can be passed to a machine learning model. The
@@
 An MCC value of 0.99 was achieved for a classifier predicting whether
-an input-model has an RMSD value below 2\AA, 2\AA--4\AA\ or above
-4\AA.
+an input-model has an RMSD value below 2~\AA, 2~\AA--4~\AA\ or above
+4~\AA.
 

### 2022-10-06 paper.tex
My main set of changes all done

@@
 \newcommand{\degree}{\mbox{${}^{\circ}$}}
-\newcommand{\lilian}[1]{{\color{red}{\bfseries Lilian:} #1}}
-\newcommand{\andrew}[1]{{\color{green}{\bfseries Andrew:} #1}}
+\newcommand{\lilian}[1]{ {\color{red}{\bfseries Lilian:} #1}}
+\newcommand{\andrew}[1]{ {\color{green}{\bfseries Andrew:} #1}}
 \newcommand{\rewrite}[1]{{\color{blue}{\bfseries Andrew to rewrite:} #1}}
-\newcommand{\highlight}[1]{{\color{cyan} #1}}
+
+\usepackage{soul}
+\newcommand{\highlight}[1]{\hl{#1}}
+% \newcommand{\highlight}[1]{{\color{cyan} #1}} % Use this if soul package not available!
+
+\let\shortcite\cite
+\emergencystretch 1in
 
@@
   structures, giving the abYmod user a clearer understanding of the
-  generated model reliability.
+  generated 3D-model reliability.
 
-  We present a model quality predictor, combining domain knowledge
+  We present a 3D-model quality predictor, combining domain knowledge
   with machine learning techniques to predict the accuracy of CDR-H3
-  models generated by antibody modelling software such as abYmod. The
+  3D-models generated by antibody modelling software such as abYmod. The
   newly developed predictor scored a Mathews Correlation Coefficient
@@
 only bind pockets, but also flat, concave or convex
-surfaces\cite{Tavers2001}. Their unique characteristics have enabled 
+surfaces\cite{Tavers2001}\lilian{Surely you can find a better reference! e.g. our one!}. Their unique characteristics have enabled 
 researchers to develop efficient antibody drugs for treating cancers,
@@
 Assessments (AMA), two blind contests that required researchers to
-build structural models from antibody sequences. The CDR-H3 loop
+build three-dimensional structural models (3D-models) from antibody sequences. The CDR-H3 loop
 modelling quality achieved at the contests was on average much lower
@@
 
-Several different approaches for generating three-dimensional
-structure models from antibody sequences exist such as
+Several different approaches for generating 
+3D-models from antibody sequences exist such as
 RosettaAntibody\cite{Sircar2009,Sivasubramanian2009}, 
@@
 canonical class using a set of key residues\cite{Martin1996} and where
-an exact match is not possible, a nearest match is made. \rewrite{Then, the
-program identifies the 10 best overall-matching PDB files according to
-sequence identity for the light and heavy chain. Of these, the best
-template is then identified for each CDR using sequence similarity and
-identity. In general, modelling the antibody using the single best
-overall-matching template works best and the CDR-specific templates
-are used if there is no canonical match.}
+an exact match is not possible, a nearest class is identified.
 
-The \VHVL\ packing angle is
-then determined either using machine learning \lilian{not yet!} or the chosen template
-structure for one of the chains. CDR specific templates, if selected,
+abYmod selects light and heavy chains separately from PDB templates.
+First these are selected on the basis of the number of matched
+canonical classes and then on the basis of sequence identity.  The
+\VHVL\ packing angle is currently selected from the parent that has
+the best sequence identity over both chains, but an improved method is
+currently in development. Any CDRs where there was no canonical match are then
 are grafted onto the framework. If there is no template of the correct
-length for CDR-H3, the loop is built using LoopDB,
-containing CDR-H3-like loops from all proteins. Finally, Gromacs energy
-minimization software is used to optimize the model. This method has
+length for CDR-H3, the loop is built using LoopDB, a database of
+CDR-H3-like loops from all proteins. Finally, Gromacs energy
+minimization software is used to optimize the 3D-model. This method has
 proven very effective and preliminary analysis suggests the method
-achieves comparable results or outperforms other modelling software
-(see results section).
+achieves comparable results, or outperforms, other modelling software
+(see Results).
 
 Using these mentioned modelling methods, framework regions can
-generally be predicted with great accuracy (with better than 1~\AA\
+generally be predicted with great accuracy (with better than 1\AA\
 RMSD\cite{Almagro2014}), as one can often find a very similar
@@
 are not as easily predicted due to their great diversity. If the
-canonical conformation of CDR loops CDR-L1--L3 and CDR-H1--H2 can be identified, they too
-can be modelled rather well, often within 1~\AA\ RMSD, for CDR-H3 loops
-the \lilian{not sure what average and usually mean} average is usually above 3~\AA\cite{Almagro2011}.
+canonical conformation of CDR loops CDR-L1,L2,L3,H1,H2 can be identified, they too
+can be modelled rather well, often within 1\AA\ \ca~RMSD, for CDR-H3 loops
+the \lilian{not sure what `average' and `usually' mean here:} average is usually above 3\AA\cite{Almagro2011}.
 
@@
 confidence score for each region (e.g.\ CDR-H2) of the antibody
-model. The given score is the probability that a specific region
-(e.g.\ CDR-H2) will be will be modeled within a specific RMSD
+3D-model. The given score is the probability that a specific region
+(e.g.\ CDR-H2) will be will be modelled within a specific RMSD
 threshold\cite{Leem2016}. Thus, it can be used to obtain an expected
@@
 loops due to the lack of data\cite{Leem2016}. ABLooper also provides a
-confidence metric for the CDR-H3 loop model, which is estimated by the
+confidence metric for the CDR-H3 loop 3D-model, which is estimated by the
 diversity of a set of predicted conformations for the same
@@
 prediction diversity score points towards loops with multiple
-conformations or a low quality model. Furthermore, it remains unclear
-how well the generated diversity score reflects model
+conformations or a low quality 3D-model. Furthermore, it remains unclear
+how well the generated diversity score reflects 3D-model
 quality\cite{Abanades2022}.
@@
 therapeutic antibodies. Currently, there is no definite, reliable way
-to determine how accurate a generated structural model is within the
+to determine how accurate a generated structural 3D-model is within the
 H3 region. Therefore, we have produced a
-user-friendly predictor of CDR-H3 model quality. The predictor will give
-the user an RMSD-range in {\AA}ngstr\"{o}ms, in which the generated model lies
+user-friendly predictor of CDR-H3 3D-model quality. The predictor will give
+the user an RMSD-range in {\AA}ngstr\"{o}ms, in which the generated 3D-model lies
 with a high probability.
@@
 user in the antibody engineering process. The user has the choice to
-determine whether the model is to be used as is, or
-whether the model should be re-worked.
+determine whether the 3D-model is to be used as is, or
+whether the 3D-model should be re-worked.
 
@@
 values increase abYmod's RMSD average. The predictor in this work
-would aim to identify such outlier models.
+would aim to identify such outlier 3D-models.
 
-The predictive power of any machine learning model is largely
+The predictive power of any machine learning model (ML-model) is largely
 dependent on the quality and size of the dataset on which it was trained. As
@@
 substantial amount of data was required. Thus, an extensive, verified
-dataset of antibody structures called abYbank/AbDb\cite{XXXX},
+dataset of antibody structures called abYbank/AbDb\cite{Ferdous2018},
 was utilised (1924 non-redundant
@@
 and modelled structures was calculated (see Methods) and
-was used to classify models.
+was used to classify 3D-models.
 
@@
     difficulties modelling the overall structure previously. Ab01 is
-    shown for the methods, where generated models were adequate for
+    shown for the methods, where generated 3D-models were adequate for
     RMSD calculation. \lilian{This needs better explanation}}
@@
 
-The full pipeline for creating the final machine learning model
+The full pipeline for creating the final ML-model
 starts with 
@@
 scaling, encoding, see methods for details). Structures with a
-resolution worse than 4~\AA\ were removed.
+resolution worse than 4\AA\ were removed.
 \lilian{You already said it was a non-redundant set?} \highlight{Identical
@@
 instances of different antibodies that matched in loop sequence were
-not removed}. Models of some of these structures with the same loop
+not removed}. 3D-Models of some of these structures with the same loop
 sequence differ significantly. The few large RMSD ranges may stem from
 low resolution. For example, the \highlight{highest} \lilian{What does `highest' mean?} datapoint contains a structure with a
-resolution of 3.00~\AA.  \lilian{Explain} \highlight{Residue differences near the loop may also
+resolution of 3.00\AA.  \lilian{Explain} \highlight{Residue differences near the loop may also
 explain the conformational difference}. Some of these structures are
@@
 RMSD range must be divided into categories. This is done either by
-creating uniform classes i.e.\ 1--2~\AA, 2--3~\AA, etc., (the optimal size of which
+creating uniform classes i.e.\ 1--2\AA, 2--3\AA, etc., (the optimal size of which
 must be determined), or by creating balanced classes. When
@@
 skewness of the RMSD distribution. However, this was found to
-affect the final model's predictive power negatively. Therefore,
+affect the final ML-model's predictive power negatively. Therefore,
 uniform classes were used.
@@
 They are also transformed \lilian{explain?} into a set of binary values according to a
-list of RMSD thresholds. This is done so that binary models can be
-trained, which will predict the probability e.g.\ that the model's RMSD
-is above 2~\AA, 2.2~\AA, 2.4~\AA, and so on. The number of binary
+list of RMSD thresholds. This is done so that binary ML-models can be
+trained, which will predict the probability e.g.\ that the 3D-model's RMSD
+is above 2\AA, 2.2\AA, 2.4\AA, and so on. The number of binary
 classifiers incorporated into the first layer has a great effect on
-the final model, the general trend being that the more binary
+the final ML-model, the general trend being that the more binary
 classifiers are used, the better the nominal prediction. \lilian{Data?}
@@
 As some features are in the form of amino acid names, these must be
-encoded before they can be passed to a machine learning model. The
-encoding strategy often determines how efficiently the model learns
+encoded before they can be passed to a ML-model. The
+encoding strategy often determines how efficiently the ML-model learns
 and how much information can be extracted. Different strategies were
-employed to represent followed by BLOSUM62 and NLF encoding. The
-physiochemical encoding strategy was implemented for all models, being
-the most effective. However, PCA-3 BLOSUM62, a dimensionality-reduced
+employed to represent \highlight{followed by}\lilian{???} BLOSUM62\cite{XXXX} and \highlight{NLF}\lilian{???}\cite{XXXX} encoding. The
+\highlight{physiochemical encoding}\lilian{explain} strategy was implemented for all ML-models, being
+the most effective. However, PCA-3 BLOSUM62\cite{XXXX}, a dimensionality-reduced
 BLOSUM62 encoding method achieved comparable results.
+Feature selection was conducted to improve the ML-model's learning
+capacity. A high-dimensional feature dataset bears the risk of
+introducing excessive noise, facilitating ML-model overfitting and can be
+responsible for an overall decrease in ML-model performance and
+stability. Each additional input feature forces the ML-model to
+handle a more complex task, which consumes excess computational power
+and time and provides more variables leading to overfitting of the ML-model.
 
-Feature selection was conducted to improve the ML model's learning
-capacity. A high-dimensional feature dataset bears the risk of
-introducing excessive noise, facilitating model overfitting and can be
-responsible for an overall decrease in model performance and
-stability. Each additionally inputted feature forces the model to
-handle a more complex task, which consumes excess computational power
-and time and leads to overfitting of the model.
+Our ML-model was trained on different feature sets selected using manual
+selection as well as \highlight{algorithmic selection strategies}\lilian{Which are?}, in order to
+determine the most effective feature selection method. None of the
+feature selection methods was a best fit for all ML-models.\lilian{Explain}
 
-Our model is trained on different feature sets selected using manual
-selection as well as algorithmic selection strategies, in order to
-determine the most effective feature selection method. None of the
-feature selection methods was a best fit for all models.
+\lilian{So, having read this, I have no idea what feature encoding you
+  actually used, or where to find that information. What worked and
+  what didn't? Where can I find a comparison of the performance?}
 
-After the data is processed, it can be fed into different machine
-learning models. Different model types are investigated, as the most
-suited model-type has to be heuristically determined. We decided on
-the following list, which includes some of the most commonly used
-algorithms: logistic regression, linear discriminant analysis,
+After the data were processed, they were used to train different
+ML-models. Different types of ML-model were investigated, as the most
+suited ML-model type has to be determined heuristically. 
+The following list, which includes some of the most commonly used
+algorithms, was used: logistic regression, linear discriminant analysis,
 K-nearest neighbours classifier, decision tree classifier, Gaussian
@@
 gradient boosting (XGBoost)\cite{Chen2016}.
+\lilian{OK, but this is the Results section, so where are the results
+  of using the different methods?}
 
-The best model, and its best hyperparameters, are then determined for
-each binary RMSD target. The set of binary models outputs a number of
-predictions that give the likelihood of the model having an RMSD above
-the threshold value of the respective model. These predictions are
-then added to the feature set, which a top-layer classifier is then
-trained on. Thus, a quasi-voting-system is incorporated into the final
-classifier, in which a set of weaker classifiers vote on the model
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{method.eps}
+  \caption {Simplified pipeline for creating the final machine
+    learning model (ML-model) that will predict 3D-model quality by giving its RMSD
+    range.}
+  \label{fig:method}
+\end{figure}
+
+The best ML-model, and its best hyperparameters, are then determined for
+each binary RMSD target. The set of binary ML-models outputs a number of
+predictions that give the likelihood\lilian{is it always a likelihood, or a confidence? Or is that the same thing?} of the 3D-model having an RMSD above
+the threshold value of the respective ML-model. These predictions are
+then added to the feature set, on which a top-layer classifier is then
+trained (Figure~\ref{fig:method}). Thus, a quasi-voting-system is incorporated into the final
+classifier, in which a set of weaker classifiers vote on the ML-model
 quality.
@@
 In the process of hyperparameter optimization, the configuration of
-model parameters which results in best performance is selected. This
+ML-model parameters which results in best performance is selected. This
 is usually a computationally expensive and manual procedure.
+In an effort to automate this process, a population was defined for
+each ML-model type, so hyperparameter optimization could be conducted
+automatically for each ML-model and seamlessly integrated into the full
+ML-model creation process. Two different methods for hyperparameter
+optimization were tested. The first was a hybrid approach of randomized
+search and grid search; the second used a genetic algorithm for
+optimization. The genetic algorithm was found to achieve slightly
+better results and was employeded for optimizing all ML-models.
 
-In an effort to automate this process, a population is defined for
-each model type, so hyperparameter optimization can be conducted
-automatically for each model and seamlessly integrated into the full
-model creation process. Two different methods for hyperparameter
-optimization were tested. The first is a hybrid approach of randomized
-search and grid search, the second uses a genetic algorithm for
-optimization. The genetic algorithm was found to achieve slightly
-better results and was selected for all models.
+\subsection{Machine Learning Model Performance}
+The overall best final ML-model was composed of several different binary
+classifiers,\lilian{More detail!} with an extreme gradient boosting (XGBoost) top-layer
+nominal classifier. Features were selected using random forest feature
+selection.
+\lilian{Explain how this works and which features were selected --- and how many?}
+A final MCC\lilian{Explain how MCC is calculated over 3 classes} value of 0.99 could be achieved for an ML-model
+using the abYmod log file \lilian{What parameters are actually used?} as input as well as the loop 3D-model file
+itself. This value slightly dropped to 0.92 if no such log file was
+given. This is mainly\lilian{is there anything else?} due to the fact that the template sequence
+abYmod used to generate the 3D-model is unknown in the latter case.
 
-\subsection{Model Performance}
-The overall best final model is composed of several different binary
-classifiers, with an extreme gradient boosting (XGBoost) top-layer
-nominal classifier. Features were selected using random forest feature
-selection. A final MCC value of 0.99 could be achieved for a model
-using the abYmod log file as input as well as the loop model file
-itself. This value slightly dropped to 0.92 if no such log file was
-given. This is mainly due to the fact that the template sequence
-abYmod used to generate the model is unknown in the latter case.
-
-The classifier predicts whether a model has an RMSD of below 2~\AA,
-between 2--4~\AA, or above 4~\AA. These cutoff values were selected
-based on the observation that abYmod generally produces a model with
-RMSD below 4~\AA. Incorrectly modelled structures (Figure~\ref{fig:AMA}) may
+\lilian{I'm not sure this is in the most logical place --- isn't this
+  something that was chosen at the start? (At least in terms of
+  telling the story}
+The classifier predicts whether a 3D-model has an RMSD of below 2\AA,
+between 2--4\AA, or above 4\AA. These cutoff values were selected
+based on the observation that abYmod generally produces a 3D-model with
+RMSD below 4\AA. Incorrectly modelled structures (Figure~\ref{fig:AMA}) may
 be identified by screening for structures estimated to have an RMSD
-above 4~\AA. If a very high-quality model is needed one should also
-exclude models above 2~\AA.
+above 4\AA. If a very high-quality 3D-model is needed one should also
+exclude 3D-models with RMSD above 2\AA.
 
@@
 \subsection{Computing}
-All machine learning and feature selection and hyperparameter
+All machine learning, feature selection and hyperparameter
 optimization algorithms were implemented in Python. The Scikit-learn
-library was used for training models, the
+library was used for training ML-models, the
 Yellowbrick\cite{Bengfort2021} library was utilized for
@@
 RMSD values, and the calculated features was screened for null
-values. If a feature column contained more than 5\% null values, it
-was dropped (none removed). Rows that contained any null values were
+values.
+Rows that contained any null values were
 removed from the dataset (11 rows in total).
@@
 Using AbDb's redundancy information it was ensured that no antibodies
-were present in the dataset more than once. The dataset is
-additionally screened for duplicate instances.
+were present in the dataset more than once. \highlight{The dataset was
+  additionally screened for duplicate instances.}
+\lilian{Did you find any? How was this screening done? It's far from trivial}
 
 \subsubsection{Scaling}
-Normalization and Standardization are tested as scaling methods. Both
+Normalization and Standardization\lilian{What's the difference? Explain what they are.} were tested as scaling methods. Both
 approaches are greatly influenced by outliers, and such datapoints are
@@
 values and removing such a large number of datapoints is not a viable
-option. A robust scaler was also used, which uses statistics that are
+option. A robust scaler\cite{XXXX} was also used, which uses statistics that are
 robust to outliers. The median is set to zero and numerical features
@@
 (or column) of the BLOSUM62 matrix. Dimensionality reduction
-techniques are employed: Principal Component Analysis (PCA),
+techniques were employed: Principal Component Analysis (PCA),
 Independent Component Analysis (ICA), projection-based methods (t-SNE,
-Isomap). Three components were used as features.
+Isomap). Three components were used as features.\lilian{All three at once?
+  If not then what did you use in the final models?}
 
 \subsubsection{Physiochemical Feature Encoding}
-In a paper by L.~Nanni and A.~Lumini a new encoding technique is
-presented which was developed for machine learning classifiers. Many
+Nanni and Lumini\shortcite{XXXX} described a new encoding technique
+for machine learning classifiers. Many\lilian{How many?}
 physiochemical properties are calculated and transformed using a
 non-linear Fisher transform for dimensionality reduction.  A vector of
-length 19 is produced for each amino acid34.  In a paper on designing
-a neural network for predicting the packing angle of the light and
-heavy variable chain of an antibodies, A.C.R.~Martin and
-K.R.~Abhinandan introduce an encoding method that produces a
-four-dimensional physiochemical feature vector25. The amino acid
-properties used are 1) the total number of sidechain atoms, 2) the
-number of sidechain atoms in the shortest path from \ca\ to the most
-distal atom, 3) the Eisenberg consensus
-hydrophobicity\cite{Eisenberg1982}, 4) the charge.
+length 19 is produced for each amino acid\highlight{34}\lilian{What is this?}. 
+Martin and Abhinandan\shortcite{XXXX} introduced an encoding using
+four physiochemical features \highlight{25}\lilian{What is this?}:
+the total number of sidechain atoms; the
+number of sidechain atoms in the shortest path from the \ca\ to the most
+distal atom; the Eisenberg consensus
+hydrophobicity\cite{Eisenberg1982}; the charge (using +0.5 for histidine).
 
 \subsection{Dataset-splitting}
-The final model was evaluated using a test set, separated from the
+The final ML-model was evaluated using a test set, separated from the
 training set at the start in a 30/70 split (lock-box principle)
-35. The performance of all individual sub-models of the first layer
-are determined using stratified K-folds cross-validation (k=10) as the
+\highlight{35}\lilian{What is this?}. The performance of all individual sub-ML-models of the first layer
+was determined using stratified K-folds cross-validation (K=10) as the
 dataset is imbalanced, being skewed towards lower RMSD values. The
-method is differentiable from K-folds cross validation as it uses
-stratified sampling instead of random sampling. This ensures each
-class is represented, as the percentage of samples for each class are
+method is different from normal K-folds cross validation as it uses
+stratified sampling instead of random sampling.
+\lilian{I think it is still random, it's just that it is selected to represent the imbalance properly}
+This ensures each
+class is represented, as the percentage of samples for each class is
 preserved.
+A validation set, usually used for testing during the optimization
+stage was omitted in favour of stratified K-folds cross-validation
+(k=10)\cite{Krstajic2014,Kohavi1995}.
+\lilian{I don't really understand what you mean here. The stratified
+  cross-validation is going to use a test set in each fold --- it's
+  just that this is selected to fairly represent the inbalance in the
+  training data. Normally the validation set is the set that is held
+  back for final testing --- which you say you did.}
 
-A validation set, usually used for testing during the optimization
-stage will be omitted in favour of stratified K-folds cross-validation
-(k=10)\cite{Krstajic2014,Kohavi1995}.
-
-\subsection{Model Assessment} 
-Model assessment must be considered at two levels as performance
+\subsection{Machine Learning Model Assessment} 
+ML-Model assessment must be considered at two levels as performance
 metrics of binary and multi-class classifiers are calculated
-differently and must thus be considered separately. The Mathews
-Correlation Coefficient (MCC)\cite{Matthews1975} is deemed the most
+differently and must thus be considered separately. The Matthews
+Correlation Coefficient (MCC)\cite{Matthews1975}\lilian{That's the wrong Matthews!!!} is deemed the most
 informative, taking the ratios of the four confusion matrix categories
-into account 39and is thus more reliable than the F1 score and
-accuracy. It is also consistent for both binary and multi-class
-problems and therefore well suited for our purpose.
+into account \highlight{39}\lilian{What is this? There are two papers on MCC being the best.} and is thus more reliable than the F1 score and
+accuracy. It is also \highlight{consistent}\lilian{is that the correct word?!} for both binary and multi-class
+problems and therefore well suited for our purpose.\lilian{How is MCC calculated for multi-class prediction?}
 
@@
   \includegraphics[width=\linewidth]{feature_table.eps}
-  \caption {A summary of how different feature values were calculated.}
+  \caption {A summary of how different feature values were calculated. \lilian{It's a table! Why import it?}}
   \label{fig:feature_table}
@@
   \includegraphics[width=\linewidth]{angle.eps}
-  \caption {Diagram visualizing the process underlying the protrusion
+  \caption {Diagram \lilian{Needs a much simpler cartoon diagram --- it's difficult to see anything from this!}
+    visualizing the process underlying the protrusion
     calculation. First, the base residues (i.e.\ H95 and H102, shown as
@@
     CDR-H3 loop to this line is calculated. The residue which has the
-    greatest distance to the line (shown as green sphere) is outputted
+    greatest distance to the line (shown as green sphere) is output
     as one-letter amino acid code and used as feature. The distance in
     \AA\ (depicted as yellow arrow) is used as the `protrusion'
-    feature.}
+    feature. \lilian{It's unclear whether you use both distance and amino acid, or just one of these.}}
   \label{fig:angle}
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{method.eps}
-  \caption {Simplified pipeline for creating the final machine
-    learning model that will predict model quality by giving its RMSD
-    range.}
-  \label{fig:method}
-\end{figure}
-
 \section{Discussion}
-The results suggest that our presented classifier can differentiate
+The results suggest that our classifier can differentiate
 between well-modelled and less well-modelled CDR-H3 loop
@@
 optimization were tested.
-
 Feature encoding methods that were very high-dimensional
@@
 methods e.g.\ t-SNE) were used on BLOSUM62 encoded matrices, which lead
-to significant improvement. However, a physiochemical encoding
+to significant improvement. However, a physicochemical encoding
 strategy was most effective.
-
 The selection of features incorporated in the training set seemed to
 be most important for effective learning. A multitude of methods were
-tested. No one fit-for-all method for the different models could be
-found. However, for our top-layer classifier in our final model
+tested. No one fit-for-all method for the different ML-models could be
+found.\lilian{I'm not sure what this means.} However, for our top-layer classifier in our final ML-model
 recursive feature elimination worked best.
+A set of commonly used machine learning algorithms were tested, and
+the best ML-models were incorporated into the final ensemble ML-model. A
+stacked ML-model approach (consisting of 23 binary classifiers and a
+single top-layer nominal classifier) was shown to outperform single
+ML-models.
+An MCC value of 0.99 was achieved for a classifier predicting whether
+an input 3D-model has an RMSD value below 2\AA, 2\AA--4\AA\ or above
+4\AA.
 
-A set of commonly used machine learning algorithms were tested, and
-the best ML models were incorporated into the final ensemble model. A
-stacked model approach (consisting of 23 binary classifiers and a
-single top-layer nominal classifier) was shown to outperform single ML
-models.
+We are now looking at incorporating the predictor into the antibody
+modelling process in the selection of high quality CDR-H3 models given
+a set of potential decoys.
 
-An MCC value of 0.99 was achieved for a classifier predicting whether
-an input-model has an RMSD value below 2~\AA, 2~\AA--4~\AA\ or above
-4~\AA.
-
-Given that abYbank/AbDb is soon to be expanded by an additional
-$\sim$2000 structures, classifier performance on models without a known
-abYmod-template sequence may be improved by a larger dataset.
-
-It is conceivable that the described predictor may also be
-incorporated in the antibody modelling process as a low-quality filter
-in the future, flagging certain structures for re-modelling.
-
-In a future research project residue patterns in correlation with RMSD
+\highlight{In a future research project residue patterns in correlation with RMSD
 may be analyzed. Possibly, one might identify certain sequence
@@
 can be built. Given that loop length is the most important determinant
-of model quality, this approach may yield some insight into the
-challenges of modelling shorter vs longer loops.
-
+of 3D-model quality, this approach may yield some insight into the
+challenges of modelling shorter \emph{vs.} longer loops.
 One could also conduct an analysis of the predictor's behaviour when
 abYmod is forced to use LoopDB-based modelling. This might shed light
-on whether the ML model presented in this paper is biased towards
+on whether the ML-model presented in this paper is biased towards
 abYmod's used source of template structures. It would also give an
 indication of how well the predictor would work in combination with
-other modelling software.
+other modelling software.}\lilian{We don't really need this, but can we see any trends from the feature selection?}
+
+\lilian{We need a concluding paragraph relating back to the
+  introduction and what this contributes to improvements in using
+  antibody models.}
 

### 2022-10-06 paper.tex
Spell-checked

@@
 also the most important for antigen binding, being located at the
-center of the binding site and forming the most contacts with the
+centre of the binding site and forming the most contacts with the
 antigen\cite{MacCallum1996}. It was demonstrated that
@@
 capacity. A high-dimensional feature dataset bears the risk of
-introducing excessive noise, facilitating ML-model overfitting and can be
+introducing excessive noise, facilitating ML-model over-fitting and can be
 responsible for an overall decrease in ML-model performance and
@@
 handle a more complex task, which consumes excess computational power
-and time and provides more variables leading to overfitting of the ML-model.
+and time and provides more variables leading to over-fitting of the ML-model.
 
@@
 optimization. The genetic algorithm was found to achieve slightly
-better results and was employeded for optimizing all ML-models.
+better results and was employed for optimizing all ML-models.
 
@@
   cross-validation is going to use a test set in each fold --- it's
-  just that this is selected to fairly represent the inbalance in the
+  just that this is selected to fairly represent the imbalance in the
   training data. Normally the validation set is the set that is held
@@
 (one-hot-encoding, BLOSUM62, NLF) were found to be
-unfavorable. Dimensionality reduction methods (Principal Component
+unfavourable. Dimensionality reduction methods (Principal Component
 Analysis (PCA), Independent Component Analysis (ICA), projection-based

### 2022-10-06 paper.tex
started working through comments

@@
 mature antibody binds a specific antigen with high affinity, while
-only weakly interacting with other antigens, or not at all. \lilian{Introduce the use as drugs} This high
-affinity and high specificity sets it apart from other pharmaceuticals.
+only weakly interacting with other antigens, or not at all.
+\colorbox{green}{This high affinity and high specificity sets them apart from other pharmaceuticals and makes them effective drugs with endless possibilities in application given their ability to target an immense variety of antigens.}
 Furthermore, in contrast with small drug molecules, antibodies can not
 only bind pockets, but also flat, concave or convex
-surfaces\cite{Tavers2001}\lilian{Surely you can find a better reference! e.g. our one!}. Their unique characteristics have enabled 
+surfaces\colorbox{green}{\cite{MacCallum1996}}. Their unique characteristics have enabled 
 researchers to develop efficient antibody drugs for treating cancers,
 autoimmune disorders, infectious diseases and many more\cite{Lu2020}.
-Their ability to target an immense variety of antigens allows for
-endless possibilities in application. 
 Four of the top 10 best-selling drugs in
@@
 All except one of these loops can be clustered
-into a limited number of `canonical structures'\cite{XXXX}. Therefore, modelling
+into a limited number of `canonical structures'\colorbox{green}{\cite{Al-Lazikani}}. Therefore, modelling
 these loops with adequate accuracy is commonly
-achievable\cite{North2011,Weitzner2015}. \lilian{Is the second reference relevant here?} However, the CDR loop 3 of the 
+achievable\cite{North2011}.  However, the CDR loop 3 of the 
 heavy chain (CDR-H3) has a far greater sequence variability due to the
@@
 According to the Kabat definition, the CDR-H3 loop is made up of the
-residues 95--105 (using the Kabat\cite{Kabat1992}, Chothia\cite{XXXX} or Martin\cite{XXXX} numbering schemes) in the heavy
+residues 95--105 (using the Kabat\colorbox{green}{\cite{Kabat1992}, Chothia\cite{Al-Lazikani} or Martin\cite{Abhinandan2008}} numbering schemes) in the heavy
 chain, with a potential insertion site at position 100. The
@@
 exceptionally long (Figure~\ref{fig:loopdist}).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{loopdist.eps}
-  \caption{Distribution of CDR-H3 loop lengths in mouse (left),
-    human (centre) and cow (right). Mouse and human antibody CDR-H3s
-    have a unimodal, yet almost normal distribution with a range of
-    $\sim$4--28 and 4--38 respectively. The length cut-off for CDR-H3s
-    depicted above is 30 amino acids. Bovine antibodies with
-    significantly longer CDR-H3 loops than depicted here exist,
-    reaching a length of 67 amino acids and
-    above\protect\cite{Wong2015}. \lilian{Do we need this?}}  
-  \label{fig:loopdist}
-\end{figure}
 
@@
 RosettaAntibody\cite{Sircar2009,Sivasubramanian2009}, 
-ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017} \lilian{Lyra, AbLooper} and our own abYmod.
+ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017}, \colorbox{green}{Lyra\cite{Klausen2015}, AbLooper\cite{Abanades2022}} and our own abYmod.
 One of the most
@@
 can be modelled rather well, often within 1\AA\ \ca~RMSD, for CDR-H3 loops
-the \lilian{not sure what `average' and `usually' mean here:} average is usually above 3\AA\cite{Almagro2011}.
+the \colorbox{green}{The average values are taken from the antibody modelling assessment} average is usually above 3\AA\cite{Almagro2011}.
 
@@
 \lilian{You already said it was a non-redundant set?} \highlight{Identical
-whole antibody structures were removed from the dataset}, \lilian{I don't understand this bit!} \highlight{while
+whole antibody structures were removed from the dataset}, \colorbox{green}{if the entire sequence is a match the structure is deleted.
+This step is probably unnecessary, given that there should be no such occurences in the non-redundant set.} while
 instances of different antibodies that matched in loop sequence were
-not removed}. 3D-Models of some of these structures with the same loop
+not removed. 3D-Models of some of these structures with the same loop
 sequence differ significantly. The few large RMSD ranges may stem from
-low resolution. For example, the \highlight{highest} \lilian{What does `highest' mean?} datapoint contains a structure with a
-resolution of 3.00\AA.  \lilian{Explain} \highlight{Residue differences near the loop may also
-explain the conformational difference}. Some of these structures are
+low resolution. \colorbox{green}{For example, the loop sequence with the largest RMSD range 
+has multiple structure files linked to it of varying quality, one of which has a resolution of only 3.00\AA. Residue differences near the loop may also
+explain the conformational difference of the loop itself, 
+even if the loop sequence does not differ}. Some of these structures are
 complexed while others are not, which may also affect the loop
@@
 
-They are also transformed \lilian{explain?} into a set of binary values according to a
-list of RMSD thresholds. This is done so that binary ML-models can be
+\colorbox{green}{The RMSD values are also transformed into a set of binary values according to a
+list of RMSD thresholds (i.e. a 1 is assigned to above and 0 to below a given threshold).} This is done so that binary ML-models can be
 trained, which will predict the probability e.g.\ that the 3D-model's RMSD

### 2022-10-12 paper.tex
Changes made according to comments. Some figures and some data still missing.

@@
   3D-models generated by antibody modelling software such as abYmod. The
-  newly developed predictor scored a Mathews Correlation Coefficient
+  newly developed predictor scored a Matthews Correlation Coefficient
   of 0.99, and can thus be described as highly reliable. The predictor
@@
 only weakly interacting with other antigens, or not at all.
-\colorbox{green}{This high affinity and high specificity sets them apart from other pharmaceuticals and makes them effective drugs with endless possibilities in application given their ability to target an immense variety of antigens.}
+This high affinity and high specificity sets them apart from other pharmaceuticals and makes them effective drugs with endless possibilities in application given their ability to target an immense variety of antigens.
 Furthermore, in contrast with small drug molecules, antibodies can not
 only bind pockets, but also flat, concave or convex
-surfaces\colorbox{green}{\cite{MacCallum1996}}. Their unique characteristics have enabled 
+surfaces\cite{MacCallum1996}. Their unique characteristics have enabled 
 researchers to develop efficient antibody drugs for treating cancers,
@@
 All except one of these loops can be clustered
-into a limited number of `canonical structures'\colorbox{green}{\cite{Al-Lazikani}}. Therefore, modelling
+into a limited number of `canonical structures'\cite{Al-Lazikani}. Therefore, modelling
 these loops with adequate accuracy is commonly
@@
 According to the Kabat definition, the CDR-H3 loop is made up of the
-residues 95--105 (using the Kabat\colorbox{green}{\cite{Kabat1992}, Chothia\cite{Al-Lazikani} or Martin\cite{Abhinandan2008}} numbering schemes) in the heavy
+residues 95--105 (using the Kabat\cite{Kabat1992}, Chothia\cite{Al-Lazikani} or Martin\cite{Abhinandan2008} numbering schemes) in the heavy
 chain, with a potential insertion site at position 100. The
@@
 RosettaAntibody\cite{Sircar2009,Sivasubramanian2009}, 
-ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017}, \colorbox{green}{Lyra\cite{Klausen2015}, AbLooper\cite{Abanades2022}} and our own abYmod.
+ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017}, Lyra\cite{Klausen2015}, AbLooper\cite{Abanades2022} and our own abYmod.
 One of the most
@@
 can be modelled rather well, often within 1\AA\ \ca~RMSD, for CDR-H3 loops
-the \colorbox{green}{The average values are taken from the antibody modelling assessment} average is usually above 3\AA\cite{Almagro2011}.
+the The average values are taken from the antibody modelling assessment average is usually above 3\AA\cite{Almagro2011}.
 
@@
 \section{Results}
-The software
-was tested on a test-set of antibody structures used in the 2014 and
-2011 Antibody Modelling Assessments
-\cite{Almagro2011,Almagro2014}. As the results depicted in
-Figure~\ref{fig:AMA} show, abYmod achieves results similar to, or better than,
-other modelling programs. However, the outliers with very high RMSD
-values increase abYmod's RMSD average. The predictor in this work
-would aim to identify such outlier 3D-models.
 
@@
     acid occurrence taken from \protect\url{http://abymod.abysis.org/} Visualized
-    using Seq2Logo. \lilian{What's the X-axis numbering? IMGT? Can you highlight the CDR residues (95--122) What range of lengths is included?}}
+    using Seq2Logo using Kabat Numbering}
   \label{fig:logo}
@@
 resolution worse than 4\AA\ were removed.
-\lilian{You already said it was a non-redundant set?} \highlight{Identical
-whole antibody structures were removed from the dataset}, \colorbox{green}{if the entire sequence is a match the structure is deleted.
-This step is probably unnecessary, given that there should be no such occurences in the non-redundant set.} while
-instances of different antibodies that matched in loop sequence were
+Instances of antibodies in our non-redundant dataset that matched in loop sequence were
 not removed. 3D-Models of some of these structures with the same loop
 sequence differ significantly. The few large RMSD ranges may stem from
-low resolution. \colorbox{green}{For example, the loop sequence with the largest RMSD range 
+low resolution. For example, the loop sequence with the largest RMSD range 
 has multiple structure files linked to it of varying quality, one of which has a resolution of only 3.00\AA. Residue differences near the loop may also
 explain the conformational difference of the loop itself, 
-even if the loop sequence does not differ}. Some of these structures are
+even if the loop sequence does not differ. Some of these structures are
 complexed while others are not, which may also affect the loop
@@
 
-\colorbox{green}{The RMSD values are also transformed into a set of binary values according to a
-list of RMSD thresholds (i.e. a 1 is assigned to above and 0 to below a given threshold).} This is done so that binary ML-models can be
+The RMSD values are also transformed into a set of binary values according to a
+list of RMSD thresholds (i.e. a 1 is assigned to above and 0 to below a given threshold). This is done so that binary ML-models can be
 trained, which will predict the probability e.g.\ that the 3D-model's RMSD
@@
 and how much information can be extracted. Different strategies were
-employed to represent \highlight{followed by}\lilian{???} BLOSUM62\cite{XXXX} and \highlight{NLF}\lilian{???}\cite{XXXX} encoding. The
-\highlight{physiochemical encoding}\lilian{explain} strategy was implemented for all ML-models, being
-the most effective. However, PCA-3 BLOSUM62\cite{XXXX}, a dimensionality-reduced
+employed to represent protein sequences numerically, such as BLOSUM62\cite{Henikoff1992} and NLF\cite{Nanni2011} encoding (a non-linear Fisher transform of a large set of physicochemical properties).
+The four-feature physiochemical encoding strategy\cite{Abhinandan2010} was implemented for all ML-models, being
+the most effective. However, PCA-3 BLOSUM62, a dimensionality-reduced
 BLOSUM62 encoding method achieved comparable results.
@@
 Our ML-model was trained on different feature sets selected using manual
-selection as well as \highlight{algorithmic selection strategies}\lilian{Which are?}, in order to
+selection as well as algorithmic selection strategies (see methods), in order to
 determine the most effective feature selection method. None of the
-feature selection methods was a best fit for all ML-models.\lilian{Explain}
+feature selection methods was a best fit for all ML-models.
+To create a ML-model implementing the encoding and feature selection strategies best suited for the specific ML-structure, a number of different combinations were tested, summarized in \ref{fig:results_table}.
+\begin{table}[results_table]
+    \centering
+    \begin{tabular}{c|c}
+         &  \\
+         & 
+    \end{tabular}
+    \caption{Summary of Results of different ML-model implementations.}
+    \label{tab:my_label}
+\end{table}
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{method.eps}
-  \caption {Simplified pipeline for creating the final machine
-    learning model (ML-model) that will predict 3D-model quality by giving its RMSD
-    range.}
-  \label{fig:method}
-\end{figure}
-
 The best ML-model, and its best hyperparameters, are then determined for
 each binary RMSD target. The set of binary ML-models outputs a number of
-predictions that give the likelihood\lilian{is it always a likelihood, or a confidence? Or is that the same thing?} of the 3D-model having an RMSD above
+predictions that give the likelihood of the 3D-model having an RMSD above
 the threshold value of the respective ML-model. These predictions are
@@
 
+The software
+was tested on a test-set of antibody structures used in the 2014 and
+2011 Antibody Modelling Assessments
+\cite{Almagro2011,Almagro2014}. As the results depicted in
+Figure~\ref{fig:AMA} show, abYmod achieves results similar to, or better than,
+other modelling programs. However, the outliers with very high RMSD
+values increase abYmod's RMSD average. The predictor in this work
+would aim to identify such outlier 3D-models.
+
 \section{Methods}
@@
 
-\subsubsection{BLOSUM 62 encoding}
+\subsubsection{BLOSUM 62 Encoding}
 The BLOSUM62 matrix reflects the frequencies of amino acid
@@
 Independent Component Analysis (ICA), projection-based methods (t-SNE,
-Isomap). Three components were used as features.\lilian{All three at once?
-  If not then what did you use in the final models?}
+Isomap). Three components were used as features. PCA was found to be the most effective dimensionality reduction method.
 
 \subsubsection{Physiochemical Feature Encoding}
-Nanni and Lumini\shortcite{XXXX} described a new encoding technique
-for machine learning classifiers. Many\lilian{How many?}
-physiochemical properties are calculated and transformed using a
-non-linear Fisher transform for dimensionality reduction.  A vector of
-length 19 is produced for each amino acid\highlight{34}\lilian{What is this?}. 
-Martin and Abhinandan\shortcite{XXXX} introduced an encoding using
-four physiochemical features \highlight{25}\lilian{What is this?}:
+Martin and Abhinandan\shortcite{Abhinandan2010} introduced an encoding using
+four physiochemical features:
 the total number of sidechain atoms; the
@@
 
+NLF-encoding \shortcite{Nanni2011} describes a new peptide encoding technique optimized for use with machine learning classifiers.
+A non-linear Fisher transform is applied to the whole set of physiochemical properties in \shortcite{Kawashima2000}
+physiochemical properties are calculated and transformed using a
+non-linear Fisher transform for dimensionality reduction.  A vector of
+length 19 is produced for each amino acid.
+
+\subsubsection{NLF Encoding}
+This method of encoding is detailed by Nanni and Lumini in their paper.
+It takes many physicochemical properties and transforms them using a Fisher Transform (similar to a PCA) creating a smaller set of features that can describe the amino acid just as well.
+There are 19 transformed features.
+
 \subsection{Dataset-splitting}
 The final ML-model was evaluated using a test set, separated from the
-training set at the start in a 30/70 split (lock-box principle)
-\highlight{35}\lilian{What is this?}. The performance of all individual sub-ML-models of the first layer
-was determined using stratified K-folds cross-validation (K=10) as the
-dataset is imbalanced, being skewed towards lower RMSD values. The
+training set at the start in a 30/70 split. The performance of all individual sub-ML-models of the first layer was determined using stratified K-folds cross-validation (K=10) as the
+dataset is imbalanced, being skewed towards lower RMSD values\cite{Krstajic2014,Kohavi1995}. The
 method is different from normal K-folds cross validation as it uses
-stratified sampling instead of random sampling.
-\lilian{I think it is still random, it's just that it is selected to represent the imbalance properly}
-This ensures each
-class is represented, as the percentage of samples for each class is
+stratified sampling, which is also random, but selections are made to represent class imbalance.
+This ensures each class is represented, as the percentage of samples for each class is
 preserved.
-A validation set, usually used for testing during the optimization
-stage was omitted in favour of stratified K-folds cross-validation
-(k=10)\cite{Krstajic2014,Kohavi1995}.
-\lilian{I don't really understand what you mean here. The stratified
-  cross-validation is going to use a test set in each fold --- it's
-  just that this is selected to fairly represent the imbalance in the
-  training data. Normally the validation set is the set that is held
-  back for final testing --- which you say you did.}
 
@@
 differently and must thus be considered separately. The Matthews
-Correlation Coefficient (MCC)\cite{Matthews1975}\lilian{That's the wrong Matthews!!!} is deemed the most
+Correlation Coefficient (MCC)\cite{Chicco2020} is deemed the most
 informative, taking the ratios of the four confusion matrix categories
-into account \highlight{39}\lilian{What is this? There are two papers on MCC being the best.} and is thus more reliable than the F1 score and
-accuracy. It is also \highlight{consistent}\lilian{is that the correct word?!} for both binary and multi-class
-problems and therefore well suited for our purpose.\lilian{How is MCC calculated for multi-class prediction?}
+into account and is thus more reliable than the F1 score and
+accuracy. It is also consistent for both binary and multi-class
+problems and therefore well suited for our purpose.\cite{Jurman2012}
 

### 2022-12-16 paper.tex
Fixed table reference
Updates from Overleaf

@@
 \usepackage{color}
+\usepackage[utf8]{inputenc}
+\usepackage{amsmath}
+
+\usepackage{tabularx} 
+\setlength\extrarowheight{2pt} % make the tables look less cramped
+\usepackage{graphicx}
+\usepackage{adjustbox}
 \newcommand{\ca}{\mbox{C$\alpha$}}
@@
 
-\title{Predicting the Quality of CDRH3 Antibody Loop Structural Models}
+\title{Predicting the Quality of CDR-H3 Antibody Loop Structural Models}
 \author{Lilian M.\ Denzler and Andrew C.R.\ Martin\\
-Structural and Molecular Biology, Division of Biosciences,\\
+Institute of Structural and Molecular Biology, Division of Biosciences,\\
 University College of London,\\
@@
   hypervariable loops, also known as the Complementary Determining
-  Regions (CDRs), all of which can be modelled with adequate accuracy,
-  except for one. It remains remarkably difficult to model the third CDR
-  loop of the antibody heavy chain. CDR-H3 has
+  Regions (CDRs), all of which can be modelled with high accuracy,
+  except for CDR-H3, which generally has
   far greater length and sequence variability, with such great structural
@@
   abYmod software, have been developed. Although such efforts have
-  improved prediction accuracy the results for CDR-H3 are
+  improved prediction accuracy, the results for CDR-H3 are
   still inconsistent and require further improvement. Providing a
@@
 are produced in response to a foreign substance, called an antigen. A
-mature antibody binds a specific antigen with high affinity, while
-only weakly interacting with other antigens, or not at all.
-This high affinity and high specificity sets them apart from other pharmaceuticals and makes them effective drugs with endless possibilities in application given their ability to target an immense variety of antigens.
-Furthermore, in contrast with small drug molecules, antibodies can not
+mature antibody binds a specific antigen with high affinity and specificity.
+This sets them apart from other pharmaceuticals and makes them effective drugs with endless possibilities in application given their ability to target an immense variety of antigens.
+In contrast with small drug molecules, antibodies can not
 only bind pockets, but also flat, concave or convex
@@
 their structure is essential. The acquired structural information can
-be used to increase binding affinity to a target of interest,
+be used to modify binding affinity to a target of interest,
 predicting both the exact binding site and the antibody stability as
@@
 achievable\cite{North2011}.  However, the CDR loop 3 of the 
-heavy chain (CDR-H3) has a far greater sequence variability due to the
+heavy chain (CDR-H3) has a far greater sequence and length variability due to the
 processes of V(D)J recombination and somatic hyper‐mutation and its
@@
 
+The classifier predicts whether a 3D-model has an RMSD of below 2\AA,
+between 2--4\AA, or above 4\AA. These cutoff values were selected
+based on the observation that abYmod generally produces a 3D-model with
+RMSD below 4\AA. Incorrectly modelled structures (Figure~\ref{fig:AMA}) may
+be identified by screening for structures estimated to have an RMSD
+above 4\AA. If a very high-quality 3D-model is needed one should also
+exclude 3D-models with RMSD above 2\AA.
+
 \begin{figure}
@@
     outperforms other modelling software in some instances, but also
-    has much lower accuracy in few outlier cases. Left: an abYmod
-    structure for C705 could be generated, yet the RMSD calculation
-    failed \lilian{Why? I'm sure we can resolve this!}.
+    has much lower accuracy in few outlier cases. 
     Right: Ab01 is the rabbit antibody PDB:4MA3, which was
@@
     shown for the methods, where generated 3D-models were adequate for
-    RMSD calculation. \lilian{This needs better explanation}}
+    RMSD calculation.}
   \label{fig:AMA}
@@
 the final ML-model, the general trend being that the more binary
-classifiers are used, the better the nominal prediction. \lilian{Data?}
+classifiers are used, the better the nominal prediction.
 
@@
 To create a ML-model implementing the encoding and feature selection strategies best suited for the specific ML-structure, a number of different combinations were tested, summarized in \ref{fig:results_table}.
-\begin{table}[results_table]
+Additional ML-Models were discarded due to poor performance.
+\begin{table}[]
+\fontsize{12}{16}\selectfont
   \centering
-    \begin{tabular}{c|c}
-         &  \\
-         & 
-    \end{tabular}
-    \caption{Summary of Results of different ML-model implementations.}
-    \label{tab:my_label}
+  \caption{Summary of Machine-Learning Classifier Performances}
+  \label{my-label}
+
+  \begin{adjustbox}{width=\textwidth}
+
+    \begin{tabularx}{\linewidth}{
+    |>{\hsize=.35\hsize}X|% 10% of 4\hsize 
+    >{\hsize=.4\hsize}X|% 30% of 4\hsize
+    >{\hsize=.4\hsize}X|% 30% of 4\hsize 
+    >{\hsize=.4\hsize}X|% 30% of 4\hsize
+    >{\hsize=.4\hsize}X|% 30% of 4\hsize 
+    >{\hsize=.4\hsize}X|% 30% of 4\hsize
+    >{\hsize=.2\hsize}X|% 30% of 4\hsize
+       % sum=4.0\hsize for 4 columns
+  }
+\hline
+Features & Feature Selection Method & Optimi-zation Method& Multi/ Single-layer & First-layer weighted &Classifier Type & MCC\\
+\hline
+Basic & None & None & single & No & SVC & 0.54\\
+Basic & None & Genetic Algorithm & single & No & SVC & 0.54 \\
+All & None & None & single& No & Random Forest & 0.58\\
+Selected & random forest feature selection & Genetic Algorithm & Single& No & Soft Voting & 0.59 \\
+Selected & random forest feature selection & Genetic Algorithm & Multi& Yes & XGB & 0.63 \\
+Selected & recursive feature elimination & Genetic Algorithm & Multi& Yes & XGB & 0.79 \\
+Selected & recursive feature elimination & Genetic Algorithm & Multi& Yes & Decision-Tree & 0.99 \\
+Selected (no log-file features) & recursive feature elimination & Genetic Algorithm & Multi& Yes & Voting(soft) & 0.92 \\
+\hline
+    \end{tabularx}
+
+  \end{adjustbox}
+
 \end{table}
-
-\lilian{So, having read this, I have no idea what feature encoding you
-  actually used, or where to find that information. What worked and
-  what didn't? Where can I find a comparison of the performance?}
+\caption{table caption}
 
@@
 gradient boosting (XGBoost)\cite{Chen2016}.
-\lilian{OK, but this is the Results section, so where are the results
-  of using the different methods?}
 
@@
 The overall best final ML-model was composed of several different binary
-classifiers,\lilian{More detail!} with an extreme gradient boosting (XGBoost) top-layer
-nominal classifier. Features were selected using random forest feature
-selection.
-\lilian{Explain how this works and which features were selected --- and how many?}
-A final MCC\lilian{Explain how MCC is calculated over 3 classes} value of 0.99 could be achieved for an ML-model
-using the abYmod log file \lilian{What parameters are actually used?} as input as well as the loop 3D-model file
+classifiers, \ref{fig:flow} with an extreme gradient boosting (XGBoost) top-layer
+nominal classifier.
+Features were selected using a recursive feature elimination algorithm, through which a the weakest feature is removed recursively and the model performance is tested.
+In the final model 9 features are included: in the final model, the following features were included: tip\_pos, protrusion, length, total\_charge, nr\_charged, identity, similarity, Hydropathy and Hydropathy\_diff \ref{fig:feature_table}.
+
+A final MCC value of 0.99 could be achieved for an ML-model
+using the abYmod log file as input as well as the loop 3D-model file
 itself. This value slightly dropped to 0.92 if no such log file was
-given. This is mainly\lilian{is there anything else?} due to the fact that the template sequence
+given. This is due to the fact that the template sequence
 abYmod used to generate the 3D-model is unknown in the latter case.
-
-\lilian{I'm not sure this is in the most logical place --- isn't this
-  something that was chosen at the start? (At least in terms of
-  telling the story}
-The classifier predicts whether a 3D-model has an RMSD of below 2\AA,
-between 2--4\AA, or above 4\AA. These cutoff values were selected
-based on the observation that abYmod generally produces a 3D-model with
-RMSD below 4\AA. Incorrectly modelled structures (Figure~\ref{fig:AMA}) may
-be identified by screening for structures estimated to have an RMSD
-above 4\AA. If a very high-quality 3D-model is needed one should also
-exclude 3D-models with RMSD above 2\AA.
 
@@
 would aim to identify such outlier 3D-models.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{flowchart_qualiloop.eps}
+  \caption {Simplified pipeline for creating the final machine learning model that will predict 3D-model quality by giving its RMSD range.}
+  \label{fig:flow}
+\end{figure}
 
@@
 Using AbDb's redundancy information it was ensured that no antibodies
-were present in the dataset more than once. \highlight{The dataset was
-  additionally screened for duplicate instances.}
-\lilian{Did you find any? How was this screening done? It's far from trivial}
+were present in the dataset more than once.
 
 \subsubsection{Scaling}
-Normalization and Standardization\lilian{What's the difference? Explain what they are.} were tested as scaling methods. Both
+Normalization and Standardization were tested as scaling methods.
+In normalization the range of the data is fixed between 0 and 1, while in Standardization the data is re-scaled to fit a Gaussian distribution.
+Both
 approaches are greatly influenced by outliers, and such datapoints are
@@
 \subsection{Feature Calculations}
-\begin{figure}
+
+\begin{table}[]
   \centering
-  \includegraphics[width=\linewidth]{feature_table.eps}
-  \caption {A summary of how different feature values were calculated. \lilian{It's a table! Why import it?}}
+  \caption{A summary of how different feature values were calculated.}
   \label{fig:feature_table}
-\end{figure}
+
+  \begin{adjustbox}{width=\textwidth}
+
+    \begin{tabular}{| m{5em} | m{20em}| m{20em} |}
+    \hline
+Feature Name & Description & method of Calculation \\
+\hline
+\hline
+Sequence & Amino acid sequence of the CDR-H3 loop. & Sequence is given in one-letter amino acid codes.\\
+\hline
+Length & Number of residues in the CDRH3-loop, which is located at residues H95-H102. & The number of residues are counted.\\
+\hline
+Sequence Identity & Sequence identity of selected template (SeqA) with input loop sequence (SeqB) is determined after sequence alignment.
+Calculated by abYmod during modelling.
+& $Identity(SeqA,SeqB) = 100\%\frac{identical residues}{length(alignment)}$\\
+\hline
+Sequence similarity & Sequence similarity of selected template (SeqA) with input loop sequence (SeqB) is determined after sequence alignment.
+Calculated by abYmod during modelling.
+Similar residues are residues that have undergone conservative substitution.
+&
+$Similarity(SeqA,SeqB) = 100\%\frac{identical residues+similar residues}{length(alignment)}$\\
+\hline
+Loop Protrusion & Distance of loop residue further away from the loop base & Geometrical calculations \protect\ref{fig:loopdist} \\
+\hline
+Protruding residue & The Amino acid code of the most protruding loop residue & Using the previously determined point furthest away from the loop base, the residue at this coordinate is determined and given as a one-letter amino acid code.\\
+\hline
+Charge & Total charge of the loop & Sum of charges of all residues in loop \\
+\hline
+Charge difference & Difference in total charge compared to template sequence & Difference between the two summed changes \\
+\hline
+Hydrophobicity & Mean Hydrophobicity values of loop & Based on Eisenberg consensus values\\
+\hline
+Hydrophobicity  difference & Sum of absolute differences between loop sequence and template loop& Based on Eisenberg consensus values\\
+\hline
+Accessibility & Total and average accessibility for the loop& lee-Richards method implemented using the pdbsolv method from the BiopTools library.\\
+\hline
+Side-chain Accessibility & Total and average side-chain accessibility for the loop& lee-Richards method implemented using the pdbsolv method from the BiopTools library.\\
+\hline
+Relative Accessibility & Total and average relative accessibility for the loop& lee-Richards method implemented using the pdbsolv method from the BiopTools library.\\
+\hline
+relative side-chain Accessibility & Total and average relative side-chain accessibility for the loop& lee-Richards method implemented using the pdbsolv method from the BiopTools library.\\
+\hline
+Happiness & Happiness score, taking accessibility and hydropobicity into account.
+If a residue is 'happy' it will not be a buried hydrophilic or a surface hydrophobic residue.
+& Hydrophobicity values (see above) are normalized to a range of -1 to +1.
+Mean accessibility values are calculated as above.
+If hydrophobicity of loop is $<0$:
+$Happiness = 1+Hydrophobicity(1-Accessibility)$
+Otherwise:
+$Happiness = 1-(Hydrophobicity Accessibility)$\\
+\hline
+Nr.
+of Contacts & Nr of contacts made by the residue of the loop within a range of 3.5\AA.
+Includes mainchain as well as sidechain atoms.
+Contacts made with residue within and outside of the loop are counted separately and as total.
+The ratio of inside vs outside is also calculated.
+& Modified version of the rangecontacts method in the BiopTools library.
+\\
+\hline
+Energy & Potential energy of the model. & Calculated by Gromacs during energy minimization step in abYmod modelling. \\
+\hline
+Lowest BLOSUM 62 Scoring Residue Pair & Each possible residue pair in the CDR-H3loop is scored by their BLOSUM 62 score.
+The lowest scoring pair's BLOSUM62 value will be combined with their residue separation to form the metric.
+& With separation being hte nuber of residues between the worst residue pair, and the worst score being the lowest BLOSUM62 score achieved by a residue pair, the metric is calculated as follows: $WorstBLOSUM = -log_2(separation)(worst score)$
+\hline
+
+    \end{tabular}
+
+  \end{adjustbox}
+
+\end{table}
 
@@
   \centering
-  \includegraphics[width=\linewidth]{angle.eps}
-  \caption {Diagram \lilian{Needs a much simpler cartoon diagram --- it's difficult to see anything from this!}
+  \includegraphics[scale=0.5]{protrusion.eps}
+  \caption {Diagram
     visualizing the process underlying the protrusion
     calculation. First, the base residues (i.e.\ H95 and H102, shown as
-    red spheres) of the CDR-H3 (shown in red) are identified. Then, a
-    line is drawn between the two \ca\ atoms of these residues (yellow
-    dashed line). The distance of the \ca-atom of each residue in the
-    CDR-H3 loop to this line is calculated. The residue which has the
-    greatest distance to the line (shown as green sphere) is output
-    as one-letter amino acid code and used as feature. The distance in
-    \AA\ (depicted as yellow arrow) is used as the `protrusion'
-    feature. \lilian{It's unclear whether you use both distance and amino acid, or just one of these.}}
+    red spheres) of the CDR-H3 (grey circles) are identified. Then, a
+    line is drawn between the two \ca\ atoms of these residues.
+    The distance of the \ca-atom of each residue in the
+    CDR-H3 loop to this line is calculated (d). The residue which has the
+    greatest distance to the line is output
+    as one-letter amino acid code and used as feature. The distance d in
+    \AA\is used as the `protrusion'
+    feature.}
   \label{fig:angle}
@@
 tested. No one fit-for-all method for the different ML-models could be
-found.\lilian{I'm not sure what this means.} However, for our top-layer classifier in our final ML-model
+found. However, for our top-layer classifier in our final ML-model
 recursive feature elimination worked best.
@@
 
-\highlight{In a future research project residue patterns in correlation with RMSD
-may be analyzed. Possibly, one might identify certain sequence
-patterns that make accurate modelling with abYmod more
-difficult. Furthermore, separate classifiers according to loop length
-can be built. Given that loop length is the most important determinant
-of 3D-model quality, this approach may yield some insight into the
-challenges of modelling shorter \emph{vs.} longer loops.
-One could also conduct an analysis of the predictor's behaviour when
-abYmod is forced to use LoopDB-based modelling. This might shed light
-on whether the ML-model presented in this paper is biased towards
-abYmod's used source of template structures. It would also give an
-indication of how well the predictor would work in combination with
-other modelling software.}\lilian{We don't really need this, but can we see any trends from the feature selection?}
-
-\lilian{We need a concluding paragraph relating back to the
-  introduction and what this contributes to improvements in using
-  antibody models.}
-
 \bibliography{references}

### 2022-12-16 paper.tex
Fixed some LaTeX errors

@@
 Additional ML-Models were discarded due to poor performance.
+
 \begin{table}[]
@@
   \end{adjustbox}
-
 \end{table}
-\caption{table caption}
 
@@
 The lowest scoring pair's BLOSUM62 value will be combined with their residue separation to form the metric.
-& With separation being hte nuber of residues between the worst residue pair, and the worst score being the lowest BLOSUM62 score achieved by a residue pair, the metric is calculated as follows: $WorstBLOSUM = -log_2(separation)(worst score)$
+& With separation being hte nuber of residues between the worst residue pair, and the worst score being the lowest BLOSUM62 score achieved by a residue pair, the metric is calculated as follows: $WorstBLOSUM = -log_2(separation)(worst score)$\\
 \hline
@@
     The distance of the \ca-atom of each residue in the
-    CDR-H3 loop to this line is calculated (d). The residue which has the
+    CDR-H3 loop to this line is calculated ($d$). The residue which has the
     greatest distance to the line is output
-    as one-letter amino acid code and used as feature. The distance d in
-    \AA\is used as the `protrusion'
+    as one-letter amino acid code and used as feature. The distance $d$ in
+    \AA\ is used as the `protrusion'
     feature.}

### 2022-12-19 paper.tex
Various text and layout cleanup

@@
 \usepackage{amsmath}
+\usepackage{lscape}
+\usepackage{longtable}
 
@@
   hypervariable loops, also known as the Complementary Determining
-  Regions (CDRs), all of which can be modelled with high accuracy,
-  except for CDR-H3, which generally has
-  far greater length and sequence variability, with such great structural
-  diversity, that modelling it is considerably harder.
+  Regions (CDRs), all of which can generally be modelled with high accuracy,
+  except for CDR-H3, which has
+  far greater length, sequence and structural variability, 
+  making modelling it is considerably harder.
 
@@
   differentiating well-modelled structures from incorrectly modelled
-  structures, giving the abYmod user a clearer understanding of the
+  structures, giving the user a clearer understanding of the
   generated 3D-model reliability.
@@
 processes of V(D)J recombination and somatic hyper‐mutation and its
-structure has remained unclassifiable\cite{Finn2016}. The variety in
+structure has remained mostly unclassifiable\cite{Finn2016}. The variety in
 structure is so great, that its structural diversity is remarkable
-even compared to other protein loops\cite{Regep2017}. It was found
+even compared with other protein loops\cite{Regep2017}. It was found
 that over 75\% of CDR-H3 loops do not have a sub-{\AA}ngstr\"{o}m non-antibody
 structural neighbour, while 30\% of CDR-H3 loops have a
-completely unique structure compared with under 3\% for all non-antibody
+completely unique structure, compared with under 3\% for all non-antibody
 loops\cite{Regep2017}.
@@
 According to the Kabat definition, the CDR-H3 loop is made up of the
-residues 95--105 (using the Kabat\cite{Kabat1992}, Chothia\cite{Al-Lazikani} or Martin\cite{Abhinandan2008} numbering schemes) in the heavy
-chain, with a potential insertion site at position 100. The
+residues H95--H102 (using the Kabat\cite{Kabat1992}, Chothia\cite{Al-Lazikani} or Martin\cite{Abhinandan2008} numbering schemes) in the heavy
+chain, with a potential insertion site at position H100. The
 possibility of such an insertion of a varying number of residues leads
 to a large range of loop lengths, with bovine antibodies being
-exceptionally long (Figure~\ref{fig:loopdist}).
+exceptionally long (Figure~\ref{fig:loopdist}).\lilian{Figure missing!}
 
 For shorter loops, a higher prediction accuracy can be achieved than
-for longer CDR-H3 loops. This was also shown by the Antibody Modelling
+for longer CDR-H3 loops. This was also shown in the Antibody Modelling
 Assessments (AMA), two blind contests that required researchers to
-build three-dimensional structural models (3D-models) from antibody sequences. The CDR-H3 loop
-modelling quality achieved at the contests was on average much lower
+build three-dimensional structural models (`3D-models' --- used throughout this text to distinguid from machine-learning models `ML-models') from antibody sequences. The CDR-H3 loop
+modelling quality achieved at the contests was, on average, much lower
 for loops of longer lengths\cite{Almagro2011,Almagro2014}.
@@
 Several different approaches for generating 
-3D-models from antibody sequences exist such as
+3D-models from antibody sequences exist including
 RosettaAntibody\cite{Sircar2009,Sivasubramanian2009}, 
-ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017}, Lyra\cite{Klausen2015}, AbLooper\cite{Abanades2022} and our own abYmod.
+ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017}, Lyra\cite{Klausen2015}, AbLooper\cite{Abanades2022} and our own abYmod (manuscript in preparation).
 One of the most
@@
 
-abYmod selects light and heavy chains separately from PDB templates.
+abYmod selects light and heavy chain frameworks separately from PDB templates.
 First these are selected on the basis of the number of matched
@@
 currently in development. Any CDRs where there was no canonical match are then
-are grafted onto the framework. If there is no template of the correct
+grafted onto the framework. If there is no template of the correct
 length for CDR-H3, the loop is built using LoopDB, a database of
@@
 
-Using these mentioned modelling methods, framework regions can
-generally be predicted with great accuracy (with better than 1\AA\
-RMSD\cite{Almagro2014}), as one can often find a very similar
+Using these modelling methods, framework regions can
+generally be predicted with great accuracy (better than 1\AA\
+\ca~RMSD\cite{Almagro2014}), as one can often find a very similar
 structure for the homology modelling process.  However, the CDR loops
@@
 canonical conformation of CDR loops CDR-L1,L2,L3,H1,H2 can be identified, they too
-can be modelled rather well, often within 1\AA\ \ca~RMSD, for CDR-H3 loops
-the The average values are taken from the antibody modelling assessment average is usually above 3\AA\cite{Almagro2011}.
+can be modelled rather well, often within 1\AA\ \ca~RMSD. \highlight{for CDR-H3 loops
+the The average values are taken from the antibody modelling assessment average} is usually above 3\AA\cite{Almagro2011}. \lilian{Something odd here --- not sure what it's supposed to say!}
 
@@
 3D-model. The given score is the probability that a specific region
-(e.g.\ CDR-H2) will be will be modelled within a specific RMSD
+(e.g.\ CDR-H2) will be modelled within a specific RMSD
 threshold\cite{Leem2016}. Thus, it can be used to obtain an expected
-RMSD value for a given probability (default 75\%). For the CDR-H3 this
+RMSD value for a given probability (default 75\%). For CDR-H3, this
 score is calculated as a function of the loop length.  The confidence
 scorer is described as robust, but less accurate in the case of CDR
-loops due to the lack of data\cite{Leem2016}. ABLooper also provides a
+loops owing to the lack of data\cite{Leem2016}. ABLooper also provides a
 confidence metric for the CDR-H3 loop 3D-model, which is estimated by the
@@
 to determine how accurate a generated structural 3D-model is within the
-H3 region. Therefore, we have produced a
+CDR-H3 region. Therefore, we have produced a
 user-friendly predictor of CDR-H3 3D-model quality. The predictor will give
@@
 
-The predictive power of any machine learning model (ML-model) is largely
+The predictive power of any machine learning model (`ML-model') is largely
 dependent on the quality and size of the dataset on which it was trained. As
@@
 Instances of antibodies in our non-redundant dataset that matched in loop sequence were
-not removed. 3D-Models of some of these structures with the same loop
-sequence differ significantly. The few large RMSD ranges may stem from
+not removed as 3D-Models \lilian{Just checking you mean models not structures?
+Do the structures also differ significantly, or do you really mean that the error varies significantly?} of some of these structures with the same loop
+sequence differ significantly.
+\lilian{If I understand correctly, you mean that CDR-H3 could have the same sequence in multiple structures, but the overall sequence was different?}
+The few large RMSD ranges may stem from
 low resolution. For example, the loop sequence with the largest RMSD range 
@@
 RMSD range must be divided into categories. This is done either by
-creating uniform classes i.e.\ 1--2\AA, 2--3\AA, etc., (the optimal size of which
-must be determined), or by creating balanced classes. When
+creating uniform classes (e.g.\ 1--2\AA, 2--3\AA, etc.), the optimal size of which
+must be determined, or by creating balanced classes. When
 creating balanced classes, the upper and lower thresholds of a
 category are chosen in such a way that each class contains an equal
-number of instances. This approach was chosen to counteract the
+number of instances. Initially, this approach was chosen to counteract the
 skewness of the RMSD distribution. However, this was found to
-affect the final ML-model's predictive power negatively. Therefore,
+have a negative effect on the final ML-model's predictive power, so
 uniform classes were used.
@@
 trained, which will predict the probability e.g.\ that the 3D-model's RMSD
-is above 2\AA, 2.2\AA, 2.4\AA, and so on. The number of binary
-classifiers incorporated into the first layer has a great effect on
+is above 2\AA, 2.2\AA, 2.4\AA, and so on. \highlight{The number of binary
+classifiers incorporated into the first layer} \lilian{You need to describe the overall architecture first so this makes sense.
+I would have a much simpler version of Figure~\ref{fig:flow} which just shows the ML architecture}  has a great effect on
 the final ML-model, the general trend being that the more binary
@@
 employed to represent protein sequences numerically, such as BLOSUM62\cite{Henikoff1992} and NLF\cite{Nanni2011} encoding (a non-linear Fisher transform of a large set of physicochemical properties).
-The four-feature physiochemical encoding strategy\cite{Abhinandan2010} was implemented for all ML-models, being
-the most effective. However, PCA-3 BLOSUM62, a dimensionality-reduced
-BLOSUM62 encoding method achieved comparable results.
+However, the simple four-feature physiochemical encoding strategy\cite{Abhinandan2010} was implemented for all ML-models, as it was found to be
+the most effective, although PCA-3 BLOSUM62, a dimensionality-reduced
+BLOSUM62 encoding method, achieved comparable results.
 Feature selection was conducted to improve the ML-model's learning
@@
 
-Our ML-model was trained on different feature sets selected using manual
-selection as well as algorithmic selection strategies (see methods), in order to
-determine the most effective feature selection method. None of the
+In order to
+determine the most effective feature selection method, the
+ML-model was trained on different feature sets selected using manual
+selection as well as algorithmic selection strategies (see methods).
+None of the
 feature selection methods was a best fit for all ML-models.
-To create a ML-model implementing the encoding and feature selection strategies best suited for the specific ML-structure, a number of different combinations were tested, summarized in \ref{fig:results_table}.
+To create a ML-model implementing the encoding and feature selection strategies best suited for the specific \highlight{ML-structure} \lilian{What is this?}, a number of different combinations were tested, summarized in Table~\ref{tab:results_table}.
 Additional ML-Models were discarded due to poor performance.
 
-\begin{table}[]
-\fontsize{12}{16}\selectfont
+\begin{table}
   \centering
-  \caption{Summary of Machine-Learning Classifier Performances}
-  \label{my-label}
+  \caption{Summary of Machine-Learning Classifier Performances \lilian{Is this just the top-level classifier?
+You need something providing this sort of info for the final selection for the binary classifiers.
+What is multi-/single-layer?
+What is `First-layer weighted'?
+Is it needed given that i is always Yes for Multi and No for Single?
+What is `SVC'?
+Is `Soft Voting' the same as `Voting(soft)'?
+What are `Basic' features?}}
+  \label{tab:results_tableX}
 
-  \begin{adjustbox}{width=\textwidth}
-
-    \begin{tabularx}{\linewidth}{
-    |>{\hsize=.35\hsize}X|% 10% of 4\hsize 
-    >{\hsize=.4\hsize}X|% 30% of 4\hsize
-    >{\hsize=.4\hsize}X|% 30% of 4\hsize 
-    >{\hsize=.4\hsize}X|% 30% of 4\hsize
-    >{\hsize=.4\hsize}X|% 30% of 4\hsize 
-    >{\hsize=.4\hsize}X|% 30% of 4\hsize
-    >{\hsize=.2\hsize}X|% 30% of 4\hsize
-       % sum=4.0\hsize for 4 columns
-  }
-\hline
-Features & Feature Selection Method & Optimi-zation Method& Multi/ Single-layer & First-layer weighted &Classifier Type & MCC\\
-\hline
-Basic & None & None & single & No & SVC & 0.54\\
-Basic & None & Genetic Algorithm & single & No & SVC & 0.54 \\
-All & None & None & single& No & Random Forest & 0.58\\
-Selected & random forest feature selection & Genetic Algorithm & Single& No & Soft Voting & 0.59 \\
-Selected & random forest feature selection & Genetic Algorithm & Multi& Yes & XGB & 0.63 \\
-Selected & recursive feature elimination & Genetic Algorithm & Multi& Yes & XGB & 0.79 \\
-Selected & recursive feature elimination & Genetic Algorithm & Multi& Yes & Decision-Tree & 0.99 \\
-Selected (no log-file features) & recursive feature elimination & Genetic Algorithm & Multi& Yes & Voting(soft) & 0.92 \\
-\hline
-    \end{tabularx}
-
-  \end{adjustbox}
+  \small
+  \begin{tabular}{lllllll}\hline
+    Features        & Feature       & Parameter         & Multi- / & First-    & Classifier    & MCC  \\
+                    & Selection     & Optimization      & Single-  & layer     & Type          &      \\
+                    & Method        & Method            & layer    & weighted  &               &      \\ \hline
+    Basic           & None          & None              & Single   & No        & SVC           & 0.54 \\
+    Basic           & None          & GA$^\dag$         & Single   & No        & SVC           & 0.54 \\
+    All             & None          & None              & Single   & No        & Random Forest & 0.58 \\
+    Selected        & Random Forest & GA                & Single   & No        & Soft Voting   & 0.59 \\
+    Selected        & Random Forest & GA                & Multi    & Yes       & XGBoost       & 0.63 \\
+    Selected        & Recursive     & GA                & Multi    & Yes       & XGBoost       & 0.79 \\
+                    & Feature       &                   &          &           &               &      \\
+                    & Elimination   &                   &          &           &               &      \\
+    Selected        & Recursive     & GA                & Multi    & Yes       & Decision-Tree & 0.99 \\
+                    & Feature       &                   &          &           &               &      \\
+                    & Elimination   &                   &          &           &               &      \\
+    Selected-NL$^*$ & Recursive     & GA                & Multi    & Yes       & Voting (soft) & 0.92 \\
+                    & Feature       &                   &          &           &               &      \\
+                    & Elimination   &                   &          &           &               &      \\ \hline
+    \multicolumn{7}{l}{$^*$ No log-file features} \\
+    \multicolumn{7}{l}{$^\dag$ Genetic algorithm} \\
+    \end{tabular}
 \end{table}
@@
 
-The best ML-model, and its best hyperparameters, are then determined for
+The best ML-model, and its best hyperparameters, were then determined for
 each binary RMSD target. The set of binary ML-models outputs a number of
@@
 then added to the feature set, on which a top-layer classifier is then
-trained (Figure~\ref{fig:method}). Thus, a quasi-voting-system is incorporated into the final
+trained (Figure~\ref{fig:method})\lilian{Incorrect reference}. Thus, a quasi-voting-system is incorporated into the final
 classifier, in which a set of weaker classifiers vote on the ML-model
@@
 The overall best final ML-model was composed of several different binary
-classifiers, \ref{fig:flow} with an extreme gradient boosting (XGBoost) top-layer
-nominal classifier.
-Features were selected using a recursive feature elimination algorithm, through which a the weakest feature is removed recursively and the model performance is tested.
-In the final model 9 features are included: in the final model, the following features were included: tip\_pos, protrusion, length, total\_charge, nr\_charged, identity, similarity, Hydropathy and Hydropathy\_diff \ref{fig:feature_table}.
+classifiers, (Figure~\ref{fig:flow}) with an extreme gradient boosting (XGBoost) top-layer
+nominal classifier. Features were selected using a recursive feature
+elimination algorithm, through which the weakest feature is removed
+recursively and the model performance is tested. In the final model, 9
+features are included: tip\_pos, protrusion, length, total\_charge, nr\_charged,
+identity, similarity, Hydropathy and Hydropathy\_diff
+(See Table~\ref{tab:feature_table}).
+\lilian{This appears to be the top level.
+What about a table showing the features used for each of the binary predictors and its MCC and anything else unique to that classifier (e.g.
+feature selection method)?}
 
@@
 given. This is due to the fact that the template sequence
-abYmod used to generate the 3D-model is unknown in the latter case.
+abYmod used to generate the 3D-model is unknown in the latter case
+and therefore, sequence identity, similarity and hydropathy difference cannot be calculated. The energy is also not available.
+\lilian{There is no option to upload the log file on the web site!}
 
@@
 \cite{Almagro2011,Almagro2014}. As the results depicted in
-Figure~\ref{fig:AMA} show, abYmod achieves results similar to, or better than,
-other modelling programs. However, the outliers with very high RMSD
+Figure~\ref{fig:AMA} show, abYmod generally achieves results similar to, or better than,
+other modelling programs. However, some outliers with very high RMSD
 values increase abYmod's RMSD average. The predictor in this work
@@
   \includegraphics[width=\textwidth]{flowchart_qualiloop.eps}
-  \caption {Simplified pipeline for creating the final machine learning model that will predict 3D-model quality by giving its RMSD range.}
+  \caption {Simplified pipeline for creating the final machine learning model that will predict 3D-model quality by giving its RMSD range. \lilian{Make Black and WHite!}}
   \label{fig:flow}
@@
 Both
-approaches are greatly influenced by outliers, and such datapoints are
-ideally removed for optimal scaling. Here we define outliers as
+approaches are greatly influenced by outliers and, ideally, such datapoints are
+removed for optimal scaling. Here we define outliers as
 datapoints that lie over 1.5 times the interquartile range (IQR) below
@@
 data. However, across all features there are a total of 632 outlier
-values and removing such a large number of datapoints is not a viable
-option. A robust scaler\cite{XXXX} was also used, which uses statistics that are
+values and removing such a large number of datapoints was not a viable
+option. A robust scaler\cite{XXXX} \lilian{Citation} was also used, which uses statistics that are
 robust to outliers. The median is set to zero and numerical features
-are scaled to the interquartile range.
+are scaled to the interquartile range. \lilian{So which of these scaling methods did you actually use in the end?!}
 
@@
 
-NLF-encoding \shortcite{Nanni2011} describes a new peptide encoding technique optimized for use with machine learning classifiers.
-A non-linear Fisher transform is applied to the whole set of physiochemical properties in \shortcite{Kawashima2000}
-physiochemical properties are calculated and transformed using a
-non-linear Fisher transform for dimensionality reduction.  A vector of
-length 19 is produced for each amino acid.
-
-\subsubsection{NLF Encoding}
-This method of encoding is detailed by Nanni and Lumini in their paper.
-It takes many physicochemical properties and transforms them using a Fisher Transform (similar to a PCA) creating a smaller set of features that can describe the amino acid just as well.
-There are 19 transformed features.
+NLF-encoding \shortcite{Nanni2011} uses multiple physicochemical
+properties as described by Kawashima\etal\shortcite{Kawashima2000} and
+transforms them using a non-linear Fisher transform (NLF, similar to a
+PCA) for dimensionality reduction to produce a vector of length 19.
 
@@
 
+\lilian{The data are missing --- it would be good to have some
+  comparison of the performance of the individual predictors and
+  discussion of Table~\ref{tab:results_table}.}
+
 \subsection{Feature Calculations}
 
-\begin{table}[]
-  \centering
+\lilian{There is no text in this section!}
+
+\begin{landscape}
+\begin{longtable}{p{3cm}p{10cm}p{10cm}}
   \caption{A summary of how different feature values were calculated.}
-  \label{fig:feature_table}
-
-  \begin{adjustbox}{width=\textwidth}
-
-    \begin{tabular}{| m{5em} | m{20em}| m{20em} |}
-    \hline
-Feature Name & Description & method of Calculation \\
-\hline
-\hline
-Sequence & Amino acid sequence of the CDR-H3 loop. & Sequence is given in one-letter amino acid codes.\\
-\hline
-Length & Number of residues in the CDRH3-loop, which is located at residues H95-H102. & The number of residues are counted.\\
-\hline
-Sequence Identity & Sequence identity of selected template (SeqA) with input loop sequence (SeqB) is determined after sequence alignment.
-Calculated by abYmod during modelling.
-& $Identity(SeqA,SeqB) = 100\%\frac{identical residues}{length(alignment)}$\\
-\hline
-Sequence similarity & Sequence similarity of selected template (SeqA) with input loop sequence (SeqB) is determined after sequence alignment.
-Calculated by abYmod during modelling.
-Similar residues are residues that have undergone conservative substitution.
-&
-$Similarity(SeqA,SeqB) = 100\%\frac{identical residues+similar residues}{length(alignment)}$\\
-\hline
-Loop Protrusion & Distance of loop residue further away from the loop base & Geometrical calculations \protect\ref{fig:loopdist} \\
-\hline
-Protruding residue & The Amino acid code of the most protruding loop residue & Using the previously determined point furthest away from the loop base, the residue at this coordinate is determined and given as a one-letter amino acid code.\\
-\hline
-Charge & Total charge of the loop & Sum of charges of all residues in loop \\
-\hline
-Charge difference & Difference in total charge compared to template sequence & Difference between the two summed changes \\
-\hline
-Hydrophobicity & Mean Hydrophobicity values of loop & Based on Eisenberg consensus values\\
-\hline
-Hydrophobicity  difference & Sum of absolute differences between loop sequence and template loop& Based on Eisenberg consensus values\\
-\hline
-Accessibility & Total and average accessibility for the loop& lee-Richards method implemented using the pdbsolv method from the BiopTools library.\\
-\hline
-Side-chain Accessibility & Total and average side-chain accessibility for the loop& lee-Richards method implemented using the pdbsolv method from the BiopTools library.\\
-\hline
-Relative Accessibility & Total and average relative accessibility for the loop& lee-Richards method implemented using the pdbsolv method from the BiopTools library.\\
-\hline
-relative side-chain Accessibility & Total and average relative side-chain accessibility for the loop& lee-Richards method implemented using the pdbsolv method from the BiopTools library.\\
-\hline
-Happiness & Happiness score, taking accessibility and hydropobicity into account.
-If a residue is 'happy' it will not be a buried hydrophilic or a surface hydrophobic residue.
-& Hydrophobicity values (see above) are normalized to a range of -1 to +1.
-Mean accessibility values are calculated as above.
-If hydrophobicity of loop is $<0$:
+  \label{tab:feature_table}\\ \hline
+%
+  \mbox{Feature} \mbox{Name}  %
+  & Description %
+  & Method of Calculation\\ \hline
+%  
+  Sequence %
+  & Amino acid sequence of CDR-H3 %
+  & Sequence is given in one-letter amino acid codes\\
+%  
+  Length %
+  & Number of residues in CDR-H3 %
+  & The number of residues are counted\\
+%  
+  \mbox{Sequence} \mbox{Identity} %
+  & Sequence identity of template loop ($SeqA$) and target loop ($SeqB$). %
+  & Calculated by abYmod\\
+%  
+  \mbox{Sequence} \mbox{Similarity} %
+  & Sequence similarity of template loop ($SeqA$) and target loop ($SeqB$). %
+  & Calculated by abYmod\\
+%  
+  \mbox{Loop} \mbox{Protrusion} %
+  & Distance of loop residue farthest away from the loop base %
+  & See Figure~\protect\ref{fig:loopdist}\\
+%  
+  \mbox{Protruding} \mbox{residue} %
+  & Amino acid code of the most protruding loop residue %
+  & See Figure~\protect\ref{fig:loopdist}\\
+%  
+  Charge %
+  & Total charge of the loop %
+  & Sum of charges of all residues in loop\\
+%  
+  \mbox{Charge} \mbox{difference} %
+  & Difference in total charge compared with template sequence %
+  & Difference between the two summed changes\\
+%  
+  Hydrophobicity %
+  & Mean Hydrophobicity values of loop %
+  & Based on Eisenberg consensus values\\
+%  
+  \mbox{Hydrophobicity} \mbox{difference} %
+  & Sum of absolute differences between loop sequence and template loop %
+  & Based on Eisenberg consensus values\\
+%  
+  Accessibility %
+  & Total and average accessibility for the loop %
+  & Lee and Richards method implemented using `pdbsolv' from BiopTools\\
+%  
+  \mbox{Sidechain} \mbox{Accessibility} %
+  & Total and average side-chain accessibility for the loop %
+  & Lee and Richards method implemented using `pdbsolv' from BiopTools\\
+%  
+  \mbox{Relative} \mbox{Accessibility}  %
+  & Total and average relative accessibility for the loop %
+  & Lee and Richards method implemented using `pdbsolv' from BiopTools\\
+%  
+  \mbox{Relative} \mbox{Sidechain} \mbox{Accessibility} %
+  & Total and average relative side-chain accessibility for the loop %
+  & Lee and Richards method implemented using `pdbsolv' from BiopTools\\
+%  
+  `Happiness' %
+  & Happiness score, taking accessibility and hydropobicity into account. If a residue is `happy' it will not be a buried hydrophilic or a surface hydrophobic residue %
+  & Hydrophobicity values are normalized to a range of -1 to +1. Mean accessibility values are calculated as above. If hydrophobicity of loop is $<0$:
   $Happiness = 1+Hydrophobicity(1-Accessibility)$
@@
   $Happiness = 1-(Hydrophobicity Accessibility)$\\
-\hline
-Nr.
-of Contacts & Nr of contacts made by the residue of the loop within a range of 3.5\AA.
-Includes mainchain as well as sidechain atoms.
-Contacts made with residue within and outside of the loop are counted separately and as total.
-The ratio of inside vs outside is also calculated.
-& Modified version of the rangecontacts method in the BiopTools library.
-\\
-\hline
-Energy & Potential energy of the model. & Calculated by Gromacs during energy minimization step in abYmod modelling. \\
-\hline
-Lowest BLOSUM 62 Scoring Residue Pair & Each possible residue pair in the CDR-H3loop is scored by their BLOSUM 62 score.
-The lowest scoring pair's BLOSUM62 value will be combined with their residue separation to form the metric.
-& With separation being hte nuber of residues between the worst residue pair, and the worst score being the lowest BLOSUM62 score achieved by a residue pair, the metric is calculated as follows: $WorstBLOSUM = -log_2(separation)(worst score)$\\
-\hline
-
-    \end{tabular}
-
-  \end{adjustbox}
-
-\end{table}
+%  
+  \mbox{Number} \mbox{of} \mbox{Contacts} %
+  & Number of $\le 3.5$\AA\ mainchain or sidechain contacts made by residues of the loop %
+    Contacts made with residues within and outside the loop are counted separately and as a total. The ratio of inside \emph{vs.} outside is also calculated. %
+  & Modified version of `rangecontacts' from BiopTools. \\
+%  
+  Energy %
+  & Potential energy of the model. %
+  & Calculated by Gromacs during the energy minimization step in abYmod. \\
+%
+  \mbox{Lowest} \mbox{BLOSUM62} \mbox{Scoring} \mbox{Residue} \mbox{Pair} %
+  & Each possible residue pair in CDR-H3 is scored by their BLOSUM 62 score. %
+    The lowest scoring pair's BLOSUM62 value is combined with their residue separation to form the metric. %
+  & Separation is the nuber of residues between the worst residue pair (i.e.\ the lowest BLOSUM62 score achieved by a residue pair), %
+    the metric is calculated as: $WorstBLOSUM = -log_2(separation)(worst score)$\\ \hline
+  \end{longtable}
+  \lilian{You need more description of the BLOSUM separation metric in the methods}
+\end{landscape}
 
@@
     \AA\ is used as the `protrusion'
-    feature.}
-  \label{fig:angle}
+    feature. \lilian{This figure needs to be described in the methods!}}
+  \label{fig:loopdist}
 \end{figure}

### 2023-03-14 paper.tex
Updates from Overleaf

@@
 to a large range of loop lengths, with bovine antibodies being
-exceptionally long (Figure~\ref{fig:loopdist}).\lilian{Figure missing!}
+exceptionally long.
 
@@
 canonical conformation of CDR loops CDR-L1,L2,L3,H1,H2 can be identified, they too
-can be modelled rather well, often within 1\AA\ \ca~RMSD. \highlight{for CDR-H3 loops
-the The average values are taken from the antibody modelling assessment average} is usually above 3\AA\cite{Almagro2011}. \lilian{Something odd here --- not sure what it's supposed to say!}
+can be modelled rather well, often within 1\AA\ \ca~RMSD, for CDR-H3 loops
+the average is usually above 3\AA\cite{Almagro2011}. The average values are taken from the second antibody modelling assessment \cite{Almagro2014}.
 
@@
 resolution worse than 4\AA\ were removed.
-Instances of antibodies in our non-redundant dataset that matched in loop sequence were
-not removed as 3D-Models \lilian{Just checking you mean models not structures?
-Do the structures also differ significantly, or do you really mean that the error varies significantly?} of some of these structures with the same loop
+Instances of antibody structures in our non-redundant dataset that matched in loop sequence (but the overall sequence was different) were
+not removed as 3D-Models of some of these structures with the same loop
 sequence differ significantly. 
-\lilian{If I understand correctly, you mean that CDR-H3 could have the same sequence in multiple structures, but the overall sequence was different?}
 The few large RMSD ranges may stem from
@@
 trained, which will predict the probability e.g.\ that the 3D-model's RMSD
-is above 2\AA, 2.2\AA, 2.4\AA, and so on. \highlight{The number of binary
-classifiers incorporated into the first layer} \lilian{You need to describe the overall architecture first so this makes sense.
-I would have a much simpler version of Figure~\ref{fig:flow} which just shows the ML architecture}  has a great effect on
+is above 2\AA, 2.2\AA, 2.4\AA, and so on.
+Several of these binary classifiers form a first layer, each outputting a prediction on whether the model is above or below the respective threshold.
+The outcome values are then fed into a second-layer classifier (Figure~\ref{fig:flow}).
+The number of binary
+classifiers incorporated into the first layer has a great effect on
 the final ML-model, the general trend being that the more binary
 classifiers are used, the better the nominal prediction.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{simple_flow.eps}
+  \caption {Simplified pipeline for creating the final machine learning model that will predict 3D-model quality by giving its RMSD range.}
+  \label{fig:flow}
+\end{figure}
 
@@
 would aim to identify such outlier 3D-models.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{flowchart_qualiloop.eps}
-  \caption {Simplified pipeline for creating the final machine learning model that will predict 3D-model quality by giving its RMSD range. \lilian{Make Black and WHite!}}
-  \label{fig:flow}
-\end{figure}
 

### 2023-03-14 paper.tex
Updates from Overleaf

@@
 feature selection methods was a best fit for all ML-models.
-To create a ML-model implementing the encoding and feature selection strategies best suited for the specific \highlight{ML-structure} \lilian{What is this?}, a number of different combinations were tested, summarized in Table~\ref{tab:results_table}.
+To create a ML-model implementing the encoding and feature selection strategies best suited for the specific types of ML-classifiers selected for the first-layer and top-layer model in combination, a number of different combinations were tested, summarized in Table~\ref{tab:results_table}.
 Additional ML-Models were discarded due to poor performance.
@@
   \centering
-  \caption{Summary of Machine-Learning Classifier Performances \lilian{Is this just the top-level classifier?
+  \caption{Summary of Machine-Learning Classifier Performances.
+The classifier type denotes the top-layer classifier.
+A single-layer model has no binary first layer, only the top-layer classifier.
+If the first layer is weighted, the binary predictions will carry more weight, the higher their certainty is.
+\lilian{Is this just the top-level classifier?
 You need something providing this sort of info for the final selection for the binary classifiers.
@@
 What are `Basic' features?}}
-  \label{tab:results_tableX}
+  \label{tab:results_table}
 
@@
     All             & None          & None              & Single   & No        & Random Forest & 0.58 \\
-    Selected        & Random Forest & GA                & Single   & No        & Soft Voting   & 0.59 \\
+    Selected        & Random Forest & GA                & Single   & No        & Voting (soft)   & 0.59 \\
     Selected        & Random Forest & GA                & Multi    & Yes       & XGBoost       & 0.63 \\

### 2023-06-29 paper.tex
More rewriting and queries from ACRM

@@
 \usepackage{graphicx}
-\usepackage{adjustbox}
+%\usepackage{adjustbox}
 \newcommand{\ca}{\mbox{C$\alpha$}}
@@
 \newcommand{\Fab}{\mbox{\it Fab}}
+\newcommand{\carmsd}{\mbox{C$\alpha$-RMSD}}
 
@@
   far greater length, sequence and structural variability, 
-  making modelling it is considerably harder.
+  making modelling it considerably harder.
 
@@
   structures, giving the user a clearer understanding of the
-  generated 3D-model reliability.
+  reliability of the 3D-model.
 
@@
   3D-models generated by antibody modelling software such as abYmod. The
-  newly developed predictor scored a Matthews Correlation Coefficient
-  of 0.99, and can thus be described as highly reliable. The predictor
+  newly developed predictor is highly reliabkle, with a Matthews Correlation Coefficient
+  of 0.99. The predictor
   is made available at \url{http://www.bioinf.org.uk/abs/qualiloop/}
@@
 Antibodies are highly specialized proteins of the immune system that
-are produced in response to a foreign substance, called an antigen. A
-mature antibody binds a specific antigen with high affinity and specificity.
-This sets them apart from other pharmaceuticals and makes them effective drugs with endless possibilities in application given their ability to target an immense variety of antigens.
-In contrast with small drug molecules, antibodies can not
-only bind pockets, but also flat, concave or convex
+are produced in response to a foreign substance, known as an antigen. A
+mature antibody binds a given antigen with high affinity and specificity.
+These characteristics allow them to be used as pharmaceuticals and make them effective drugs with endless possibilities in application given their ability to target an immense variety of antigens.
+In contrast to small drug molecules, antibodies can not
+only bind into pockets, but also flat, concave or convex
 surfaces\cite{MacCallum1996}. Their unique characteristics have enabled 
 researchers to develop efficient antibody drugs for treating cancers,
-autoimmune disorders, infectious diseases and many more\cite{Lu2020}.
-Four of the top 10 best-selling drugs in
-2020 were monoclonal antibodies\cite{Urquhart2021}.
+autoimmune disorders and infectious diseases amongst others\cite{Lu2020}.
+Exclusing Covid, half of the top 10 best-selling drugs in
+2022 were monoclonal antibodies\cite{Buntz:TopDrugs2022}.
 
-In order to design therapeutic antibodies rationally, knowledge of
+In order to add a rational element to the design of therapeutic antibodies, knowledge of
 their structure is essential. The acquired structural information can
@@
 experimental structure determination is costly and time
-consuming, computational predictions of an antibody's structure are
+consuming, computational predictions of an antibody's structure are often
 used to streamline the process.
@@
 All except one of these loops can be clustered
-into a limited number of `canonical structures'\cite{Al-Lazikani}. Therefore, modelling
-these loops with adequate accuracy is commonly
-achievable\cite{North2011}.  However, the CDR loop 3 of the 
-heavy chain (CDR-H3) has a far greater sequence and length variability due to the
+into a limited number of `canonical structures'\cite{Al-Lazikani}.
+Since these have characteristic sequence motifs, modelling
+these loops with good accuracy is commonly
+achievable\cite{North2011}.  However, the third CDR of the 
+heavy chain (CDR-H3) has a far greater sequence and length variability owing to the
 processes of V(D)J recombination and somatic hyper‐mutation and its
@@
 
-According to the Kabat definition, the CDR-H3 loop is made up of the
+According to the Kabat definition, the CDR-H3 loop is made up of
 residues H95--H102 (using the Kabat\cite{Kabat1992}, Chothia\cite{Al-Lazikani} or Martin\cite{Abhinandan2008} numbering schemes) in the heavy
@@
 Assessments (AMA), two blind contests that required researchers to
-build three-dimensional structural models (`3D-models' --- used throughout this text to distinguid from machine-learning models `ML-models') from antibody sequences. The CDR-H3 loop
-modelling quality achieved at the contests was, on average, much lower
+build three-dimensional structural models from antibody sequences.
+Throughout the rest of this paper, we use the term `3D-models' to distinguish them from machine-learning models (`ML-models'). The CDR-H3 loop
+model quality achieved at the contests was, on average, much lower
 for loops of longer lengths\cite{Almagro2011,Almagro2014}.
@@
 RosettaAntibody\cite{Sircar2009,Sivasubramanian2009}, 
-ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017}, Lyra\cite{Klausen2015}, AbLooper\cite{Abanades2022} and our own abYmod (manuscript in preparation).
-One of the most
-used methods is RosettaAntibody, which implements template selection
+ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017},
+Lyra\cite{Klausen2015}, AbLooper\cite{Abanades2022},
+IgFold\cite{XXXX}, \lilian{Please add a reference}
+and our own abYmod (Martin\etal, manuscript in preparation).
+RosettaAntibody implements template selection
 and \emph{ab initio} CDR-H3 loop modelling using loop fragments and employing
@@
 contrast, ABodyBuilder uses a database search algorithm
-(FREAD\cite{Choi2010}) for CDR loop modelling.
-abYmod \url{http://abymod.abysis.org/} utilizes extensive canonical
-class definitions, \VHVL\ angle prediction and a large database of loop
-structures (LoopDB) for CDR-H3 modelling.
-Upon inputting an antibody sequence, abYmod assigns the
-canonical class using a set of key residues\cite{Martin1996} and where
-an exact match is not possible, a nearest class is identified.
+(FREAD\cite{Choi2010}) for CDR loop modelling. Our own method,
+abYmod, (Available at \url{http://abymod.abysis.org/}) utilizes extensive canonical
+class definitions\cite{Martin1996}, \VHVL\ angle prediction and a large database of loop
+structures from all PDB protein structures (LoopDB) for CDR-H3 modelling.
 
-abYmod selects light and heavy chain frameworks separately from PDB templates.
-First these are selected on the basis of the number of matched
-canonical classes and then on the basis of sequence identity.  The
-\VHVL\ packing angle is currently selected from the parent that has
-the best sequence identity over both chains, but an improved method is
-currently in development. Any CDRs where there was no canonical match are then
-grafted onto the framework. If there is no template of the correct
-length for CDR-H3, the loop is built using LoopDB, a database of
-CDR-H3-like loops from all proteins. Finally, Gromacs energy
-minimization software is used to optimize the 3D-model. This method has
-proven very effective and preliminary analysis suggests the method
-achieves comparable results, or outperforms, other modelling software
-(see Results).
+% abYmod selects light and heavy chain frameworks separately from PDB templates.
+% First these are selected on the basis of the number of matched
+% canonical classes and then on the basis of sequence identity.  The
+% \VHVL\ packing angle is currently selected from the parent that has
+% the best sequence identity over both chains, but an improved method is
+% currently in development. Any CDRs where there was no canonical match are then
+% grafted onto the framework. If there is no template of the correct
+% length for CDR-H3, the loop is built using LoopDB, a database of
+% CDR-H3-like loops from all proteins. Finally, Gromacs energy
+% minimization software is used to optimize the 3D-model. This method has
+% proven very effective and preliminary analysis suggests the method
+% achieves comparable results, or outperforms, other modelling software
+% (see Results).
 
 Using these modelling methods, framework regions can
-generally be predicted with great accuracy (better than 1\AA\
-\ca~RMSD\cite{Almagro2014}), as one can often find a very similar
+generally be predicted with high accuracy (better than 1\AA\
+\carmsd\cite{Almagro2014}), as one can often find a very similar
 structure for the homology modelling process.  However, the CDR loops
-are not as easily predicted due to their great diversity. If the
+are not as easily predicted owing to their great diversity. If the
 canonical conformation of CDR loops CDR-L1,L2,L3,H1,H2 can be identified, they too
-can be modelled rather well, often within 1\AA\ \ca~RMSD, for CDR-H3 loops
+can be modelled rather well, generally with better than 1\AA\ \carmsd, while for CDR-H3 loops,
 the average is usually above 3\AA\cite{Almagro2011}. The average values are taken from the second antibody modelling assessment \cite{Almagro2014}.
@@
 3D-model. The given score is the probability that a specific region
-(e.g.\ CDR-H2) will be modelled within a specific RMSD
+(e.g.\ CDR-H2) will be modelled within a specific \carmsd\
 threshold\cite{Leem2016}. Thus, it can be used to obtain an expected
-RMSD value for a given probability (default 75\%). For CDR-H3, this
+\carmsd\ value for a given probability (default 75\%). For CDR-H3, this
 score is calculated as a function of the loop length.  The confidence
-scorer is described as robust, but less accurate in the case of CDR
+score is described as robust, but is less accurate in the case of CDR
 loops owing to the lack of data\cite{Leem2016}. ABLooper also provides a
-confidence metric for the CDR-H3 loop 3D-model, which is estimated by the
+confidence metric for CDR-H3 3D-models, which is estimated by the
 diversity of a set of predicted conformations for the same
-loop\cite{Abanades2022}. However, it remains unclear whether a high
-prediction diversity score points towards loops with multiple
+loop\cite{Abanades2022}. While CDRs are generally not flexible,
+16\% of CDR-H3s show a local conformational change of $>1.0\AA$
+and 5\% $>2.0\AA$ on binding (Liu and Martin, manuscript in preparation).
+It therefore remains unclear whether a high
+prediction diversity score in CDR-H3 points towards loops with multiple
 conformations or a low quality 3D-model. Furthermore, it remains unclear
@@
 
-Modelling the CDR-H3 loop is a hurdle for \emph{in silico} development of
-therapeutic antibodies. Currently, there is no definite, reliable way
-to determine how accurate a generated structural 3D-model is within the
-CDR-H3 region. Therefore, we have produced a
+Modelling CDR-H3 is a hurdle for \emph{in silico} development of
+therapeutic antibodies; currently, there is no definite, reliable way
+to predict the accuracy of a 3D-model of 
+CDR-H3. Therefore, we have produced a
 user-friendly predictor of CDR-H3 3D-model quality. The predictor will give
-the user an RMSD-range in {\AA}ngstr\"{o}ms, in which the generated 3D-model lies
+the user an \carmsd-range in {\AA}ngstr\"{o}ms, in which the generated 3D-model lies
 with a high probability.
-This information can guide the
-user in the antibody engineering process. The user has the choice to
-determine whether the 3D-model is to be used as is, or
+The user has the choice of
+determining whether the 3D-model should be used as is, or
 whether the 3D-model should be re-worked.
@@
 substantial amount of data was required. Thus, an extensive, verified
-dataset of antibody structures called abYbank/AbDb\cite{Ferdous2018},
-was utilised (1924 non-redundant
-structures). The \ca\ root-mean-square deviation (RMSD) value
+dataset of antibody structures called (AbDb\cite{Ferdous2018}),
+was utilised containing 1924 non-redundant
+structures. Models were built using abYmod and the \carmsd\ value
 between the crystal structures
 and modelled structures was calculated (see Methods) and
-was used to classify 3D-models.
+was used to classify the CDR-H3 3D-models.
 
-The classifier predicts whether a 3D-model has an RMSD of below 2\AA,
+The classifier predicts whether a 3D-model of CDR-H3 has an \carmsd\ of below 2\AA,
 between 2--4\AA, or above 4\AA. These cutoff values were selected
 based on the observation that abYmod generally produces a 3D-model with
-RMSD below 4\AA. Incorrectly modelled structures (Figure~\ref{fig:AMA}) may
-be identified by screening for structures estimated to have an RMSD
-above 4\AA. If a very high-quality 3D-model is needed one should also
-exclude 3D-models with RMSD above 2\AA.
+\carmsd\ below 4\AA\  (Figure~\ref{fig:AMA}). 
+If a high-quality 3D-model is needed, one should also
+exclude 3D-models with \carmsd\ above 2\AA.
 
@@
   \includegraphics[width=\linewidth]{AMA.eps}
-  \caption {RMSD values of the CDR-H3 loop for structures from the
+  \caption {\carmsd\ values of the CDR-H3 loop for structures from the
     Antibody Modelling Assessment I (2011) and AMAII (2014). abYmod
@@
     Right: Ab01 is the rabbit antibody PDB:4MA3, which was
-    excluded in the CDR-H3 modelling stage in AMAII due to
+    excluded in the CDR-H3 modelling stage in AMAII owing to
     difficulties modelling the overall structure previously. Ab01 is
@@
   \caption {Sequence Logo of the CDR-H3 loop sequence. Data on amino
-    acid occurrence taken from \protect\url{http://abymod.abysis.org/} Visualized
-    using Seq2Logo using Kabat Numbering}
+    acid occurrence taken from \protect\url{http://www.abysis.org/} and visualized
+    using Seq2Logo using Kabat numbering.
+    \lilian{Did you use all species for the frequencies or limit to, say, human?}}
   \label{fig:logo}
@@
 
-After creating the feature dataset, it is pre-processed (cleaning,
-scaling, encoding, see methods for details). Structures with a
+After creating the feature dataset (see Methods, Table~\ref{tab:feature_table}), it is pre-processed (cleaning,
+scaling, encoding. See Methods for details). Structures with a
 resolution worse than 4\AA\ were removed.
-Instances of antibody structures in our non-redundant dataset that matched in loop sequence (but the overall sequence was different) were
+Instances of antibody structures in our non-redundant dataset that matched in loop sequence (but where the overall sequence was different) were
 not removed as 3D-Models of some of these structures with the same loop
 sequence differ significantly. 
-The few large RMSD ranges may stem from
-low resolution. For example, the loop sequence with the largest RMSD range 
+The few large \carmsd\ ranges may stem from
+low resolution. For example, the loop sequence with the largest \carmsd\ range 
 has multiple structure files linked to it of varying quality, one of which has a resolution of only 3.00\AA. Residue differences near the loop may also
 explain the conformational difference of the loop itself, 
-even if the loop sequence does not differ. Some of these structures are
-complexed while others are not, which may also affect the loop
-structure (manuscript in preparation).
+even if the sequence of the loop itself does not differ. Some of these structures are
+complexed while others are not, which can also affect the loop
+structure (Liu and Martin, manuscript in preparation).
 
-The target data (i.e.\ RMSD values) are transformed from numerical
+The target data (i.e.\ \carmsd\ values) are transformed from numerical
 values to nominal values so that they can be used for
 classification. In order to define these nominal categories, the total
-RMSD range must be divided into categories. This is done either by
+\carmsd\ range must be divided into categories. This is done either by
 creating uniform classes (e.g.\ 1--2\AA, 2--3\AA, etc.), the optimal size of which
@@
 number of instances. Initially, this approach was chosen to counteract the
-skewness of the RMSD distribution. However, this was found to
+skewness of the \carmsd\ distribution. However, this was found to
 have a negative effect on the final ML-model's predictive power, so
@@
 
-The RMSD values are also transformed into a set of binary values according to a
-list of RMSD thresholds (i.e. a 1 is assigned to above and 0 to below a given threshold). This is done so that binary ML-models can be
-trained, which will predict the probability e.g.\ that the 3D-model's RMSD
-is above 2\AA, 2.2\AA, 2.4\AA, and so on.
+The \carmsd\ values are also transformed into a set of binary values according to a
+list of \carmsd\ thresholds (i.e. a 1 is assigned to above and 0 to below a given threshold). This is done so that binary ML-models can be
+trained, which will predict the probability that the 3D-model's \carmsd\
+is, for example, above or below 2\AA, 2.2\AA, 2.4\AA, and so on.
 Several of these binary classifiers form a first layer, each outputting a prediction on whether the model is above or below the respective threshold.
@@
   \includegraphics[width=\textwidth]{simple_flow.eps}
-  \caption {Simplified pipeline for creating the final machine learning model that will predict 3D-model quality by giving its RMSD range.}
+  \caption {Simplified pipeline for creating the final machine learning model that will predict 3D-model quality by giving its \carmsd\ range.}
   \label{fig:flow}
@@
 As some features are in the form of amino acid names, these must be
-encoded before they can be passed to a ML-model. The
+encoded before they can be passed to an ML-model. The
 encoding strategy often determines how efficiently the ML-model learns
 and how much information can be extracted. Different strategies were
-employed to represent protein sequences numerically, such as BLOSUM62\cite{Henikoff1992} and NLF\cite{Nanni2011} encoding (a non-linear Fisher transform of a large set of physicochemical properties).
-However, the simple four-feature physiochemical encoding strategy\cite{Abhinandan2010} was implemented for all ML-models, as it was found to be
-the most effective, although PCA-3 BLOSUM62, a dimensionality-reduced
-BLOSUM62 encoding method, achieved comparable results.
+employed to represent protein sequences numerically, such as
+BLOSUM62\cite{Henikoff1992} and NLF\cite{Nanni2011} encoding (a
+non-linear Fisher transform of a large set of physicochemical
+properties). However, a simple four-feature physiochemical encoding
+strategy\cite{Abhinandan2010} was found to be the most effective,
+although PCA-3 BLOSUM62 (a dimensionality-reduced BLOSUM62 encoding
+method) achieved comparable results. The simple physical encoding was
+implemented for all ML-models.
 Feature selection was conducted to improve the ML-model's learning
@@
 ML-model was trained on different feature sets selected using manual
-selection as well as algorithmic selection strategies (see methods).
+and algorithmic selection strategies (see Methods).
 None of the
 feature selection methods was a best fit for all ML-models.
-To create a ML-model implementing the encoding and feature selection strategies best suited for the specific types of ML-classifiers selected for the first-layer and top-layer model in combination, a number of different combinations were tested, summarized in Table~\ref{tab:results_table}.
-Additional ML-Models were discarded due to poor performance.
+To create an ML-model implementing the encoding and feature selection strategies best suited for the specific types of ML-classifiers selected for the first-layer and top-layer models in combination, a number of different combinations were tested, summarized in Table~\ref{tab:results_table}.
+Additional ML-Models were discarded owing to poor performance.
 
@@
 
-The best ML-model, and its best hyperparameters, were then determined for
-each binary RMSD target. The set of binary ML-models outputs a number of
-predictions that give the likelihood of the 3D-model having an RMSD above
+The best ML-model, together with its best hyperparameters, was then determined for
+each binary \carmsd\ target. The set of binary ML-models outputs a number of
+predictions that give the likelihood of the 3D-model having an \carmsd\ above
 the threshold value of the respective ML-model. These predictions are
 then added to the feature set, on which a top-layer classifier is then
-trained (Figure~\ref{fig:method})\lilian{Incorrect reference}. Thus, a quasi-voting-system is incorporated into the final
+trained (Figure~\ref{fig:method})\lilian{Incorrect reference}.
+Thus, a quasi-voting-system is incorporated into the final
 classifier, in which a set of weaker classifiers vote on the ML-model
@@
 The overall best final ML-model was composed of several different binary
-classifiers, (Figure~\ref{fig:flow}) with an extreme gradient boosting (XGBoost) top-layer
+classifiers (Figure~\ref{fig:flow}), with an extreme gradient boosting (XGBoost) top-layer
 nominal classifier. Features were selected using a recursive feature
 elimination algorithm, through which the weakest feature is removed
-recursively and the model performance is tested. In the final model, 9
-features are included: tip\_pos, protrusion, length, total\_charge, nr\_charged,
+recursively and the model performance is tested. In the final model, nine
+features were included: tip\_pos, protrusion, length, total\_charge, nr\_charged,
 identity, similarity, Hydropathy and Hydropathy\_diff
-(See Table~\ref{tab:feature_table}).
+(See Methods, Table~\ref{tab:feature_table}).
 \lilian{This appears to be the top level.
@@
 
-A final MCC value of 0.99 could be achieved for an ML-model
-using the abYmod log file as input as well as the loop 3D-model file
-itself. This value slightly dropped to 0.92 if no such log file was
-given. This is due to the fact that the template sequence
-abYmod used to generate the 3D-model is unknown in the latter case
-and therefore, sequence identity, similarity and hydropathy difference cannot be calculated. The energy is also not available.
+A final MCC value of 0.99 could be achieved for an ML-model using the
+3D-model together with the abYmod log file from which sequence
+identity, similarity and hydropathy difference (all compared with the
+parent structures) as well as the energy from energy minimization
+could be included. For a predictor that doesn't incorporate these data
+and required only the 3D-model (and could thus be used with different
+modelling approaches), the MCC drops slightly to 0.92.
+\lilian{What was the test set for these MCC values?}
 \lilian{There is no option to upload the log file on the web site!}
@@
 Figure~\ref{fig:AMA} show, abYmod generally achieves results similar to, or better than,
-other modelling programs. However, some outliers with very high RMSD
-values increase abYmod's RMSD average. The predictor in this work
-would aim to identify such outlier 3D-models.
+other modelling programs. However, some outliers with very high \carmsd\
+values increase abYmod's \carmsd\ average. \highlight{The predictor in this work
+  would aim to identify such outlier 3D-models.} \lilian{This needs rewording ---
+  does the predictor actually succeed in doing so?!}
 
@@
 optimization algorithms were implemented in Python. The Scikit-learn
-library was used for training ML-models, the
+library was used for training ML-models and the
 Yellowbrick\cite{Bengfort2021} library was utilized for
@@
 \subsection{Data Pre-Processing and Preparation}
-Handling Null Values and Duplicates: The dataset containing target
-RMSD values, and the calculated features was screened for null
-values.
+
+\subsection{Handling Null Values}
+The dataset containing target
+\carmsd\ values and calculated features was screened for null
+values which occur when a parameter cannot be calculated.
 Rows that contained any null values were
-removed from the dataset (11 rows in total).
+removed from the dataset (11 rows in total). \lilian{From how many?}
 
@@
 Normalization and Standardization were tested as scaling methods.
-In normalization the range of the data is fixed between 0 and 1, while in Standardization the data is re-scaled to fit a Gaussian distribution.
+In normalization the range of the data is fixed between 0 and 1, while in Standardization the data are re-scaled to fit a Gaussian distribution.
 Both
@@
 values and removing such a large number of datapoints was not a viable
-option. A robust scaler\cite{XXXX} \lilian{Citation} was also used, which uses statistics that are
+option. Consequently, a robust scaler\cite{XXXX} \lilian{Add Citation} was employed, which uses statistics that are
 robust to outliers. The median is set to zero and numerical features
-are scaled to the interquartile range. \lilian{So which of these scaling methods did you actually use in the end?!}
+are scaled to the interquartile range. \lilian{I'm assimung this
+  robust scaler was what was used for the final predictions?!}
 
@@
 The BLOSUM62 matrix reflects the frequencies of amino acid
-substitutions within a locally aligned, conserved regions of proteins
+substitutions within locally aligned, conserved regions of proteins
 with at least 62\% similarity. Each amino acid is represented by a row
@@
 NLF-encoding \shortcite{Nanni2011} uses multiple physicochemical
-properties as described by Kawashima\etal\shortcite{Kawashima2000} and
+properties as described by Kawashima\etal\shortcite{Kawashima2000}
+\lilian{This reference isn't in the .bib file} and
 transforms them using a non-linear Fisher transform (NLF, similar to a
@@
 The final ML-model was evaluated using a test set, separated from the
-training set at the start in a 30/70 split. The performance of all individual sub-ML-models of the first layer was determined using stratified K-folds cross-validation (K=10) as the
-dataset is imbalanced, being skewed towards lower RMSD values\cite{Krstajic2014,Kohavi1995}. The
+training set at the start in a 30/70 split. The performance of each of the individual sub-ML-models of the first layer was determined using stratified K-folds cross-validation (K=10) as the
+dataset is imbalanced, being skewed towards lower \carmsd\ values\cite{Krstajic2014,Kohavi1995}. The
 method is different from normal K-folds cross validation as it uses
@@
 differently and must thus be considered separately. The Matthews
-Correlation Coefficient (MCC)\cite{Chicco2020} is deemed the most
+Correlation Coefficient (MCC)\cite{Chicco2020} is generally considered to be the most
 informative, taking the ratios of the four confusion matrix categories
@@
 accuracy. It is also consistent for both binary and multi-class
-problems and therefore well suited for our purpose.\cite{Jurman2012}
+problems and therefore well suited for our purpose\cite{Jurman2012}.
 
@@
 between well-modelled and less well-modelled CDR-H3 loop
-structures. An MCC value of 0.99 was achieved, which underlines this
+structures. An MCC value of 0.99 was achieved,
+\lilian{You need more explanation of how this was obtained:
+  what was the train and test? was it k-fold cross-validation
+  (if so what was $k$?) How did you calculate an MCC for a
+  3-class problem?}
+which underlines this
 ability for accurate discrimination. Different methods for data
@@
 methods e.g.\ t-SNE) were used on BLOSUM62 encoded matrices, which lead
-to significant improvement. However, a physicochemical encoding
-strategy was most effective.
+to significant improvement. However, a simple physicochemical encoding
+strategy was found to be the most effective.
 The selection of features incorporated in the training set seemed to
 be most important for effective learning. A multitude of methods were
-tested. No one fit-for-all method for the different ML-models could be
-found. However, for our top-layer classifier in our final ML-model
+tested. No single fit-for-all method for the different ML-models could be
+found. However, for our top-layer classifier in the final ML-model,
 recursive feature elimination worked best.
@@
 An MCC value of 0.99 was achieved for a classifier predicting whether
-an input 3D-model has an RMSD value below 2\AA, 2\AA--4\AA\ or above
+an input 3D-model has an \carmsd\ value below 2\AA, 2\AA--4\AA\ or above
 4\AA.
 
-We are now looking at incorporating the predictor into the antibody
-modelling process in the selection of high quality CDR-H3 models given
-a set of potential decoys.
+The performance of predictor suggests that it would be a very useful
+addition to antibody modelling strategies as it gives a reliable
+prediction of the quality of a CDR-H3 model. Given the ability to
+distinguish good models from bad, we are now looking at incorporating
+the predictor into the antibody modelling process in the selection of
+high quality CDR-H3 models given a set of potential decoys.
 
